---
title: "Social learning by type-token frequency - analysis"
author: |
  | Ansgar D. Endress
  | City, University of London
bibliography: /Users/endress/ansgar.bib
output:
  pdf_document:
    citation_package: natbib
    toc: no
    number_sections: yes
    keep_tex: yes
    fig_caption: yes
    highlight: tango
  html_notebook:
    theme: spacelab
    number_sections: yes
    toc: yes
    toc_float: yes
    fig_caption: yes
    highlight: tango
  html_document:
    theme: spacelab
    number_sections: yes
    df_print: paged
    toc: yes
    toc_float: yes
    fig_caption: yes
    highlight: tango
csl: /Users/endress/csl_files/science.csl
keywords: Keywords
abstract: Abstract (to be written). Discuss quorum sensing [@Sumpter2009]
---

```{r setup, echo = FALSE, include=FALSE}
rm (list=ls())

options (digits = 3)
knitr::opts_chunk$set(
    # Run the chunk
    eval = TRUE,
    # Don't include source code
    echo = FALSE, 
    # Print warnings to console rather than the output file
    warning = FALSE,  
    # Stop on errors
    error = FALSE,
    # Print message to console rather than the output file
    message = FALSE,
    # Include chunk output into output
    include = TRUE,
    # Don't reformat R code
    tidy = FALSE,
    # Center images
    fig.align = 'center',
    # Default image width
    out.width = '80%')

# other knits options are here:
# https://yihui.name/knitr/options/
```


```{r load-libraries, include = FALSE, message = TRUE, warning = TRUE}

if (Sys.info()[["user"]] %in% c("ansgar", "endress")){
    source ("/Users/endress/R.ansgar/ansgarlib/R/tt.R")
    source ("/Users/endress/R.ansgar/ansgarlib/R/null.R")
    #source ("helper_functions.R")
} else {
    # Note that these will probably not be the latest versions
    source("http://endress.org/progs/tt.R")
    source("http://endress.org/progs/null.R")
}

library (knitr)
library (kableExtra)
```

```{r set-parameters}
DATA.DIR <- "../data/"
OUTPUT.DIR <- "output/"
FIG.DIR <- "figs/"




FILTER.BY.ATTRACTIVENESS <- FALSE    
MIN.ATTRACTIVENESS.QUANTILE <- .25
MAX.ATTRACTIVENESS.QUANTILE <- 1

# Parameters for analysis
IGNORE.COL.PREFIXES <- c("ITI_", "presTime_", "ISI_")

PRINT.INDIVIDUAL.FIGURES <- FALSE
PRINT.INDIVIDUAL.TABLES <- FALSE

REMOVE.BAD.SUBJ <- TRUE


# Should we remove participants who take excessively long/short?
DURATION.REMOVAL.THRESHOLD.Z <- 3

# Stimulus parameters
# PRESTIME <- 4000
# ITI <- 1000
PRESTIME <- 4500
ITI <- 500


N.REPETITIONS.PER.ACTION <- 6
# Number of face stimuli required
N.FACES.PER.GENDER <- 3 * 4 * 3 * N.REPETITIONS.PER.ACTION

VALENCE.IS.BETWEEN.SUBJECTS <- TRUE

# Set seed to Cesar's birthday
set.seed (1207100)
```

```{r helper-functions}


```


```{r read-data, include = FALSE}
dat.social.type.token.sequential.raw <- read.testable.results("../data/994749_sequential_1/results", 
                                                   n.subj.info.lines = 2,
                                                   comment.char = "",
                                                   ignore.col.prefixes = IGNORE.COL.PREFIXES,
                                                   stringsAsFactors = FALSE) 

```


```{r check-attention-test}

dat.social.type.token.sequential.bad.subj.attention <- dat.social.type.token.sequential.raw %>% 
    dplyr::filter (myPhase == "attentionTest") %>% 
    dplyr::select(filename, myPhase, response) %>% 
    dplyr::filter(response !=2)

if (nrow (dat.social.type.token.sequential.bad.subj.attention) > 0 ){
    dat.social.type.token.sequential.raw <- 
        anti_join(
            dat.social.type.token.sequential.raw,
            dat.social.type.token.sequential.bad.subj.attention,
            by = "filename")
    
}
    
    
```

We excluded `r nrow (dat.social.type.token.sequential.bad.subj.attention)` participants because they failed the attention test.

We next analyze the SD and combine the results with the data frame for the main experiment. 


```{r analyze-sd3}

dat.social.type.token.sequential.sd3 <- dat.social.type.token.sequential.raw %>% 
    dplyr::filter (myPhase == "SD3") %>% 
    dplyr::mutate (max.response = str_count (responseOptions, ";") + 1) %>% 
    dplyr::mutate (responseCode = as.numeric (responseCode)) %>% 
    # Don't know if it's logical or not
    dplyr::mutate (mySD3reversed = as.character (mySD3reversed)) %>% 
    dplyr::mutate (responseCode = ifelse (mySD3reversed == "TRUE",
                                          max.response + 1 - responseCode,
                                          responseCode)) %>% 
    dplyr::group_by (filename, myPhase, mySD3subScale) %>% 
    dplyr::summarize (score = sum (responseCode)) %>% 
    tidyr::pivot_wider(id_cols = c(filename, myPhase),
                       names_from = mySD3subScale,
                       values_from = score)
    
                       
```

```{r combine-with-sd3}

dat.social.type.token.sequential <- 
    left_join(
        dat.social.type.token.sequential.raw %>% 
            dplyr::filter (myPhase == "experiment"),
        dat.social.type.token.sequential.sd3 %>% 
            dplyr::select(-c(myPhase)),
        by = "filename") 
    

```

```{r format-responses}
# * separate response code into 3 separate response
# * add binary responses
# * transform to long

dat.social.type.token.sequential <- 
    dat.social.type.token.sequential %>% 
    dplyr::mutate (max.response = str_count (responseOptions, ";") + 1) %>% 
    tidyr::separate(responseCode, 
                    c("prevalence_raw", "third.party.acceptability_raw", "first.party.acceptablity_raw"),
                    convert = TRUE) %>% 
    dplyr::mutate (dplyr::across (ends_with("raw"),
                                  ~ 1 * (.x > max.response/2), 
                                  .names = "{.col}_bin")) %>% 
    dplyr::rename_with (~ str_replace (.x, "raw_bin", "bin"), ends_with("bin")) %>% 
    tidyr::pivot_longer(c(ends_with("raw"), ends_with("bin")),
                        names_to = "question",
                        values_to = "rating") %>% 
    tidyr::separate(question, c("question", "scoring"), "_") %>% 
    dplyr::mutate (question = factor (question, levels = c("prevalence", "third.party.acceptability", "first.party.acceptablity"))) %>% 
    dplyr::mutate (myValence = factor (myValence, levels = c("bad", "neutral", "good")))
    
    

```

```{r make-averages}

dat.social.type.token.sequential.m <- dat.social.type.token.sequential %>% 
    dplyr::group_by (filename, age, gender, Machiavellianism, Narcissism, Psychopathy, myQueriedActionStatus, myValence, question, scoring) %>% 
    dplyr::summarize (rating = mean (rating)) %>% 
    dplyr::arrange (filename, scoring, myValence, myQueriedActionStatus, question)



```

```{r make-wide}

make.diff.score <- function (x, y, relative = TRUE){
    
    if (relative) {
        
        (x - y) / (x + y)
    } else {
        
        x - y 
    }
        
}

dat.social.type.token.sequential.m.wide <- dat.social.type.token.sequential.m %>% 
    tidyr::pivot_wider(id_cols = c(filename, age, gender, Machiavellianism, Narcissism, Psychopathy, myValence),
                       names_from = c(myQueriedActionStatus, question, scoring),
                       values_from = rating) %>% 
    # Difference scores compared to single occurrence
    dplyr::mutate (
        # Difference scores high type frequency vs single - binary
        d.vs.single_highTypeFreq_prevalence_bin = make.diff.score (highTypeFreq_prevalence_bin,
                                                                   single_prevalence_bin),
        d.vs.single_highTypeFreq_third.party.acceptability_bin = make.diff.score (highTypeFreq_third.party.acceptability_bin,
                                                                                  single_third.party.acceptability_bin),
        d.vs.single_highTypeFreq_first.party.acceptablity_bin = make.diff.score (highTypeFreq_first.party.acceptablity_bin,
                                                                                 single_first.party.acceptablity_bin),
        
        
        # Difference scores low type frequency vs single - binary
        d.vs.single_lowTypeFreq_prevalence_bin = make.diff.score (lowTypeFreq_prevalence_bin,
                                                                  single_prevalence_bin),
        d.vs.single_lowTypeFreq_third.party.acceptability_bin = make.diff.score (lowTypeFreq_third.party.acceptability_bin,
                                                                                 single_third.party.acceptability_bin),
        d.vs.single_lowTypeFreq_first.party.acceptablity_bin = make.diff.score (lowTypeFreq_first.party.acceptablity_bin,
                                                                                single_first.party.acceptablity_bin),
        
        # Difference scores high type frequency vs single - raw
        d.vs.single_highTypeFreq_prevalence_raw = make.diff.score (highTypeFreq_prevalence_raw,
                                                                   single_prevalence_raw),
        d.vs.single_highTypeFreq_third.party.acceptability_raw = make.diff.score (highTypeFreq_third.party.acceptability_raw,
                                                                                  single_third.party.acceptability_raw),
        d.vs.single_highTypeFreq_first.party.acceptablity_raw = make.diff.score (highTypeFreq_first.party.acceptablity_raw,
                                                                                 single_first.party.acceptablity_raw),
        
        # Difference scores low type frequency vs single - raw
        d.vs.single_lowTypeFreq_prevalence_raw = make.diff.score (lowTypeFreq_prevalence_raw,
                                                                  single_prevalence_raw),
        d.vs.single_lowTypeFreq_third.party.acceptability_raw = make.diff.score (lowTypeFreq_third.party.acceptability_raw,
                                                                                 single_third.party.acceptability_raw),
        d.vs.single_lowTypeFreq_first.party.acceptablity_raw = make.diff.score (lowTypeFreq_first.party.acceptablity_raw,
                                                                                single_first.party.acceptablity_raw)
    ) %>% 
    
    # Difference scores high vs. low type frequency
    dplyr::mutate (
     # Difference scores high type frequency vs low type frequency - binary
        d.high.vs.low.TypeFreq_prevalence_bin = make.diff.score (highTypeFreq_prevalence_bin,
                                                                   lowTypeFreq_prevalence_bin),
        d.high.vs.low.TypeFreq_third.party.acceptability_bin = make.diff.score (highTypeFreq_third.party.acceptability_bin,
                                                                                  lowTypeFreq_third.party.acceptability_bin),
        d.high.vs.low.TypeFreq_first.party.acceptablity_bin = make.diff.score (highTypeFreq_first.party.acceptablity_bin,
                                                                                 lowTypeFreq_first.party.acceptablity_bin),
        
        
        # Difference scores high type frequency vs low type frequency - raw
        d.high.vs.low.TypeFreq_prevalence_raw = make.diff.score (highTypeFreq_prevalence_raw,
                                                                   single_prevalence_raw),
        d.high.vs.low.TypeFreq_third.party.acceptability_raw = make.diff.score (highTypeFreq_third.party.acceptability_raw,
                                                                                  single_third.party.acceptability_raw),
        d.high.vs.low.TypeFreq_first.party.acceptablity_raw = make.diff.score (highTypeFreq_first.party.acceptablity_raw,
                                                                                 single_first.party.acceptablity_raw)
    )


```

```{r save-for-students}

xlsx::write.xlsx (
    data.frame (column = names (dat.social.type.token.sequential.m.wide)),
    file="output/dat.social.type.token.sequential.xlsx",
    row.names=FALSE,
    sheetName="Explanation",
    append=FALSE)

xlsx::write.xlsx (
    dat.social.type.token.sequential.m.wide %>% 
        dplyr::select(-ends_with(fixed ("_bin"))) %>% 
        as.data.frame,
    file="output/dat.social.type.token.sequential.xlsx",
    row.names=FALSE,
    sheetName="Raw ratings",
    append=TRUE)


xlsx::write.xlsx (
    dat.social.type.token.sequential.m.wide %>% 
        dplyr::select(-ends_with(fixed ("_raw"))) %>% 
        as.data.frame,
    file="output/dat.social.type.token.sequential.xlsx",
    row.names=FALSE,
    sheetName="Binary ratings",
    append=TRUE)
```

`r clearpage()`

# Summary
## Ratings

### Prevalence

We observed a main effect of valency, suggesting that good actions were judged better than neutral actions, which were judged better than neutral actions. VERIFY THIS. GLMER: good > neutral = bad

We also observed a main effect of Action Status, suggesting that single occurence actions were judged as less prevalent than low frequency actions, which we judged as less prevalent than high type frequency actions. 

The interaction was not significant. 

### Third party acceptability

We observed a main effect of valency, suggesting that good actions were judged better than neutral actions, which were judged better than neutral actions. 

We also observed a main effect of Action Status, suggesting that single occurence actions were judged as worse than low frequency actions, which we judged as worse than high type frequency actions. 

These factors did not interact.

### First party acceptability

We observed a main effect of valency, suggesting that good actions were judged better than neutral actions, which were judged better than neutral actions. VERIFY THIS. GLMER: good > neutral = bad

We also observed a main effect of Action Status, suggesting that single occurence actions were judged as worse than low frequency actions, which we judged as worse than high type frequency actions. 

These factors interacted. The effect of Action Status was only significant for neutral and good action, where the effect size for neutral actions was twice as high as for good actions.

## Difference scores
### Prevalence

The difference score comparing the high/low type frequency condition against the single occurrence condition yielded a significant main effect of Action Status, suggesting that the difference score was greater for the high type frequency condition than for the low type frequency condition. While the main effect of valency did not reach significance, the the interaction reached significance. The effect size associated with Action Status was much larger for neutral scenarios. 

The difference score comparing the high and the low typ frequency condition revealed a significant main effect of Valency, suggesting that that the difference score did not differ between bad and neutral actions, but between neutral and good actions. 

### Third party acceptability
The difference score comparing the high/low type frequency condition against the single occurrence condition yielded a significant main effect of Action Status, suggesting that the difference score was greater for the high type frequency condition than for the low type frequency condition. Neither the main effect of valency nor the interaction reached significance. 

Following up this interaction, we found that the main effect of Valency was only significant for high type frequency actions, but not for low frequency actions. Further, the effect size association with Action Status was much larger for neutral scenarios. 

The difference score comparing the high and the low typ frequency condition revealed a marginal main effect of Valency, suggesting that that the difference score did not differ between bad and neutral actions, but differed marginally between neutral and good actions. 

### First party acceptability
The difference score comparing the high/low type frequency condition against the single occurrence condition yielded a significant main effect of Action Status, suggesting that the difference score was greater for the high type frequency condition than for the low type frequency condition. The main effect of valency reached significance, as did the interaction.

Following up this interaction, we found that the main effect of Valency was only significant for high type frequency actions, but not for low frequency actions. Further, the effect size association with Action Status was much larger for neutral scenarios, and reached significance only for these scenarios. 

The difference score comparing the high and the low typ frequency condition revealed a marginal main effect of Valency, suggesting that that the difference score differed marginally between bad and neutral actions, but differed significantly between neutral and good actions. 


`r clearpage()`

# Raw ratings
## Ratings (analyzed using ANOVAs)

```{r print-descriptives-ratings-raw}

dat.social.type.token.sequential.m %>% 
    dplyr::filter(scoring == "raw") %>% 
    dplyr::select(-scoring) %>% 
    dplyr::group_by(myValence, myQueriedActionStatus, question) %>% 
    dplyr::summarize(
        N = n(),
        M = mean(rating),
        SE = se(rating),
        d = M/sd(rating),
        # That's correct only for raw ratings
        p = wilcox.p(rating, mu = 2.5)
        ) %>% 
    dplyr::arrange (question, myValence, myQueriedActionStatus) %>% 
    tidyr::unite(pack.col, myValence, question, sep = " - ") %>% 
    kable.packed("pack.col", 
                 caption = "Descriptive for the untransformed data. The p value reflects a Wilcoxon test against the scale midpoint of 2.5.",
                 col.names = c("", "N", "M", "SE", "Cohen's d", "p"),
                 booktabs = TRUE,
                 longtable=TRUE) %>% 
    kableExtra::kable_styling(latex_options = "repeat_header") %>% 
    kableExtra::kable_classic_2()


```

```{r plot-ratings-raw, fig.cap = "Raw ratings"}

dat.social.type.token.sequential.m %>% 
    dplyr::filter (scoring == "raw") %>% 
    dplyr::mutate (myQueriedActionStatus = str_wrap(myQueriedActionStatus, 10)) %>% 
    dplyr::mutate (question = str_replace_all(question, fixed ("."), " ")) %>% 
    dplyr::mutate (question = str_wrap(question, 20)) %>% 
    ggplot (aes (x = myQueriedActionStatus, y = rating)) +
        theme_light(14) +
    theme (axis.title.x = element_blank(),
           axis.text.x = element_text(angle = 35, vjust = .5, hjust=.5)) + 
    ylab ("Rating (raw)") + 
    geom_violin() +
    geom_dotplot(binaxis='y', stackdir='center', dotsize=1) +
    stat_summary(fun.data=mean_se, 
                 geom="pointrange", color="red") +
    geom_hline(yintercept=2.5, linetype = "dotted") +
    #scale_x_discrete(labels = c("Pre-segmented", "Continuous (1)", "Continuous (2)"))
    facet_grid(question ~ myValence)




```

`r clearpage()`

### Prevalence 

```{r city-prevalence-sw}

#get.lambda.trans 

dat.social.type.token.sequential.prevalence.sw <- 
    calculate.shapiro.wilk.test.for.cells(
        dat.social.type.token.sequential.m %>% 
            dplyr::filter(scoring == "raw") %>% 
            dplyr::filter(question == "prevalence"),
        c("myValence",
          "myQueriedActionStatus"),
        "rating")

dat.social.type.token.sequential.prevalence.sw %>% 
    kable (caption = "SW acceptability for participants themselves", booktabs = TRUE, escape = FALSE) %>% 
    kableExtra::kable_classic_2()
```

As shown in Table \ref{tab:city-prevalence-sw}, a number of cells deviated from normality. TODO: TRY TO HEAL IT BY TRANSFORMING


```{r city-typrevalence-aov-calculate}

aov.social.type.token.sequential.prevalence <- aov(
    rating ~ myQueriedActionStatus * myValence + 
        Error (filename/(myQueriedActionStatus)), 
    data = dat.social.type.token.sequential.m %>% 
        dplyr::filter(scoring == "raw") %>% 
        dplyr::filter(question == "prevalence"))

dat.aov.social.type.token.sequential.prevalence <- report.aov(aov.social.type.token.sequential.prevalence,
           .correct.for.repeated.tests = FALSE,
           .return.df = TRUE,
           .print.results = FALSE) %>%
    dplyr::select(-c("model.name"))

```

```{r city-prevalence-aov-ez-calculate}
aov.social.type.token.sequential.prevalence.ez <- ezANOVA(
    data = dat.social.type.token.sequential.m %>% 
        dplyr::filter(scoring == "raw") %>% 
        dplyr::filter(question == "prevalence"),
    dv = .(rating),
    wid = .(filename),
    between = .(myValence),
    within = .(myQueriedActionStatus),
    detailed = TRUE,
    type = 3)

aov.social.type.token.sequential.prevalence.ez.sphericity <- 
    extract.sphericity.from.ezANOVA(aov.social.type.token.sequential.prevalence.ez)

```

As shown in Table \ref{tab:city-prevalence-aov-show}, we observed the expected main effect of Valency on first-party acceptability. Further, we observer a main effect of Action Status. The interaction between Action Status and Valency did not reach significance. 



```{r city-prevalence-aov-follow-up-valency}
dat.aov.social.type.token.sequential.prevalence.followup.valency <- 
dat.social.type.token.sequential.m %>% 
    dplyr::filter(scoring == "raw") %>% 
    dplyr::filter(question == "prevalence") %>% 
    dplyr::group_by(myValence) %>% 
    tidyr::nest() %>% 
    # data is the column created by nest
    dplyr::mutate(aov =  map(data,
                             ~ aov(
                                 rating ~ myQueriedActionStatus + 
                                     Error (filename/(myQueriedActionStatus)), 
                                 data = .x) %>% 
                                 report.aov(.correct.for.repeated.tests = FALSE,
                                            .return.df = TRUE,
                                            .print.results = FALSE)
    )) %>% 
    dplyr::select(-data) %>% 
    unnest %>% 
    dplyr::select(-model.name)



```

As shown in Table \ref{tab:city-prevalence-aov-show}, separate ANOVAs for each valency revealed a strong main effect of Action Status for all valencies.

```{r city-prevalence-aov-follow-up-action-status}
v.myQueriedActionStatuses <- levels2(dat.social.type.token.sequential.m$myQueriedActionStatus) %>% 
    rev

dat.aov.social.type.token.sequential.prevalence.followup.actionStatus <- 
    purrr::map(v.myQueriedActionStatuses,
               ~ dat.social.type.token.sequential.m %>%
                   dplyr::ungroup() %>% 
                   dplyr::filter(scoring == "raw") %>% 
                   dplyr::filter(question == "prevalence") %>% 
                   dplyr::mutate(myQueriedActionStatus.excluded = .x, .before = 1) %>% 
                   dplyr::filter(myQueriedActionStatus != myQueriedActionStatus.excluded)) %>% 
    dplyr::bind_rows() %>% 
    dplyr::group_by(myQueriedActionStatus.excluded) %>% 
    tidyr::nest() %>% 
    dplyr::mutate(aov =  map(data,
                             ~ aov(
                                 rating ~ myQueriedActionStatus * myValence +
                                     Error (filename/(myQueriedActionStatus)),
                                 data = .x) %>%
                                 report.aov(.correct.for.repeated.tests = FALSE,
                                            .return.df = TRUE,
                                            .print.results = FALSE))) %>%
    dplyr::select(-data) %>%
    tidyr::unnest() %>%
    dplyr::mutate(myQueriedActionStatus =  str_c (v.myQueriedActionStatuses[!(v.myQueriedActionStatuses %in% myQueriedActionStatus.excluded)], collapse = " vs. "), .before = 1) %>%
    dplyr::ungroup() %>%
    dplyr::select(-myQueriedActionStatus.excluded, -model.name) 




```    
Finally, Table \ref{tab:city-prevalence-aov-show} shows separate two way ANOVAs leaving out one of the Action Statuses. In all ANOVAs, we observed the expected main effect of Valency. We also observed a main effect of Action Status for all comparisons, suggesting that both an increased token frequency and an increased type frequency affect first party acceptability. 

Finally, the interaction between Action Status and Valency failed to reach significance .

```{r city-prevalence-aov-show}

if (!is.null (aov.social.type.token.sequential.prevalence.ez.sphericity)){
    warning ("There were sphericity corrections available that you ignored, do something about them.")    
}

dplyr::bind_rows(
    # Overall anova
    dat.aov.social.type.token.sequential.prevalence %>% 
        dplyr::mutate(model.type = "Overall"),
    
    # Follow-up valency
    dat.aov.social.type.token.sequential.prevalence.followup.valency %>% 
        dplyr::mutate(model.type = "Follow-up of valency") %>% 
        tidyr::unite(model.type, model.type, myValence, sep = ": "),
    
    # Follow-up action status
    dat.aov.social.type.token.sequential.prevalence.followup.actionStatus %>%
        dplyr::mutate(model.type = "Follow-up of Action Status") %>% 
        tidyr::unite(model.type, model.type, myQueriedActionStatus, sep = ": "),
) %>%  
    setNames(replace_default_column_labels(names (.))) %>%
    kable.packed("model.type",
                  caption = "ANOVA for prevalence judgments and unprocessed ratings. The data combines male and female participants. (Top) Overall ANOVA. (Middle) Differences between frequency conditions separately for each valency for first person acceptability for all participants. (Bottom). Differences for each frequency conditions separately for first person acceptability for all participants.",
                  booktabs = TRUE, escape = FALSE) %>%
            kable_styling(latex_options =
                              c("hold_position", "striped", "scale_down")) %>%
    kableExtra::kable_classic_2()

```


`r clearpage()`

### Third-party acceptability

```{r city-acceptability-other-sw}

#get.lambda.trans 

dat.social.type.token.sequential.acceptability.other.sw <- 
    calculate.shapiro.wilk.test.for.cells(
        dat.social.type.token.sequential.m %>% 
            dplyr::filter(scoring == "raw") %>% 
            dplyr::filter(question == "third.party.acceptability"),
        c("myValence",
          "myQueriedActionStatus"),
        "rating")

dat.social.type.token.sequential.acceptability.other.sw %>% 
    kable (caption = "SW acceptability for participants themselves", booktabs = TRUE, escape = FALSE) %>% 
    kableExtra::kable_classic_2()
```

As shown in Table \ref{tab:city-acceptability-other-sw}, a number of cells deviated from normality. TODO: TRY TO HEAL IT BY TRANSFORMING

```{r city-tyacceptability-other-aov-calculate}

aov.social.type.token.sequential.acceptability.other <- aov(
    rating ~ myQueriedActionStatus * myValence + 
        Error (filename/(myQueriedActionStatus)), 
    data = dat.social.type.token.sequential.m %>% 
        dplyr::filter(scoring == "raw") %>% 
        dplyr::filter(question == "third.party.acceptability"))

dat.aov.social.type.token.sequential.acceptability.other <- report.aov(aov.social.type.token.sequential.acceptability.other,
           .correct.for.repeated.tests = FALSE,
           .return.df = TRUE,
           .print.results = FALSE) %>%
    dplyr::select(-c("model.name"))

```
```{r city-acceptability-other-aov-ez-calculate}
aov.social.type.token.sequential.acceptability.other.ez <- ezANOVA(
    data = dat.social.type.token.sequential.m %>% 
        dplyr::filter(scoring == "raw") %>% 
        dplyr::filter(question == "third.party.acceptability"),
    dv = .(rating),
    wid = .(filename),
    between = .(myValence),
    within = .(myQueriedActionStatus),
    detailed = TRUE,
    type = 3)

aov.social.type.token.sequential.acceptability.other.ez.sphericity <- 
    extract.sphericity.from.ezANOVA(aov.social.type.token.sequential.acceptability.other.ez)

```

As shown in Table \ref{tab:city-acceptability-other-aov-show}, we observed the expected main effect of Valency on third-party acceptability. Further, we observed a main effect of Action Status. The interaction between Action Status and Valency was not significant. 

```{r city-acceptability-other-aov-follow-up-valency}

dat.aov.social.type.token.sequential.acceptability.other.followup.valency <- 
    dat.social.type.token.sequential.m %>% 
    dplyr::filter(scoring == "raw") %>% 
    dplyr::filter(question == "third.party.acceptability") %>% 
    dplyr::group_by(myValence) %>% 
    tidyr::nest() %>% 
    # data is the column created by nest
    dplyr::mutate(aov =  map(data,
                             ~ aov(
                                 rating ~ myQueriedActionStatus + 
                                     Error (filename/(myQueriedActionStatus)), 
                                 data = .x) %>% 
                                 report.aov(.correct.for.repeated.tests = FALSE,
                                            .return.df = TRUE,
                                            .print.results = FALSE)
    )) %>% 
    dplyr::select(-data) %>% 
    unnest %>% 
    dplyr::select(-model.name)


```

As shown in Table \ref{tab:city-acceptability-other-aov-show}, separate ANOVAs for each valency revealed a strong main effect of Action Status for all scenarios, though the effect size for neutral actions was somewhat stronger. 



```{r city-acceptability-other-aov-follow-up-action-status}
v.myQueriedActionStatuses <- levels2(dat.social.type.token.sequential.m$myQueriedActionStatus) %>% 
    rev

dat.aov.social.type.token.sequential.acceptability.other.followup.actionStatus <- 
    purrr::map(v.myQueriedActionStatuses,
               ~ dat.social.type.token.sequential.m %>%
                   dplyr::ungroup() %>% 
                   dplyr::filter(scoring == "raw") %>% 
                   dplyr::filter(question == "third.party.acceptability") %>% 
                   dplyr::mutate(myQueriedActionStatus.excluded = .x, .before = 1) %>% 
                   dplyr::filter(myQueriedActionStatus != myQueriedActionStatus.excluded)) %>% 
    dplyr::bind_rows() %>% 
    dplyr::group_by(myQueriedActionStatus.excluded) %>% 
    tidyr::nest() %>% 
    dplyr::mutate(aov =  map(data,
                             ~ aov(
                                 rating ~ myQueriedActionStatus * myValence +
                                     Error (filename/(myQueriedActionStatus)),
                                 data = .x) %>%
                                 report.aov(.correct.for.repeated.tests = FALSE,
                                            .return.df = TRUE,
                                            .print.results = FALSE))) %>%
    dplyr::select(-data) %>%
    tidyr::unnest() %>%
    dplyr::mutate(myQueriedActionStatus =  str_c (v.myQueriedActionStatuses[!(v.myQueriedActionStatuses %in% myQueriedActionStatus.excluded)], collapse = " vs. "), .before = 1) %>%
    dplyr::ungroup() %>%
    dplyr::select(-myQueriedActionStatus.excluded, -model.name) 



    
```    
Finally, Table \ref{tab:city-acceptability-other-aov-show} shows separate two way ANOVAs leaving out one of the Action Statuses. In all ANOVAs, we observed the expected main effect of Valency. We also observed a main effect of Action Status for all comparisons, suggesting that both an increased token frequency and an increased type frequency affect first party acceptability. 

Finally, the interactions between Action Status and Valency failed to reach significance.

```{r city-acceptability-other-aov-show}

if (!is.null (aov.social.type.token.sequential.acceptability.other.ez.sphericity)){
    warning ("There were sphericity corrections available that you ignored, do something about them.")    
}

dplyr::bind_rows(
    # Overall anova
    dat.aov.social.type.token.sequential.acceptability.other %>% 
        dplyr::mutate(model.type = "Overall"),
    
    # Follow-up valency
    dat.aov.social.type.token.sequential.acceptability.other.followup.valency %>% 
        dplyr::mutate(model.type = "Follow-up of valency") %>% 
        tidyr::unite(model.type, model.type, myValence, sep = ": "),
    
    # Follow-up action status
    dat.aov.social.type.token.sequential.acceptability.other.followup.actionStatus %>%
        dplyr::mutate(model.type = "Follow-up of Action Status") %>% 
        tidyr::unite(model.type, model.type, myQueriedActionStatus, sep = ": "),
) %>%  
    setNames(replace_default_column_labels(names (.))) %>%
    kable.packed("model.type",
                  caption = "ANOVA for third-person acceptability. The data combines male and female participants. (Top) Overall ANOVA. (Middle) Differences between frequency conditions separately for each valency for first person acceptability for all participants. (Bottom). Differences for each frequency conditions separately for first person acceptability for all participants.",
                  booktabs = TRUE, escape = FALSE) %>%
            kable_styling(latex_options =
                              c("hold_position", "striped", "scale_down")) %>%
    kableExtra::kable_classic_2()

```



`r clearpage()`

### First-party acceptability

```{r city-acceptability-self-sw}

#get.lambda.trans 

dat.social.type.token.sequential.acceptability.self.sw <- 
    calculate.shapiro.wilk.test.for.cells(
        dat.social.type.token.sequential.m %>% 
            dplyr::filter(scoring == "raw") %>% 
            dplyr::filter(question == "first.party.acceptablity"),
        c("myValence",
          "myQueriedActionStatus"),
        "rating")

dat.social.type.token.sequential.acceptability.self.sw %>% 
    kable (caption = "SW acceptability for participants themselves", booktabs = TRUE, escape = FALSE) %>% 
    kableExtra::kable_classic_2()
```

As shown in Table \ref{tab:city-acceptability-self-sw}, a number of cells deviated from normality. TODO: TRY TO HEAL IT BY TRANSFORMING


```{r city-tyacceptability-self-aov-calculate}

aov.social.type.token.sequential.acceptability.self <- aov(
    rating ~ myQueriedActionStatus * myValence + 
        Error (filename/(myQueriedActionStatus)), 
    data = dat.social.type.token.sequential.m %>% 
        dplyr::filter(scoring == "raw") %>% 
        dplyr::filter(question == "first.party.acceptablity"))

dat.aov.social.type.token.sequential.acceptability.self <- report.aov(aov.social.type.token.sequential.acceptability.self,
           .correct.for.repeated.tests = FALSE,
           .return.df = TRUE,
           .print.results = FALSE) %>%
    dplyr::select(-c("model.name"))

```

```{r city-acceptability-self-aov-ez-calculate}
aov.social.type.token.sequential.acceptability.self.ez <- ezANOVA(
    data = dat.social.type.token.sequential.m %>% 
        dplyr::filter(scoring == "raw") %>% 
        dplyr::filter(question == "first.party.acceptablity"),
    dv = .(rating),
    wid = .(filename),
    between = .(myValence),
    within = .(myQueriedActionStatus),
    detailed = TRUE,
    type = 3)

aov.social.type.token.sequential.acceptability.self.ez.sphericity <- 
    extract.sphericity.from.ezANOVA(aov.social.type.token.sequential.acceptability.self.ez)

```

As shown in Table \ref{tab:city-acceptability-self-aov-show}, we observed the expected main effect of Valency on first-party acceptability. Further, we observerd a main effect of Action Status as well as an interaction between Action Status and Valency. 


```{r city-acceptability-self-aov-follow-up-valency}
dat.aov.social.type.token.sequential.acceptability.self.followup.valency <- 
dat.social.type.token.sequential.m %>% 
    dplyr::filter(scoring == "raw") %>% 
    dplyr::filter(question == "first.party.acceptablity") %>% 
    dplyr::group_by(myValence) %>% 
    tidyr::nest() %>% 
    # data is the column created by nest
    dplyr::mutate(aov =  map(data,
                             ~ aov(
                                 rating ~ myQueriedActionStatus + 
                                     Error (filename/(myQueriedActionStatus)), 
                                 data = .x) %>% 
                                 report.aov(.correct.for.repeated.tests = FALSE,
                                            .return.df = TRUE,
                                            .print.results = FALSE)
    )) %>% 
    dplyr::select(-data) %>% 
    unnest %>% 
    dplyr::select(-model.name)



```

As shown in Table \ref{tab:city-acceptability-self-aov-show}, separate ANOVAs for each valency revealed a strong main effect of Action Status for neutral scenarios, a weaker one for good scenarios, and none for bad scenarios. This is also expected, as the moral acceptability of neutral scenarios should be more malleable. 


```{r city-acceptability-self-aov-follow-up-action-status}
v.myQueriedActionStatuses <- levels2(dat.social.type.token.sequential.m$myQueriedActionStatus) %>% 
    rev

dat.aov.social.type.token.sequential.acceptability.self.followup.actionStatus <- 
    purrr::map(v.myQueriedActionStatuses,
               ~ dat.social.type.token.sequential.m %>%
                   dplyr::ungroup() %>% 
                   dplyr::filter(scoring == "raw") %>% 
                   dplyr::filter(question == "first.party.acceptablity") %>% 
                   dplyr::mutate(myQueriedActionStatus.excluded = .x, .before = 1) %>% 
                   dplyr::filter(myQueriedActionStatus != myQueriedActionStatus.excluded)) %>% 
    dplyr::bind_rows() %>% 
    dplyr::group_by(myQueriedActionStatus.excluded) %>% 
    tidyr::nest() %>% 
    dplyr::mutate(aov =  map(data,
                             ~ aov(
                                 rating ~ myQueriedActionStatus * myValence +
                                     Error (filename/(myQueriedActionStatus)),
                                 data = .x) %>%
                                 report.aov(.correct.for.repeated.tests = FALSE,
                                            .return.df = TRUE,
                                            .print.results = FALSE))) %>%
    dplyr::select(-data) %>%
    tidyr::unnest() %>%
    dplyr::mutate(myQueriedActionStatus =  str_c (v.myQueriedActionStatuses[!(v.myQueriedActionStatuses %in% myQueriedActionStatus.excluded)], collapse = " vs. "), .before = 1) %>%
    dplyr::ungroup() %>%
    dplyr::select(-myQueriedActionStatus.excluded, -model.name) 



    

```    
Finally, Table \ref{tab:city-acceptability-self-aov-show} shows separate two way ANOVAs leaving out one of the Action Statuses. In all ANOVAs, we observed the expected main effect of Valency. We also observed a main effect of Action Status for all comparisons, suggesting that both an increased token frequency and an increased type frequency affect first party acceptability. 

Finally, the interaction between Action Status and Valency failed to reach significance only when single occurrence actions were compare to low type frequency actions, but was significant when single occurrence actions were compared to high Type Frequency actions and when the other two frequency conditions were compared. We further investigate this by simultaneous restricting the Action Status and the Valency.


```{r city-acceptability-self-aov-show}

if (!is.null (aov.social.type.token.sequential.acceptability.self.ez.sphericity)){
    warning ("There were sphericity corrections available that you ignored, do something about them.")    
}

dplyr::bind_rows(
    # Overall anova
    dat.aov.social.type.token.sequential.acceptability.self %>% 
        dplyr::mutate(model.type = "Overall"),
    
    # Follow-up valency
    dat.aov.social.type.token.sequential.acceptability.self.followup.valency %>% 
        dplyr::mutate(model.type = "Follow-up of valency") %>% 
        tidyr::unite(model.type, model.type, myValence, sep = ": "),
    
    # Follow-up action status
    dat.aov.social.type.token.sequential.acceptability.self.followup.actionStatus %>%
        dplyr::mutate(model.type = "Follow-up of Action Status") %>% 
        tidyr::unite(model.type, model.type, myQueriedActionStatus, sep = ": "),
) %>%  
    setNames(replace_default_column_labels(names (.))) %>%
    kable.packed("model.type",
                  caption = "ANOVA for first-person acceptability. The data combines male and female participants. (Top) Overall ANOVA. (Middle) Differences between frequency conditions separately for each valency for first person acceptability for all participants. (Bottom). Differences for each frequency conditions separately for first person acceptability for all participants.",
                  booktabs = TRUE, escape = FALSE) %>%
            kable_styling(latex_options =
                              c("hold_position", "striped", "scale_down")) %>%
    kableExtra::kable_classic_2()

```

  
```{r city-acceptability-self-aov-follow-up-valency-action-status}
tidyr::expand_grid(myValence = c("bad", "neutral", "good"),
                   myQueriedActionStatus.excluded = v.myQueriedActionStatuses) %>% 
    purrr::pmap_df(~ dat.social.type.token.sequential.m %>%
                                             dplyr::ungroup() %>% 
                                             dplyr::filter(scoring == "raw") %>% 
                                             dplyr::filter(question == "first.party.acceptablity") %>% 
                                             dplyr::filter(myValence == ..1) %>% 
                                             dplyr::mutate(myQueriedActionStatus.excluded = ..2, .before = 1) %>% 
                                             dplyr::filter(myQueriedActionStatus != myQueriedActionStatus.excluded)) %>% 
    dplyr::group_by(myValence, myQueriedActionStatus.excluded) %>% 
    tidyr::nest()  %>% 
    dplyr::mutate(aov =  map(data,
                             ~ aov(
                                 rating ~ myQueriedActionStatus +
                                     Error (filename/(myQueriedActionStatus)),
                                 data = .x) %>%
                                 report.aov(.correct.for.repeated.tests = FALSE,
                                            .return.df = TRUE,
                                            .print.results = FALSE))) %>%
    dplyr::select(-data) %>%
    tidyr::unnest() %>%
    dplyr::mutate(myQueriedActionStatus =  str_c (v.myQueriedActionStatuses[!(v.myQueriedActionStatuses %in% myQueriedActionStatus.excluded)], collapse = " vs. "), .before = 1) %>%
    dplyr::ungroup() %>%
    dplyr::select(-myQueriedActionStatus.excluded) %>%
    tidyr::unite(pack.col, myValence, myQueriedActionStatus, sep = " - ") %>% 
    dplyr::select(-model.name) %>% 
    kable.packed ("pack.col",
                  caption="Differences for each frequency conditions separately for first person acceptability for all participants.", booktabs = TRUE, escape = FALSE) %>%
    kable_styling(latex_options =
                      c("hold_position")) %>%
    kableExtra::kable_classic_2()


    
```    
  
`r clearpage()`


## Difference scores
```{r city-prepare-diff-scores-raw}
dat.social.type.token.sequential.m.d <- dat.social.type.token.sequential.m.wide %>% 
    dplyr::ungroup() %>% 
    tidyr::pivot_longer(starts_with(fixed ("d.")),
                        names_to = "Contrast",
                        values_to = "d") 

# 2 x scoring
# 3 x questions
# (against single: 2 x scores + high vs. low: 1 score)
if(nrow(dat.social.type.token.sequential.m.wide) * 2 * 3 * 3 !=  nrow(dat.social.type.token.sequential.m.d)){
    stop("Check the creation of difference scores")
}


dat.social.type.token.sequential.m.d <- dplyr::bind_rows(
    # We need to separate them as there is no myQueriedActionStatus for the difference scores comparing 
    # the high and low frequency condition 
    
    dat.social.type.token.sequential.m.d %>% 
        dplyr::filter(str_starts(Contrast, "d.vs.single", negate = FALSE)) %>% 
        tidyr::separate_wider_delim(Contrast,
                                    delim = "_",
                                    names = c("Contrast", "myQueriedActionStatus", "question", "scoring"), 
                                    too_few = "error"),
    

    dat.social.type.token.sequential.m.d %>% 
        dplyr::filter(str_starts(Contrast, "d.vs.single", negate = TRUE)) %>%
        tidyr::separate_wider_delim(Contrast,
                                    delim = "_",
                                    names = c("Contrast", "question", "scoring"), 
                                    too_few = "error")
)

```


```{r city-plot-difference-vs-single-raw, fig.cap = "Raw difference scores vs. single occurrence actions"}

dat.social.type.token.sequential.m.d %>% 
    dplyr::filter(scoring == "raw") %>% 
    dplyr::filter(Contrast == "d.vs.single") %>% 
    dplyr::mutate (question = str_replace_all(question, fixed ("."), " ")) %>% 
    dplyr::mutate (question = str_wrap(question, 20)) %>% 
    ggplot (aes (x = myQueriedActionStatus, y = d)) +
        theme_light(14) +
    theme (axis.title.x = element_blank(),
           axis.text.x = element_text(angle = 35, vjust = .5, hjust=.5)) + 
    ylab ("Difference score (raw)") + 
    geom_violin() +
    geom_dotplot(binaxis='y', stackdir='center', dotsize=1) +
    stat_summary(fun.data=mean_se, 
                 geom="pointrange", color="red") +
    geom_hline(yintercept=0, linetype = "dotted") +
    #scale_x_discrete(labels = c("Pre-segmented", "Continuous (1)", "Continuous (2)"))
    facet_grid(question ~ myValence)




```

```{r city-print-difference-vs-single-raw}

dat.social.type.token.sequential.m.d %>% 
    dplyr::filter(scoring == "raw") %>% 
    dplyr::filter(Contrast == "d.vs.single") %>% 
    dplyr::mutate (question = str_replace_all(question, fixed ("."), " ")) %>% 
    dplyr::group_by(question, myValence, myQueriedActionStatus) %>% 
    dplyr::summarize(N = n(),
                     M = mean(d),
                     SE = se(d),
                     cohen.d = M/sd(d),
                     p = wilcox.p(d, 0)) %>% 
    kable.packed("question", 
                 caption = "Descriptive for the difference scores against the single occurrence condition using the untransformed data. The p value reflects a Wilcoxon test against zero.",
                 col.names = c("Valency", "Action Status", "N", "M", "SE", "Cohen's d", "p"),
                 booktabs = TRUE,
                 longtable = TRUE) %>% 
    kableExtra::kable_styling(latex_options = "repeat_header") %>% 
    kableExtra::kable_classic_2()
    
```


```{r plot-difference-high-vs-low-type-frequency-raw, fig.cap = "Raw difference scores high vs. low type frequency actions"}

dat.social.type.token.sequential.m.d %>% 
    dplyr::filter(scoring == "raw") %>% 
    dplyr::filter(Contrast != "d.vs.single") %>% 
    dplyr::mutate (question = str_replace_all(question, fixed ("."), " ")) %>% 
    dplyr::mutate (question = str_wrap(question, 20)) %>% 
    ggplot (aes (x = question, y = d)) +
        theme_light(14) +
    theme (axis.title.x = element_blank(),
           axis.text.x = element_text(angle = 35, vjust = .5, hjust=.5)) + 
    ylab ("Difference score (raw)") + 
    geom_violin() +
    geom_dotplot(binaxis='y', stackdir='center', dotsize=1) +
    stat_summary(fun.data=mean_se, 
                 geom="pointrange", color="red") +
    geom_hline(yintercept=0, linetype = "dotted") +
    #scale_x_discrete(labels = c("Pre-segmented", "Continuous (1)", "Continuous (2)"))
    facet_grid(. ~ myValence)




```

```{r city-print-difference-high-vs-low-type-frequency-raw}

dat.social.type.token.sequential.m.d %>% 
    dplyr::filter(scoring == "raw") %>% 
    dplyr::filter(Contrast != "d.vs.single") %>% 
    dplyr::mutate (question = str_replace_all(question, fixed ("."), " ")) %>% 
    dplyr::group_by(question, myValence) %>% 
    dplyr::summarize(N = n(),
                     M = mean(d),
                     SE = se(d),
                     cohen.d = M/sd(d),
                     p = wilcox.p(d, 0)) %>% 
    kable.packed("question", 
                 caption = "Descriptive for the difference scores against the single occurrence condition using the untransformed data. The p value reflects a Wilcoxon test against zero.",
                 col.names = c("Valency", "N", "M", "SE", "Cohen's d", "p"),
                 booktabs = TRUE,
                 longtable = TRUE) %>% 
    kableExtra::kable_styling(latex_options = "repeat_header") %>% 
    kableExtra::kable_classic_2()
    
```

### Prevalence 

```{r city-prevalence-d-vs-single-sw}

#get.lambda.trans 

dat.social.type.token.sequential.prevalence.d.vs.single.sw <- 
    calculate.shapiro.wilk.test.for.cells(
        dat.social.type.token.sequential.m.d  %>% 
            dplyr::filter(scoring == "raw") %>% 
            dplyr::filter(question == "prevalence") %>% 
            dplyr::filter(Contrast == "d.vs.single"),
        c("myValence",
          "myQueriedActionStatus"),
        "d")

dat.social.type.token.sequential.prevalence.d.vs.single.sw %>% 
    kable (caption = "SW acceptability for participants themselves", booktabs = TRUE, escape = FALSE) %>% 
    kableExtra::kable_classic_2()


 
```

As shown in Table \ref{tab:city-prevalence-d-vs-single-sw}, no of cells deviated from normality. 



```{r city-prevalence-d-vs-single-aov-calculate}

aov.social.type.token.sequential.prevalence.d.vs.single <- aov(
    d ~ myQueriedActionStatus * myValence + 
        Error (filename/(myQueriedActionStatus)), 
    data = dat.social.type.token.sequential.m.d %>% 
        dplyr::filter(scoring == "raw") %>%
        dplyr::filter(Contrast == "d.vs.single") %>% 
        dplyr::filter(question == "prevalence"))

dat.aov.social.type.token.sequential.prevalence.d.vs.single <- report.aov(aov.social.type.token.sequential.prevalence.d.vs.single,
           .correct.for.repeated.tests = FALSE,
           .return.df = TRUE,
           .print.results = FALSE) %>%
    dplyr::select(-c("model.name"))

```


```{r city-prevalence-d-vs-single-aov-ez-calculate}
aov.social.type.token.sequential.prevalence.d.vs.single.ez <- ezANOVA(
    data = dat.social.type.token.sequential.m.d %>% 
        dplyr::filter(scoring == "raw") %>% 
        dplyr::filter(Contrast == "d.vs.single") %>% 
        dplyr::filter(question == "prevalence"),
    dv = .(d),
    wid = .(filename),
    between = .(myValence),
    within = .(myQueriedActionStatus),
    detailed = TRUE,
    type = 3)

aov.social.type.token.sequential.prevalence.d.vs.single.ez.sphericity <- 
    extract.sphericity.from.ezANOVA(aov.social.type.token.sequential.prevalence.d.vs.single.ez)

```
As shown in Table \ref{tab:city-prevalence-d-vs-single-aov-show}, we observed no main effect of Valency on the difference score against single occurrence actions for prevalence. We observed a main effect of Action Status as well as a marginal interaction between Action Status and Valency. 

```{r city-prevalence-d-vs-single-aov-follow-up-valency}
dat.aov.social.type.token.sequential.prevalence.d.vs.single.followup.valency <- 
    dat.social.type.token.sequential.m.d %>% 
    dplyr::filter(scoring == "raw") %>% 
    dplyr::filter(Contrast == "d.vs.single") %>% 
    dplyr::filter(question == "prevalence") %>% 
    dplyr::group_by(myValence) %>% 
    tidyr::nest() %>% 
    # data is the column created by nest
    dplyr::mutate(aov =  map(data,
                             ~ aov(
                                 d ~ myQueriedActionStatus + 
                                     Error (filename/(myQueriedActionStatus)), 
                                 data = .x) %>% 
                                 report.aov(.correct.for.repeated.tests = FALSE,
                                            .return.df = TRUE,
                                            .print.results = FALSE)
    )) %>% 
    dplyr::select(-data) %>% 
    unnest %>% 
    dplyr::select(-model.name) 

```

As shown in Table \ref{tab:city-prevalence-d-vs-single-aov-show}, separate ANOVAs for each valency revealed a strong main effect of Action Status only for all three valencies.


```{r city-prevalence-d-vs-single-aov-follow-up-action-status}

dat.aov.social.type.token.sequential.prevalence.d.vs.single.followup.actionStatus <- 
    dat.social.type.token.sequential.m.d %>% 
    dplyr::filter(scoring == "raw") %>% 
    dplyr::filter(Contrast == "d.vs.single") %>% 
    dplyr::filter(question == "prevalence") %>% 
    dplyr::group_by(myQueriedActionStatus) %>% 
    dplyr::group_modify(~ aov(
        d ~ myValence,
        data = .x) %>%
            report.aov(.correct.for.repeated.tests = FALSE,
                       .return.df = TRUE,
                       .print.results = FALSE)) %>% 
    dplyr::select(-model.name) 



```    

Finally, Table \ref{tab:city-prevalence-d-vs-single-aov-show} shows separate ANOVAs for each Action Status. The main effect of valency was significant only for high type frequency scenarios. 

```{r city-prevalence-d-vs-single-aov-show}

if (!is.null (aov.social.type.token.sequential.prevalence.d.vs.single.ez.sphericity)){
    warning ("There were sphericity corrections available that you ignored, do something about them.")    
}

dplyr::bind_rows(
    # Overall anova
    dat.aov.social.type.token.sequential.prevalence.d.vs.single %>% 
        dplyr::mutate(model.type = "Overall"),
    
    # Follow-up valency
    dat.aov.social.type.token.sequential.prevalence.d.vs.single.followup.valency %>% 
        dplyr::mutate(model.type = "Follow-up of valency") %>% 
        tidyr::unite(model.type, model.type, myValence, sep = ": "),
    
    # Follow-up action status
    dat.aov.social.type.token.sequential.prevalence.d.vs.single.followup.actionStatus %>%
        dplyr::mutate(model.type = "Follow-up of Action Status") %>% 
        tidyr::unite(model.type, model.type, myQueriedActionStatus, sep = ": "),
) %>%  
    setNames(replace_default_column_labels(names (.))) %>%
    kable.packed("model.type",
                  caption = "ANOVA for difference scores comparing each frequency condition to the single occurrence condition. first-person acceptability. The data combines male and female participants. (Top) Overall ANOVA. (Middle) Differences between frequency conditions separately for each valency for first person acceptability for all participants. (Bottom). Differences for each frequency conditions separately for first person acceptability for all participants.",
                  booktabs = TRUE, escape = FALSE) %>%
            kable_styling(latex_options =
                              c("hold_position", "striped")) %>%
    kableExtra::kable_classic_2()


```


#### Difference scores comparing high type frequency against low type frequency

```{r city-prevalence-d-high-vs-low-tf-sw}

#get.lambda.trans 

dat.social.type.token.sequential.prevalence.d.high.vs.low.tf.sw <- 
    calculate.shapiro.wilk.test.for.cells(
        dat.social.type.token.sequential.m.d  %>% 
            dplyr::filter(scoring == "raw") %>% 
            dplyr::filter(Contrast == "d.high.vs.low.TypeFreq"),
        c("myValence"),
        "d")

dat.social.type.token.sequential.prevalence.d.high.vs.low.tf.sw %>% 
    kable (caption = "SW acceptability for participants themselves for high vs. low difference scores", booktabs = TRUE, escape = FALSE) %>% 
    kableExtra::kable_classic_2()


 
```

As shown in Table \ref{tab:city-prevalence-d-high-vs-low-tf-sw}, a number of cells deviated from normality. TODO: TRY TO HEAL IT BY TRANSFORMING


```{r city-typrevalence-d-high-vs-low-tf-aov-calculate}

aov.social.type.token.sequential.prevalence.d.high.vs.low.tf <- aov(
    d ~  myValence, 
    data = dat.social.type.token.sequential.m.d %>% 
        dplyr::filter(scoring == "raw") %>%
        dplyr::filter(Contrast == "d.high.vs.low.TypeFreq") %>% 
        dplyr::filter(question == "prevalence"))

dat.aov.social.type.token.sequential.prevalence.d.high.vs.low.tf <- report.aov(aov.social.type.token.sequential.prevalence.d.high.vs.low.tf,
           .correct.for.repeated.tests = FALSE,
           .return.df = TRUE,
           .print.results = FALSE) %>%
    dplyr::select(-c("model.name"))

```


```{r city-prevalence-d-high-vs-low-tf-aov-ez-calculate}
aov.social.type.token.sequential.prevalence.d.high.vs.low.tf.ez <- ezANOVA(
    data = dat.social.type.token.sequential.m.d %>% 
        dplyr::filter(scoring == "raw") %>% 
        dplyr::filter(Contrast == "d.high.vs.low.TypeFreq") %>% 
        dplyr::filter(question == "prevalence"),
    dv = .(d),
    wid = .(filename),
    between = .(myValence),
    within = NULL,
    detailed = TRUE,
    type = 3)

aov.social.type.token.sequential.prevalence.d.high.vs.low.tf.ez.sphericity <- 
    extract.sphericity.from.ezANOVA(aov.social.type.token.sequential.prevalence.d.high.vs.low.tf.ez)

```
As shown in Table \ref{tab:city-prevalence-d-high-vs-low-tf-aov-show}, we observed a marginal main effect of Valency on difference scores for first-party acceptability. 


```{r city-prevalence-d-high-vs-low-tf-aov-follow-up-valency}

v.valencies <- levels(dat.social.type.token.sequential.m.d$myValence)

dat.aov.social.type.token.sequential.prevalence.d.high.vs.low.tf.followup.valency <- 
    purrr::map(v.valencies,
               ~ dat.social.type.token.sequential.m.d %>% 
                   dplyr::ungroup() %>% 
                   dplyr::filter(scoring == "raw") %>% 
                   dplyr::filter(Contrast == "d.high.vs.low.TypeFreq") %>% 
                   dplyr::filter(question == "prevalence") %>% 
                   dplyr::mutate(myValence.excluded = .x, .before = 1) %>% 
                   dplyr::filter(myValence != myValence.excluded)) %>% 
    dplyr::bind_rows() %>% 
    dplyr::group_by(myValence.excluded) %>% 
    tidyr::nest() %>% 
    # data is the column created by nest
    dplyr::mutate(aov =  map(data,
                             ~ aov(
                                 d ~ myValence,
                                 data = .x) %>% 
                                 report.aov(.correct.for.repeated.tests = FALSE,
                                            .return.df = TRUE,
                                            .print.results = FALSE)
    )) %>% 
    dplyr::select(-data) %>% 
    unnest(cols = c(aov)) %>% 
    dplyr::mutate(myValence =  str_c (v.valencies[!(v.valencies %in% myValence.excluded)], 
                                      collapse = " vs. "), 
                  .before = 1) %>% 
    dplyr::ungroup() %>% 
    dplyr::select(-model.name, -myValence.excluded) 


```
As shown in Table \ref{tab:city-prevalence-d-high-vs-low-tf-aov-show}, separate ANOVAs for each valency pair revealed a strong main effect of Action Status only for the bad vs. good comparison the the neutral vs. good comparison. 

```{r city-prevalence-d-high-vs-low-tf-aov-show}

if (!is.null (aov.social.type.token.sequential.prevalence.d.high.vs.low.tf.ez.sphericity)){
    warning ("There were sphericity corrections available that you ignored, do something about them.")    
}


dplyr::bind_rows(
    # Overall anova
    dat.aov.social.type.token.sequential.prevalence.d.high.vs.low.tf %>% 
        dplyr::mutate(model.type = "Overall"),
    
    # By valencyy
    dat.aov.social.type.token.sequential.prevalence.d.high.vs.low.tf.followup.valency %>% 
        dplyr::mutate(model.type = "By valency")
) %>% 
    dplyr::select(model.type, myValence, effect, everything()) %>% 
    setNames(replace_default_column_labels(names (.))) %>%
    kable.packed("model.type",
                 caption = "ANOVA for difference scores comparing the high vs low type frequency conditions for prevalence. The data combines male and female participants. (Top) Overall ANOVA. (Middle) Differences between frequency conditions separately for each valency for first person acceptability for all participants. (Bottom). Differences for each frequency conditions separately for first person acceptability for all participants.",
                 booktabs = TRUE, escape = FALSE) %>%
    kable_styling(latex_options =
                      c("hold_position", "striped")) %>%
    kableExtra::kable_classic_2()


```


`r clearpage()`


### Third-party acceptability

#### Difference scores against single actions

```{r city-acceptability-other-d-vs-single-sw}

#get.lambda.trans 

dat.social.type.token.sequential.acceptability.other.d.vs.single.sw <- 
    calculate.shapiro.wilk.test.for.cells(
        dat.social.type.token.sequential.m.d  %>% 
            dplyr::filter(scoring == "raw") %>% 
            dplyr::filter(question == "third.party.acceptability") %>% 
            dplyr::filter(Contrast == "d.vs.single"),
        c("myValence",
          "myQueriedActionStatus"),
        "d")

dat.social.type.token.sequential.acceptability.other.d.vs.single.sw %>% 
    kable (caption = "SW acceptability for participants themselves", booktabs = TRUE, escape = FALSE) %>% 
    kableExtra::kable_classic_2()


 
```

As shown in Table \ref{tab:city-acceptability-other-d-vs-single-sw}, a number of cells deviated from normality. TODO: TRY TO HEAL IT BY TRANSFORMING


```{r city-acceptability-other-d-vs-single-aov-calculate}

aov.social.type.token.sequential.acceptability.other.d.vs.single <- aov(
    d ~ myQueriedActionStatus * myValence + 
        Error (filename/(myQueriedActionStatus)), 
    data = dat.social.type.token.sequential.m.d %>% 
        dplyr::filter(scoring == "raw") %>%
        dplyr::filter(Contrast == "d.vs.single") %>% 
        dplyr::filter(question == "third.party.acceptability"))

dat.aov.social.type.token.sequential.acceptability.other.d.vs.single <- report.aov(aov.social.type.token.sequential.acceptability.other.d.vs.single,
           .correct.for.repeated.tests = FALSE,
           .return.df = TRUE,
           .print.results = FALSE) %>%
    dplyr::select(-c("model.name"))

```


```{r city-acceptability-other-d-vs-single-aov-ez-calculate}
aov.social.type.token.sequential.acceptability.other.d.vs.single.ez <- ezANOVA(
    data = dat.social.type.token.sequential.m.d %>% 
        dplyr::filter(scoring == "raw") %>% 
        dplyr::filter(Contrast == "d.vs.single") %>% 
        dplyr::filter(question == "third.party.acceptability"),
    dv = .(d),
    wid = .(filename),
    between = .(myValence),
    within = .(myQueriedActionStatus),
    detailed = TRUE,
    type = 3)

aov.social.type.token.sequential.acceptability.other.d.vs.single.ez.sphericity <- 
    extract.sphericity.from.ezANOVA(aov.social.type.token.sequential.acceptability.other.d.vs.single.ez)

```
As shown in Table \ref{tab:city-acceptability-other-d-vs-single-aov-show}, we observed no main effect of Valency on the difference score against single occurrence actions for first-party acceptability. , we observed a main effect of Action Status as well as an interaction between Action Status and Valency. 


```{r city-acceptability-other-d-vs-single-aov-follow-up-valency}
dat.aov.social.type.token.sequential.acceptability.other.d.vs.single.followup.valency <- 
    dat.social.type.token.sequential.m.d %>% 
    dplyr::filter(scoring == "raw") %>% 
    dplyr::filter(Contrast == "d.vs.single") %>% 
    dplyr::filter(question == "third.party.acceptability") %>% 
    dplyr::group_by(myValence) %>% 
    tidyr::nest() %>% 
    # data is the column created by nest
    dplyr::mutate(aov =  map(data,
                             ~ aov(
                                 d ~ myQueriedActionStatus + 
                                     Error (filename/(myQueriedActionStatus)), 
                                 data = .x) %>% 
                                 report.aov(.correct.for.repeated.tests = FALSE,
                                            .return.df = TRUE,
                                            .print.results = FALSE)
    )) %>% 
    dplyr::select(-data) %>% 
    unnest %>% 
    dplyr::select(-model.name) 

```

As shown in Table \ref{tab:city-acceptability-other-d-vs-single-aov-show}, separate ANOVAs for each valency revealed a strong main effect of Action Status only for neutral scenarios. The main effect was not significant for good or bad scenarios. Again, this is redundant with the direct difference scores.




```{r city-acceptability-other-d-vs-single-aov-follow-up-action-status}

dat.aov.social.type.token.sequential.acceptability.other.d.vs.single.followup.actionStatus <- 
    dat.social.type.token.sequential.m.d %>% 
    dplyr::filter(scoring == "raw") %>% 
    dplyr::filter(Contrast == "d.vs.single") %>% 
    dplyr::filter(question == "third.party.acceptability") %>% 
    dplyr::group_by(myQueriedActionStatus) %>% 
    dplyr::group_modify(~ aov(
        d ~ myValence,
        data = .x) %>%
            report.aov(.correct.for.repeated.tests = FALSE,
                       .return.df = TRUE,
                       .print.results = FALSE)) %>% 
    dplyr::select(-model.name) 




```    
Finally, Table \ref{tab:city-acceptability-other-d-vs-single-aov-show} shows separate ANOVAs for each Action Status. The main effect of valency was marginal;ly significant only for high type frequency scenarios. 


```{r city-acceptability-other-d-vs-single-aov-show}

if (!is.null (aov.social.type.token.sequential.acceptability.other.d.vs.single.ez.sphericity)){
    warning ("There were sphericity corrections available that you ignored, do something about them.")    
}

dplyr::bind_rows(
    # Overall anova
    dat.aov.social.type.token.sequential.acceptability.other.d.vs.single %>% 
        dplyr::mutate(model.type = "Overall"),
    
    # Follow-up valency
    dat.aov.social.type.token.sequential.acceptability.other.d.vs.single.followup.valency %>% 
        dplyr::mutate(model.type = "Follow-up of valency") %>% 
        tidyr::unite(model.type, model.type, myValence, sep = ": "),
    
    # Follow-up action status
    dat.aov.social.type.token.sequential.acceptability.other.d.vs.single.followup.actionStatus %>%
        dplyr::mutate(model.type = "Follow-up of Action Status") %>% 
        tidyr::unite(model.type, model.type, myQueriedActionStatus, sep = ": "),
) %>%  
    setNames(replace_default_column_labels(names (.))) %>%
    kable.packed("model.type",
                  caption = "ANOVA for difference scores comparing each frequency condition to the single occurrence condition. third-person acceptability. The data combines male and female participants. (Top) Overall ANOVA. (Middle) Differences between frequency conditions separately for each valency for first person acceptability for all participants. (Bottom). Differences for each frequency conditions separately for first person acceptability for all participants.",
                  booktabs = TRUE, escape = FALSE) %>%
            kable_styling(latex_options =
                              c("hold_position", "striped")) %>%
    kableExtra::kable_classic_2()


```


#### Difference scores comparing high type frequency against low type frequency

```{r city-acceptability-other-d-high-vs-low-tf-sw}

#get.lambda.trans 

dat.social.type.token.sequential.acceptability.other.d.high.vs.low.tf.sw <- 
    calculate.shapiro.wilk.test.for.cells(
        dat.social.type.token.sequential.m.d  %>% 
            dplyr::filter(scoring == "raw") %>% 
            dplyr::filter(Contrast == "d.high.vs.low.TypeFreq"),
        c("myValence"),
        "d")

dat.social.type.token.sequential.acceptability.other.d.high.vs.low.tf.sw %>% 
    kable (caption = "SW acceptability for participants themselves for high vs. low difference scores", booktabs = TRUE, escape = FALSE) %>% 
    kableExtra::kable_classic_2()


 
```

As shown in Table \ref{tab:city-acceptability-other-d-high-vs-low-tf-sw}, a number of cells deviated from normality. TODO: TRY TO HEAL IT BY TRANSFORMING

```{r city-tyacceptability-other-d-high-vs-low-tf-aov-calculate}

aov.social.type.token.sequential.acceptability.other.d.high.vs.low.tf <- aov(
    d ~  myValence, 
    data = dat.social.type.token.sequential.m.d %>% 
        dplyr::filter(scoring == "raw") %>%
        dplyr::filter(Contrast == "d.high.vs.low.TypeFreq") %>% 
        dplyr::filter(question == "third.party.acceptability"))

dat.aov.social.type.token.sequential.acceptability.other.d.high.vs.low.tf <- report.aov(aov.social.type.token.sequential.acceptability.other.d.high.vs.low.tf,
           .correct.for.repeated.tests = FALSE,
           .return.df = TRUE,
           .print.results = FALSE) %>%
    dplyr::select(-c("model.name"))

```


```{r city-acceptability-other-d-high-vs-low-tf-aov-ez-calculate}
aov.social.type.token.sequential.acceptability.other.d.high.vs.low.tf.ez <- ezANOVA(
    data = dat.social.type.token.sequential.m.d %>% 
        dplyr::filter(scoring == "raw") %>% 
        dplyr::filter(Contrast == "d.high.vs.low.TypeFreq") %>% 
        dplyr::filter(question == "third.party.acceptability"),
    dv = .(d),
    wid = .(filename),
    between = .(myValence),
    within = NULL,
    detailed = TRUE,
    type = 3)

aov.social.type.token.sequential.acceptability.other.d.high.vs.low.tf.ez.sphericity <- 
    extract.sphericity.from.ezANOVA(aov.social.type.token.sequential.acceptability.other.d.high.vs.low.tf.ez)

```
As shown in Table \ref{tab:city-acceptability-other-d-high-vs-low-tf-aov-show}, we observed a marginal main effect of Valency on difference scores for first-party acceptability. 

```{r city-acceptability-other-d-high-vs-low-tf-aov-follow-up-valency}

v.valencies <- levels(dat.social.type.token.sequential.m.d$myValence)

dat.aov.social.type.token.sequential.acceptability.other.d.high.vs.low.tf.followup.valency <- 
    purrr::map(v.valencies,
               ~ dat.social.type.token.sequential.m.d %>% 
                   dplyr::ungroup() %>% 
                   dplyr::filter(scoring == "raw") %>% 
                   dplyr::filter(Contrast == "d.high.vs.low.TypeFreq") %>% 
                   dplyr::filter(question == "third.party.acceptability") %>% 
                   dplyr::mutate(myValence.excluded = .x, .before = 1) %>% 
                   dplyr::filter(myValence != myValence.excluded)) %>% 
    dplyr::bind_rows() %>% 
    dplyr::group_by(myValence.excluded) %>% 
    tidyr::nest() %>% 
    # data is the column created by nest
    dplyr::mutate(aov =  map(data,
                             ~ aov(
                                 d ~ myValence,
                                 data = .x) %>% 
                                 report.aov(.correct.for.repeated.tests = FALSE,
                                            .return.df = TRUE,
                                            .print.results = FALSE)
    )) %>% 
    dplyr::select(-data) %>% 
    unnest(cols = c(aov)) %>% 
    dplyr::mutate(myValence =  str_c (v.valencies[!(v.valencies %in% myValence.excluded)], 
                                      collapse = " vs. "), 
                  .before = 1) %>% 
    dplyr::ungroup() %>% 
    dplyr::select(-model.name, -myValence.excluded) 


```
As shown in Table \ref{tab:city-acceptability-other-d-high-vs-low-tf-aov-show}, separate ANOVAs for each valency pair revealed a strong main effect of Action Status only for the bad vs. good comparison, and a marginal one for the neutral vs. good comparison. 


```{r city-acceptability-other-d-high-vs-low-tf-aov-show}

if (!is.null (aov.social.type.token.sequential.acceptability.other.d.high.vs.low.tf.ez.sphericity)){
    warning ("There were sphericity corrections available that you ignored, do something about them.")    
}


dplyr::bind_rows(
    # Overall anova
    dat.aov.social.type.token.sequential.acceptability.other.d.high.vs.low.tf %>% 
        dplyr::mutate(model.type = "Overall"),
    
    # By valencyy
    dat.aov.social.type.token.sequential.acceptability.other.d.high.vs.low.tf.followup.valency %>% 
        dplyr::mutate(model.type = "By valency")
) %>% 
    dplyr::select(model.type, myValence, effect, everything()) %>% 
        setNames(replace_default_column_labels(names (.))) %>%
        kable.packed("model.type",
                     caption = "ANOVA for difference scores comparing the high vs low type frequency conditions for first-person acceptability. The data combines male and female participants. (Top) Overall ANOVA. (Middle) Differences between frequency conditions separately for each valency for first person acceptability for all participants. (Bottom). Differences for each frequency conditions separately for first person acceptability for all participants.",
                     booktabs = TRUE, escape = FALSE) %>%
    kable_styling(latex_options =
                      c("hold_position", "striped")) %>%
    kableExtra::kable_classic_2()


```


`r clearpage()`

### First-party acceptability
#### Difference scores against single actions

```{r city-acceptability-self-d-vs-single-sw}

#get.lambda.trans 

dat.social.type.token.sequential.acceptability.self.d.vs.single.sw <- 
    calculate.shapiro.wilk.test.for.cells(
        dat.social.type.token.sequential.m.d  %>% 
            dplyr::filter(scoring == "raw") %>% 
            dplyr::filter(question == "first.party.acceptablity") %>% 
            dplyr::filter(Contrast == "d.vs.single"),
        c("myValence",
          "myQueriedActionStatus"),
        "d")

dat.social.type.token.sequential.acceptability.self.d.vs.single.sw %>% 
    kable (caption = "SW acceptability for participants themselves", booktabs = TRUE, escape = FALSE) %>% 
    kableExtra::kable_classic_2()


 
```

As shown in Table \ref{tab:city-acceptability-self-d-vs-single-sw}, a number of cells deviated from normality. TODO: TRY TO HEAL IT BY TRANSFORMING

```{r city-acceptability-self-d-vs-single-aov-calculate}

aov.social.type.token.sequential.acceptability.self.d.vs.single <- aov(
    d ~ myQueriedActionStatus * myValence + 
        Error (filename/(myQueriedActionStatus)), 
    data = dat.social.type.token.sequential.m.d %>% 
        dplyr::filter(scoring == "raw") %>%
        dplyr::filter(Contrast == "d.vs.single") %>% 
        dplyr::filter(question == "first.party.acceptablity"))

dat.aov.social.type.token.sequential.acceptability.self.d.vs.single <- report.aov(aov.social.type.token.sequential.acceptability.self.d.vs.single,
           .correct.for.repeated.tests = FALSE,
           .return.df = TRUE,
           .print.results = FALSE) %>%
    dplyr::select(-c("model.name"))

```


```{r city-acceptability-self-d-vs-single-aov-ez-calculate}
aov.social.type.token.sequential.acceptability.self.d.vs.single.ez <- ezANOVA(
    data = dat.social.type.token.sequential.m.d %>% 
        dplyr::filter(scoring == "raw") %>% 
        dplyr::filter(Contrast == "d.vs.single") %>% 
        dplyr::filter(question == "first.party.acceptablity"),
    dv = .(d),
    wid = .(filename),
    between = .(myValence),
    within = .(myQueriedActionStatus),
    detailed = TRUE,
    type = 3)

aov.social.type.token.sequential.acceptability.self.d.vs.single.ez.sphericity <- 
    extract.sphericity.from.ezANOVA(aov.social.type.token.sequential.acceptability.self.d.vs.single.ez)

```
As shown in Table \ref{tab:city-acceptability-self-d-vs-single-aov-show}, we observed the expected main effect of Valency on first-party acceptability. Further, we observed a main effect of Action Status as well as an interaction between Action Status and Valency. (Not that including the factor Action Status is redundant with the direct difference score below.)

```{r city-acceptability-self-d-vs-single-aov-follow-up-valency}
dat.aov.social.type.token.sequential.acceptability.self.d.vs.single.followup.valency <- 
    dat.social.type.token.sequential.m.d %>% 
    dplyr::filter(scoring == "raw") %>% 
    dplyr::filter(Contrast == "d.vs.single") %>% 
    dplyr::filter(question == "first.party.acceptablity") %>% 
    dplyr::group_by(myValence) %>% 
    tidyr::nest() %>% 
    # data is the column created by nest
    dplyr::mutate(aov =  map(data,
                             ~ aov(
                                 d ~ myQueriedActionStatus + 
                                     Error (filename/(myQueriedActionStatus)), 
                                 data = .x) %>% 
                                 report.aov(.correct.for.repeated.tests = FALSE,
                                            .return.df = TRUE,
                                            .print.results = FALSE)
    )) %>% 
    dplyr::select(-data) %>% 
    unnest %>% 
    dplyr::select(-model.name)



```
As shown in Table \ref{tab:city-acceptability-self-d-vs-single-aov-show}, separate ANOVAs for each valency revealed a strong main effect of Action Status only for neutral scenarios. The main effect was not significant for good or bad scenarios. Again, this is redundant with the direct difference scores.

```{r city-acceptability-self-d-vs-single-aov-follow-up-action-status}

dat.aov.social.type.token.sequential.acceptability.self.d.vs.single.followup.actionStatus <- 
    dat.social.type.token.sequential.m.d %>% 
    dplyr::filter(scoring == "raw") %>% 
    dplyr::filter(Contrast == "d.vs.single") %>% 
    dplyr::filter(question == "first.party.acceptablity") %>% 
    dplyr::group_by(myQueriedActionStatus) %>% 
    dplyr::group_modify(~ aov(
        d ~ myValence,
        data = .x) %>%
            report.aov(.correct.for.repeated.tests = FALSE,
                       .return.df = TRUE,
                       .print.results = FALSE)) %>% 
    dplyr::select(-model.name) 




```    
Finally, Table \ref{tab:city-acceptability-self-d-vs-single-aov-show} shows separate ANOVAs for each Action Status. The main effect of valency was significant only for high type frequency scenarios. 

```{r city-acceptability-self-d-vs-single-aov-show}

if (!is.null (aov.social.type.token.sequential.acceptability.self.d.vs.single.ez.sphericity)){
    warning ("There were sphericity corrections available that you ignored, do something about them.")    
}

dplyr::bind_rows(
    # Overall anova
    dat.aov.social.type.token.sequential.acceptability.self.d.vs.single %>% 
        dplyr::mutate(model.type = "Overall"),
    
    # Follow-up valency
    dat.aov.social.type.token.sequential.acceptability.self.d.vs.single.followup.valency %>% 
        dplyr::mutate(model.type = "Follow-up of valency") %>% 
        tidyr::unite(model.type, model.type, myValence, sep = ": "),
    
    # Follow-up action status
    dat.aov.social.type.token.sequential.acceptability.self.d.vs.single.followup.actionStatus %>%
        dplyr::mutate(model.type = "Follow-up of Action Status") %>% 
        tidyr::unite(model.type, model.type, myQueriedActionStatus, sep = ": "),
) %>%  
    setNames(replace_default_column_labels(names (.))) %>%
    kable.packed("model.type",
                  caption = "ANOVA for difference scores comparing each frequency condition to the single occurrence condition. first-person acceptability. The data combines male and female participants. (Top) Overall ANOVA. (Middle) Differences between frequency conditions separately for each valency for first person acceptability for all participants. (Bottom). Differences for each frequency conditions separately for first person acceptability for all participants.",
                  booktabs = TRUE, escape = FALSE) %>%
            kable_styling(latex_options =
                              c("hold_position", "striped")) %>%
    kableExtra::kable_classic_2()


```

#### Difference scores comparing high type frequency against low type frequency

```{r city-acceptability-self-d-high-vs-low-tf-sw}

#get.lambda.trans 

dat.social.type.token.sequential.acceptability.self.d.high.vs.low.tf.sw <- 
    calculate.shapiro.wilk.test.for.cells(
        dat.social.type.token.sequential.m.d  %>% 
            dplyr::filter(scoring == "raw") %>% 
            dplyr::filter(Contrast == "d.high.vs.low.TypeFreq"),
        c("myValence"),
        "d")

dat.social.type.token.sequential.acceptability.self.d.high.vs.low.tf.sw %>% 
    kable (caption = "SW acceptability for participants themselves for high vs. low difference scores", booktabs = TRUE, escape = FALSE) %>% 
    kableExtra::kable_classic_2()


 
```

As shown in Table \ref{tab:city-acceptability-self-d-high-vs-low-tf-sw}, a number of cells deviated from normality. TODO: TRY TO HEAL IT BY TRANSFORMING


```{r city-tyacceptability-self-d-high-vs-low-tf-aov-calculate}

aov.social.type.token.sequential.acceptability.self.d.high.vs.low.tf <- aov(
    d ~  myValence, 
    data = dat.social.type.token.sequential.m.d %>% 
        dplyr::filter(scoring == "raw") %>%
        dplyr::filter(Contrast == "d.high.vs.low.TypeFreq") %>% 
        dplyr::filter(question == "first.party.acceptablity"))

dat.aov.social.type.token.sequential.acceptability.self.d.high.vs.low.tf <- report.aov(aov.social.type.token.sequential.acceptability.self.d.high.vs.low.tf,
           .correct.for.repeated.tests = FALSE,
           .return.df = TRUE,
           .print.results = FALSE) %>%
    dplyr::select(-c("model.name"))

```


```{r city-acceptability-self-d-high-vs-low-tf-aov-ez-calculate}
aov.social.type.token.sequential.acceptability.self.d.high.vs.low.tf.ez <- ezANOVA(
    data = dat.social.type.token.sequential.m.d %>% 
        dplyr::filter(scoring == "raw") %>% 
        dplyr::filter(Contrast == "d.high.vs.low.TypeFreq") %>% 
        dplyr::filter(question == "first.party.acceptablity"),
    dv = .(d),
    wid = .(filename),
    between = .(myValence),
    within = NULL,
    detailed = TRUE,
    type = 3)

aov.social.type.token.sequential.acceptability.self.d.high.vs.low.tf.ez.sphericity <- 
    extract.sphericity.from.ezANOVA(aov.social.type.token.sequential.acceptability.self.d.high.vs.low.tf.ez)

```
As shown in Table \ref{tab:city-acceptability-self-d-high-vs-low-tf-aov-show}, we observed the expected main effect of Valency on difference scores for first-party acceptability. 


```{r city-acceptability-self-d-high-vs-low-tf-aov-follow-up-valency}

v.valencies <- levels(dat.social.type.token.sequential.m.d$myValence)

dat.aov.social.type.token.sequential.acceptability.self.d.high.vs.low.tf.followup.valency <- 
    purrr::map(v.valencies,
               ~ dat.social.type.token.sequential.m.d %>% 
                   dplyr::ungroup() %>% 
                   dplyr::filter(scoring == "raw") %>% 
                   dplyr::filter(Contrast == "d.high.vs.low.TypeFreq") %>% 
                   dplyr::filter(question == "first.party.acceptablity") %>% 
                   dplyr::mutate(myValence.excluded = .x, .before = 1) %>% 
                   dplyr::filter(myValence != myValence.excluded)) %>% 
    dplyr::bind_rows() %>% 
    dplyr::group_by(myValence.excluded) %>% 
    tidyr::nest() %>% 
    # data is the column created by nest
    dplyr::mutate(aov =  map(data,
                             ~ aov(
                                 d ~ myValence,
                                 data = .x) %>% 
                                 report.aov(.correct.for.repeated.tests = FALSE,
                                            .return.df = TRUE,
                                            .print.results = FALSE)
    )) %>% 
    dplyr::select(-data) %>% 
    unnest(cols = c(aov)) %>% 
    dplyr::mutate(myValence =  str_c(v.valencies[!(v.valencies %in% myValence.excluded)], 
                                      collapse = " vs. "), 
                  .before = 1) %>% 
    dplyr::ungroup() %>% 
    dplyr::select(-model.name, -myValence.excluded) 


```
As shown in Table \ref{tab:city-acceptability-self-d-high-vs-low-tf-aov-show}, separate ANOVAs for each valency revealed a strong main effect of Action Status only for neutral scenarios. The main effect was not significant for good or bad scenarios. Again, this is redundant with the direct difference scores.



```{r city-acceptability-self-d-high-vs-low-tf-aov-show}

if (!is.null (aov.social.type.token.sequential.acceptability.self.d.high.vs.low.tf.ez.sphericity)){
    warning ("There were sphericity corrections available that you ignored, do something about them.")    
}


dplyr::bind_rows(
    # Overall anova
    dat.aov.social.type.token.sequential.acceptability.self.d.high.vs.low.tf %>% 
        dplyr::mutate(model.type = "Overall"),
    
    # By valencyy
    dat.aov.social.type.token.sequential.acceptability.self.d.high.vs.low.tf.followup.valency %>% 
        dplyr::mutate(model.type = "By valency")
) %>% 
    dplyr::select(model.type, myValence, effect, everything()) %>% 
        setNames(replace_default_column_labels(names (.))) %>%
        kable.packed("model.type",
                     caption = "ANOVA for difference scores comparing the high vs low type frequency conditions for first-person acceptability. The data combines male and female participants. (Top) Overall ANOVA. (Middle) Differences between frequency conditions separately for each valency for first person acceptability for all participants. (Bottom). Differences for each frequency conditions separately for first person acceptability for all participants.",
                     booktabs = TRUE, escape = FALSE) %>%
    kable_styling(latex_options =
                      c("hold_position", "striped")) %>%
    kableExtra::kable_classic_2()


```



`r clearpage()`

# Correlations

```{r correlations-vs-single-calculate}


l.dat.social.type.token.sequential.corr.vs.single <- dat.social.type.token.sequential.m.wide %>% 
    dplyr::group_by (myValence, Machiavellianism, Narcissism, Psychopathy) %>% 
    dplyr::select(starts_with(fixed ("d.vs.single_"))) %>% 
    dplyr::select(-ends_with(fixed ("_bin"))) %>%
    dplyr::rename_with(~ .x %>% 
                           str_remove(fixed ("d.vs.single_")) %>% 
                           str_remove (fixed ("_raw")) %>% 
                           str_replace_all ("_", " - ") %>% 
                           str_replace_all (fixed ("."), " ") %>% 
                           str_wrap(width = 15)) %>% 
    dplyr::group_by(myValence) %>% 
    dplyr::group_split () %>% 
    map (~ list (myValence = levels2 (.$myValence),
                 corrmat = .x %>% 
                     ungroup %>% 
                     dplyr::select(-c(myValence)) %>% 
                     as.matrix %>% 
                     Hmisc::rcorr (.)))



```

```{r extract-correlations-vs-single}
v.predictors <- c("Machiavellianism", "Narcissism", "Psychopathy")

l.dat.social.type.token.sequential.corr.vs.single %>% 
    map (~ .x$corrmat$P %>% 
             as.data.frame() %>% 
             #dplyr::mutate(across (everything(), ~ .x <= .05)) %>% 
             tibble::rownames_to_column ("var") %>% 
             dplyr::select(-v.predictors) %>% 
             dplyr::rowwise() %>% 
             dplyr::mutate (keep.row = any (dplyr::c_across(-c("var")) <= .05, na.rm= TRUE)) %>% 
             dplyr::filter (keep.row) %>% 
             dplyr::select (-keep.row) %>% 
             dplyr::filter (var %in% v.predictors) %>% 
             tibble::column_to_rownames("var") %>% 
             tdf %>% 
             tibble::rownames_to_column("var") %>% 
             dplyr::rowwise() %>% 
             dplyr::mutate (keep.row = any (dplyr::c_across(-c("var")) <= .05, na.rm= TRUE)) %>% 
             dplyr::filter (keep.row) %>% 
             dplyr::select (-keep.row) %>% 
             dplyr::mutate (myValence = .x$myValence, .before = 1)) %>% 
    dplyr::bind_rows() %>% 
    dplyr::mutate (var = str_replace_all (var, fixed ("\n"), " ")) %>%
    kable.packed (
        "myValence",
        caption = "P values of significant correlations between dark triad predictors and difference scores comparing ratings to the equivalent ratings in the single occurrence condition,",
        escape = TRUE,
       booktabs = TRUE) %>%
kableExtra::kable_classic()
    

```

```{r correlations-high-vs-low-calculate}


l.dat.social.type.token.sequential.corr.high.vs.low <- dat.social.type.token.sequential.m.wide %>% 
    dplyr::group_by (myValence, Machiavellianism, Narcissism, Psychopathy) %>% 
    dplyr::select(starts_with(fixed ("d.high.vs.low.TypeFreq_"))) %>% 
    dplyr::select(-ends_with(fixed ("_bin"))) %>%
    dplyr::rename_with(~ .x %>% 
                           str_remove(fixed ("d.high.vs.low.TypeFreq_")) %>% 
                           str_remove (fixed ("_raw")) %>% 
                           str_replace_all ("_", " - ") %>% 
                           str_replace_all (fixed ("."), " ") %>% 
                           str_wrap(width = 15)) %>% 
    dplyr::group_by(myValence) %>% 
    dplyr::group_split () %>% 
    map (~ list (myValence = levels2 (.$myValence),
                 corrmat = .x %>% 
                     ungroup %>% 
                     dplyr::select(-c(myValence)) %>% 
                     as.matrix %>% 
                     Hmisc::rcorr (.)))



```

```{r extract-correlations-high-vs-low}

l.dat.social.type.token.sequential.corr.high.vs.low %>% 
    map (~ .x$corrmat$P %>% 
             as.data.frame() %>% 
             #dplyr::mutate(across (everything(), ~ .x <= .05)) %>% 
             tibble::rownames_to_column ("var") %>% 
             dplyr::select(-v.predictors) %>% 
             dplyr::rowwise() %>% 
             dplyr::mutate (keep.row = any (dplyr::c_across(-c("var")) <= .05, na.rm= TRUE)) %>% 
             dplyr::filter (keep.row) %>% 
             dplyr::select (-keep.row) %>% 
             dplyr::filter (var %in% v.predictors) %>% 
             tibble::column_to_rownames("var") %>% 
             tdf %>% 
             tibble::rownames_to_column("var") %>% 
             dplyr::rowwise() %>% 
             dplyr::mutate (keep.row = any (dplyr::c_across(-c("var")) <= .05, na.rm= TRUE)) %>% 
             dplyr::filter (keep.row) %>% 
             dplyr::select (-keep.row) %>% 
             dplyr::mutate (myValence = .x$myValence, .before = 1)) %>% 
    dplyr::bind_rows() %>% 
    dplyr::mutate (var = str_replace_all (var, fixed ("\n"), " ")) %>%
    kable.packed (
        "myValence",
        caption = "P values of significant correlations between dark triad predictors and difference scores comparing comparing the high and the low type frequency conditions.",
        escape = TRUE,
       booktabs = TRUE) %>%
kableExtra::kable_classic()


```

```{r correlations-vs-single-plot, fig.cap = "Correlation for difference scores comparing actions against single occurrence actions.", fig.height=17}


par(mfrow=c(3, 1),  
    mar = c(1, 1, 1, 1))
    #xpd = TRUE)

l.dat.social.type.token.sequential.corr.vs.single %>% 
    purrr::walk(~ corrplot::corrplot(.x$corrmat$r,
                       is.corr = TRUE,
                       type = "lower",
                       diag = FALSE,
                       tl.col = "blue",
                       tl.cex = 1.5,
                       cl.cex = .5,
                       #bg = "gray",
                       tl.srt = 75,
                       title = str_c ("\n\n\n\n\n", .x$myValence),
                       addCoef.col = "black",
                       addgrid.col = "black",
                       #order = "hclust",
                       p.mat = .x$corrmat$P,
                       insig = "label_sig",
                       sig.level = .05,
                       mar = c(1, 1, 1, 1)
                       ))






```

```{r correlations-high-vs-low-plot, fig.cap = "Correlation for difference scores comparing high vs. low type frequency actions.", fig.height=17}


par(mfrow=c(3, 1),  
    mar = c(1, 1, 1, 1))
    #xpd = TRUE)

l.dat.social.type.token.sequential.corr.high.vs.low %>% 
    purrr::walk(~ corrplot::corrplot(.x$corrmat$r,
                       is.corr = TRUE,
                       type = "lower",
                       diag = FALSE,
                       tl.col = "blue",
                       tl.cex = 1.5,
                       cl.cex = .5,
                       #bg = "gray",
                       tl.srt = 75,
                       title = str_c ("\n\n\n\n\n", .x$myValence),
                       addCoef.col = "black",
                       addgrid.col = "black",
                       #order = "hclust",
                       p.mat = .x$corrmat$P,
                       insig = "label_sig",
                       sig.level = .05,
                       mar = c(1, 1, 1, 1)
                       ))






```

`r clearpage()`

# Binary ratings (analyzed using GLMER)
## Ratings

```{r print-descriptives-ratings-bin}

dat.social.type.token.sequential.m %>% 
    dplyr::filter(scoring == "bin") %>% 
    dplyr::select(-scoring) %>% 
    dplyr::group_by(myValence, myQueriedActionStatus, question) %>% 
    dplyr::summarize(
        N = n(),
        M = mean(rating),
        SE = se(rating)
        ) %>% 
    dplyr::arrange (question, myValence, myQueriedActionStatus) %>% 
    tidyr::unite(pack.col, myValence, question, sep = " - ") %>% 
    kable.packed("pack.col", 
                 caption = "Descriptives for the data into binary ratings.",
                 col.names = c("", "N", "M", "SE"),
                 booktabs = TRUE,
                 longtable=TRUE) %>% 
    kableExtra::kable_styling(latex_options = "repeat_header") %>% 
    kableExtra::kable_classic_2()


```

```{r plot-acurracy-bin, fig.cap = "Bin ratings"}

dat.social.type.token.sequential.m %>% 
    dplyr::filter (scoring == "bin") %>% 
    dplyr::mutate (myQueriedActionStatus = str_wrap(myQueriedActionStatus, 10)) %>% 
    dplyr::mutate (question = str_replace_all(question, fixed ("."), " ")) %>% 
    dplyr::mutate (question = str_wrap(question, 20)) %>% 
    ggplot (aes (x = myQueriedActionStatus, y = rating)) +
        theme_light(14) +
    theme (axis.title.x = element_blank(),
           axis.text.x = element_text(angle = 35, vjust = .5, hjust=.5)) + 
    ylab ("Rating (binary)") + 
    geom_violin() +
    geom_dotplot(binaxis='y', stackdir='center', dotsize=1) +
    stat_summary(fun.data=mean_se, 
                 geom="pointrange", color="red") +
    geom_hline(yintercept=.5, linetype = "dotted") +
    #scale_x_discrete(labels = c("Pre-segmented", "Continuous (1)", "Continuous (2)"))
    facet_grid(question ~ myValence)



```

### Prevalence 



```{r city-prevalence-glmer-bin-calculate}


dat.social.type.token.sequential.for.glmm <- dat.social.type.token.sequential %>% 
        dplyr::filter(scoring == "bin") %>% 
        dplyr::mutate(myQueriedActionStatus = factor(myQueriedActionStatus,
                                                     levels = c("single", "lowTypeFreq", "highTypeFreq")),
                      myValence = factor(myValence, 
                                         levels = c("neutral", "bad", "good"))) %>% 
        dplyr::mutate(across(c(filename, myQueriedAction), factor))


lmer.social.type.token.sequential.city.bin.prevalence.1 <- glmer(
    rating ~ myQueriedActionStatus * myValence + 
        (1|filename) + (1|myQueriedAction), 
    control=glmerControl(optimizer="bobyqa"),
    family="binomial",
    data = dat.social.type.token.sequential.for.glmm %>% 
                dplyr::filter(question == "prevalence"))

    
# Remove random factor  
lmer.social.type.token.sequential.city.bin.prevalence.2 <- update(
    lmer.social.type.token.sequential.city.bin.prevalence.1,
    ~ . - (1|myQueriedAction))  
    
# anova(lmer.social.type.token.sequential.city.bin.prevalence.1,
#       lmer.social.type.token.sequential.city.bin.prevalence.2)

## Remove interaction
lmer.social.type.token.sequential.city.bin.prevalence.3 <- update(
    lmer.social.type.token.sequential.city.bin.prevalence.1,
    ~ . - myQueriedActionStatus:myValence)  

# anova(lmer.social.type.token.sequential.city.bin.prevalence.1,
#       lmer.social.type.token.sequential.city.bin.prevalence.3)

# Keep full model

lmer.social.type.token.sequential.city.bin.prevalence.results <- 
    extract.results.from.binary.model(lmer.social.type.token.sequential.city.bin.prevalence.1)


```


### Third-party acceptability

```{r city-acceptability-other-glmer-bin-calculate}


lmer.social.type.token.sequential.city.bin.acceptability.other.1 <- glmer(
    rating ~ myQueriedActionStatus * myValence + 
        (1|filename) + (1|myQueriedAction), 
    control = glmerControl(optimizer="bobyqa"),
    family = "binomial",
    data = dat.social.type.token.sequential.for.glmm %>% 
        dplyr::filter(question == "third.party.acceptability"))

    
# Remove random factor  
lmer.social.type.token.sequential.city.bin.acceptability.other.2 <- update(
    lmer.social.type.token.sequential.city.bin.acceptability.other.1,
    ~ . - (1|myQueriedAction))  
    
# anova(lmer.social.type.token.sequential.city.bin.acceptability.other.1,
#       lmer.social.type.token.sequential.city.bin.acceptability.other.2)

## Remove interaction
lmer.social.type.token.sequential.city.bin.acceptability.other.3 <- update(
    lmer.social.type.token.sequential.city.bin.acceptability.other.1,
    ~ . - myQueriedActionStatus:myValence)  

# anova(lmer.social.type.token.sequential.city.bin.acceptability.other.1,
#       lmer.social.type.token.sequential.city.bin.acceptability.other.3)

# Keep full model

lmer.social.type.token.sequential.city.bin.acceptability.other.results <- 
    extract.results.from.binary.model(lmer.social.type.token.sequential.city.bin.acceptability.other.1)



    
```



### First-party acceptability

```{r city-acceptability-self-glmer-bin-calculate}


lmer.social.type.token.sequential.city.bin.acceptability.self.1 <- glmer(
    rating ~ myQueriedActionStatus * myValence + 
        (1|filename) + (1|myQueriedAction), 
    control = glmerControl(optimizer="bobyqa"),
    family = "binomial",
    data = dat.social.type.token.sequential.for.glmm %>% 
        dplyr::filter(question == "first.party.acceptablity"))

    
# Remove random factor  
lmer.social.type.token.sequential.city.bin.acceptability.self.2 <- update(
    lmer.social.type.token.sequential.city.bin.acceptability.self.1,
    ~ . - (1|myQueriedAction))  
    
# anova(lmer.social.type.token.sequential.city.bin.acceptability.self.1,
#       lmer.social.type.token.sequential.city.bin.acceptability.self.2)

## Remove interaction
lmer.social.type.token.sequential.city.bin.acceptability.self.3 <- update(
    lmer.social.type.token.sequential.city.bin.acceptability.self.1,
    ~ . - myQueriedActionStatus:myValence)  

# anova(lmer.social.type.token.sequential.city.bin.acceptability.self.1,
#       lmer.social.type.token.sequential.city.bin.acceptability.self.3)

# Keep full model for consistency

lmer.social.type.token.sequential.city.bin.acceptability.self.results <- 
    extract.results.from.binary.model(lmer.social.type.token.sequential.city.bin.acceptability.self.1)
```


```{r city-glmer-print}
dplyr::bind_rows(
    lmer.social.type.token.sequential.city.bin.prevalence.results %>% 
        dplyr::mutate(pack.col = "Prevalence", .before = 1),
    
lmer.social.type.token.sequential.city.bin.acceptability.other.results %>% 
        dplyr::mutate(pack.col = "Third party acceptability", .before = 1),

lmer.social.type.token.sequential.city.bin.acceptability.self.results %>% 
    dplyr::mutate(pack.col = "First party acceptability", .before = 1)
) %>% 
    dplyr::select (-c("t_log", "p_log")) %>% 
    #filter (!grepl ("Intercept", term)) %>% 
    kable.packed (
    "pack.col",
    caption = "GLMER results, using the full models.",
    col.names = str_remove(names (.[,-1]), "_.*$"),
       booktabs = TRUE, escape = FALSE) %>%
    kableExtra::kable_classic() %>%
    kableExtra::add_header_above(c(" " = 1, "Log-odds" = 3, "Odd ratios" = 3, " " = 2),
                                 bold = TRUE) %>% 
    kableExtra::kable_styling(latex_options =
                                  c("scale_down",
                              "hold_position",
                              "full_width"))

```







## Difference scores (GLMER or ANOVA?)

```{r plot-difference-vs-single-bin, fig.cap = "Binary difference scores vs. single occurrence actions"}

dat.social.type.token.sequential.m.wide %>% 
    group_by (myValence) %>% 
    dplyr::select(starts_with(fixed ("d."))) %>% 
    dplyr::select(ends_with(fixed ("_bin"))) %>% 
    dplyr::select(contains (fixed ("vs.single"))) %>% 
    tidyr::pivot_longer(-c(myValence),
                        names_to = "Contrast",
                        values_to = "d") %>% 
    dplyr::mutate (Contrast = Contrast %>% 
                       str_remove ("_bin$") %>% 
                       str_remove ("^d\\.vs\\.single\\_")) %>% 
    tidyr::separate(Contrast, c("myQueriedActionStatus", "question"), sep = "_") %>% 
    dplyr::mutate (question = str_replace_all(question, fixed ("."), " ")) %>% 
    dplyr::mutate (question = str_wrap(question, 20)) %>% 
    ggplot (aes (x = myQueriedActionStatus, y = d)) +
        theme_light(14) +
    theme (axis.title.x = element_blank(),
           axis.text.x = element_text(angle = 35, vjust = .5, hjust=.5)) + 
    ylab ("Difference score (binary)") + 
    geom_violin() +
    geom_dotplot(binaxis='y', stackdir='center', dotsize=1) +
    stat_summary(fun.data=mean_se, 
                 geom="pointrange", color="red") +
    geom_hline(yintercept=0, linetype = "dotted") +
    #scale_x_discrete(labels = c("Pre-segmented", "Continuous (1)", "Continuous (2)"))
    facet_grid(question ~ myValence)




```


```{r plot-difference-high-vs-low-type-frequency-bin, fig.cap = "Binary difference scores high vs. low type frequency actions"}

dat.social.type.token.sequential.m.wide %>% 
    group_by (myValence) %>% 
    dplyr::select(starts_with(fixed ("d."))) %>% 
    dplyr::select(ends_with(fixed ("_bin"))) %>% 
    dplyr::select(-contains (fixed ("vs.single"))) %>% 
    tidyr::pivot_longer(-c(myValence),
                        names_to = "question",
                        values_to = "d") %>%
    dplyr::mutate (question = question %>% 
                       str_remove ("_bin$") %>% 
                       str_remove ("^d\\.high\\.vs\\.low\\.TypeFreq_")) %>% 
    dplyr::mutate (question = str_replace_all(question, fixed ("."), " ")) %>% 
    dplyr::mutate (question = str_wrap(question, 20)) %>% 
    ggplot (aes (x = question, y = d)) +
        theme_light(14) +
    theme (axis.title.x = element_blank(),
           axis.text.x = element_text(angle = 35, vjust = .5, hjust=.5)) + 
    ylab ("Difference score (binary)") + 
    geom_violin() +
    geom_dotplot(binaxis='y', stackdir='center', dotsize=1) +
    stat_summary(fun.data=mean_se, 
                 geom="pointrange", color="red") +
    geom_hline(yintercept=0, linetype = "dotted") +
    #scale_x_discrete(labels = c("Pre-segmented", "Continuous (1)", "Continuous (2)"))
    facet_grid(. ~ myValence)




```

### Prevalence 

### Third-party acceptability

### First-party acceptability
