---
title: "Social learning by type-token frequency - analysis"
author: |
  | Ansgar D. Endress
  | City, University of London
bibliography: /Users/endress/ansgar.bib
output:
  bookdown::pdf_document2:
    latex_engine: xelatex      
    citation_package: natbib
    includes:
#      in_header: ansgar.sty
    toc: no
    number_sections: yes
    keep_tex: yes
    fig_caption: yes
    highlight: tango
  html_notebook:
    theme: spacelab
    number_sections: yes
    toc: yes
    toc_float: yes
    fig_caption: yes
    highlight: tango
    mathjax: local
  html_document:
    theme: spacelab
    number_sections: yes
    df_print: paged
    toc: yes
    toc_float: yes
    fig_caption: yes
    highlight: tango
    mathjax: local
csl: /Users/endress/csl_files/science.csl
keywords: Keywords
abstract: Abstract (to be written). Argument structure - See below. Analysis structure - 1. Descriptives of difference scores and tests against zero. 2. GLMMs, with reference to ANOVA. Discuss quorum sensing [@Sumpter2009] Discuss moral repetition effect, and tolerance principle and submit to psych sci. In intro. Different formal perspectives suggest that mere frequency should not be relevant, From a learning perspective,  [Explanation of tolerance principle; argue later that threshold is 8/ln(8) = 3.8, but that we did not vary this experimentally as it's too long; general explanation of tolerance principle- When having a productive rule is faster than listing all items as exception]. From a representational perspective, dispositions. intrinsic properties of banana; bayesian argument. From a social perspective, majority. Whatever the moral frequency guy argues.
---

```{r setup, echo = FALSE, include=FALSE}
rm (list=ls())


options(digits = 3,
        knitr.kable.NA = '')

knitr::opts_chunk$set(
    # Run the chunk
    eval = TRUE,
    # Don't include source code
    echo = FALSE, 
    # Print warnings to console rather than the output file
    warning = FALSE,  
    # Stop on errors
    error = FALSE,
    # Print message to console rather than the output file
    message = FALSE,
    # Include chunk output into output
    include = TRUE,
    # Don't reformat R code
    tidy = FALSE,
    # Center images
    fig.align = 'center',
    # Default image width
    out.width = '80%')

# other knits options are here:
# https://yihui.name/knitr/options/
```


```{r load-libraries, include = FALSE, message = TRUE, warning = TRUE}

if (Sys.info()[["user"]] %in% c("ansgar", "endress")){
    source ("/Users/endress/R.ansgar/ansgarlib/R/tt.R")
    source ("/Users/endress/R.ansgar/ansgarlib/R/null.R")
    #source ("helper_functions.R")
} else {
    # Note that these will probably not be the latest versions
    source("http://endress.org/progs/tt.R")
    source("http://endress.org/progs/null.R")
}


librarian::shelf(
    ordinal,
    knitr,
    kableExtra,
    janitor,
    purrr,
    ggpubr)

# Set default theme
#theme_set(theme_linedraw(14))
#theme_set(cowplot::theme_minimal_grid(14))
theme_set(ggthemes::theme_clean(14))
theme_update(legend.position = "bottom",
             legend.justification = "center")

```

```{r set-parameters}
DATA.DIR <- "../data/"
OUTPUT.DIR <- "output/"
FIG.DIR <- "figs/"




FILTER.BY.ATTRACTIVENESS <- FALSE    
MIN.ATTRACTIVENESS.QUANTILE <- .25
MAX.ATTRACTIVENESS.QUANTILE <- 1

# Parameters for analysis
IGNORE.COL.PREFIXES <- c("ITI_", "presTime_", "ISI_")

PRINT.INDIVIDUAL.FIGURES <- FALSE
PRINT.INDIVIDUAL.TABLES <- FALSE

REMOVE.BAD.SUBJ <- TRUE


# Should we remove participants who take excessively long/short?
DURATION.REMOVAL.THRESHOLD.Z <- 3

# Stimulus parameters
# PRESTIME <- 4000
# ITI <- 1000
PRESTIME <- 4500
ITI <- 500


N.REPETITIONS.PER.ACTION <- 6
# Number of face stimuli required
N.FACES.PER.GENDER <- 3 * 4 * 3 * N.REPETITIONS.PER.ACTION

VALENCE.IS.BETWEEN.SUBJECTS <- TRUE

# Set seed to Cesar's birthday
set.seed (1207100)
```



```{r read-data, include = FALSE}

dat.social.type.token.sequential.raw <- dplyr::bind_rows(
    read.testable.results("../data/994749_sequential_1/results", 
                          n.subj.info.lines = 2,
                          comment.char = "",
                          ignore.col.prefixes = IGNORE.COL.PREFIXES,
                          stringsAsFactors = FALSE) %>% 
        dplyr::mutate(population = "students", .before = 1),
    read.testable.results("../data/159771_sequential_testable/results",
                          n.subj.info.lines = 2,
                          comment.char = "",
                          ignore.col.prefixes = IGNORE.COL.PREFIXES,
                          stringsAsFactors = FALSE) %>% 
        dplyr::mutate(population = "testable", .before = 1))
    

l.populations <- dat.social.type.token.sequential.raw %>% 
    pull(population) %>% 
    levels2 %>% 
    as.list

    

```


```{r helper-functions}

map.by.population <- function(...){
    l.populations %>% 
        purrr::set_names() %>% 
        purrr::map(...)
}
 
make.diff.score <- function(x, y, relative = TRUE){
    

    if(length(x) != length(y)) {
        stop("x and y must be of the same length.")
    }
    
    if(relative) {
        
        return(dplyr::if_else((x == 0) & (y == 0),
                              0,
                              (x - y)/(x + y)))
        
    } else {
        
        return(x - y)
        
    }
        
}


relabel_conds <- function(dat = ., wrap = TRUE, cond_col = myQueriedActionStatus){
    
    cond_col <- rlang::enquo(cond_col)
    
    dat.out <- dat %>% 
        dplyr::mutate(!!cond_col := 
                          !!cond_col %>% 
                          str_replace("(high|low)", "\\1 ") %>% 
                          str_replace("Freq$", "-Frequency") %>% 
                          str_replace("single", "Single Occurrence") %>% 
                          str_to_title())
    
    if(wrap){
        dat.out <- dat.out %>% 
            dplyr::mutate(!!cond_col := 
                              !!cond_col %>% 
                              str_wrap(10))
        
    }
    
    dat.out
}

    
    
relabel_questions <- function(dat = ., wrap = TRUE, sort = FALSE, sort_order = c(1, 3, 2), question_col = question){
    
    
    question_col <- rlang::enquo(question_col)
    
    
    dat.out <- dat %>% 
        #dplyr::mutate(!!question_col := str_replace_all(!!question_col, fixed ("."), " ")) %>% 
        #dplyr::mutate(!!question_col := str_wrap(!!question_col, 20)) %>% 
        mutate(!!question_col := forcats::fct_relabel(!!question_col, ~ str_replace_all(.x, fixed("."), " "))) %>%
        mutate(!!question_col := forcats::fct_relabel(!!question_col, ~ str_to_title(.x))) 
    
    if(wrap){
        dat.out <- dat.out %>% 
            mutate(!!question_col := forcats::fct_relabel(!!question_col, ~ str_wrap(.x, 20)))
        
    } 
    
    if(sort){
        dat.out <- dat.out %>% 
            mutate(!!question_col := factor(!!question_col, levels = levels(!!question_col)[sort_order]))
        
    }
    
    dat.out
    
}

relabel_terms <- function(dat = ., wrap = TRUE, type = c("glm", "aov"), term_col = Parameter){
    
    term_col <- rlang::enquo(term_col)
    
    type <- match.arg(type)
    
    if (!rlang::as_name(term_col) %in% colnames(dat)) {
        stop("The specified column does not exist in the data.")
    }
    
    if(type == "glm"){
    dat.out <- dat %>% 
        dplyr::mutate(!!term_col := 
                          !!term_col %>% 
                          str_replace_all(":", "$\\\\times$") %>% 
                          str_replace("myValence(good|bad)", "Valence:\\1") %>% 
                          str_replace("myQueriedActionStatus(.)", "Freq. Cond:\\1") %>% 
                          str_replace("(high|low)", "\\1 ") %>% 
                          str_replace("Freq$", "-Freq.") %>% 
                          str_replace("single", "Single Occ.") %>% 
                          str_to_title() %>% 
                          str_replace(fixed("\\Times"), fixed("\\times")))
    } else {
        if(type == "aov"){
            
            dat.out <- dat %>% 
                dplyr::mutate(!!term_col := 
                                  !!term_col %>% 
                                  str_replace_all(":", "$\\\\times$") %>% 
                                  str_replace("myValence", "Valence") %>% 
                                  str_replace("myQueriedActionStatus", "Freq. Cond") %>% 
                                  str_to_title() %>% 
                                  str_replace(fixed("\\Times"), fixed("\\times")))
            
        } else {
            stop("Unknown type")
        }
    }
    
    if(wrap){
        dat.out <- dat.out %>% 
            dplyr::mutate(!!term_col := 
                              !!term_col %>% 
                              str_wrap(10))
        
    }
    
    dat.out
}



abbreviate_cols <- function(dat = .){
    
    col_abbreviations <- c(
        Sum_Squares        = "SS",
        Sum_Squares_Error  = "SS_error",
        df                 = "df",
        df_error           = "df_error",
        Mean_Square        = "MSq"
    )
    
    dat %>% 
        dplyr::rename_with(.fn = ~ col_abbreviations[.x],
                           .cols = intersect(names(col_abbreviations), names(dat))) 
}
    

rename_col_names <- function(x = .){
    
    x %>% 
        replace_default_column_labels %>% 
        str_replace_all("myValence", "Valence") %>% 
        str_replace_all("^sig$", " ")
    
        
    
}

# Custom labeller that converts to title case
title_case_labeller <- function(labels) {
  lapply(labels, str_to_title)
}
       
```

# Methods (continued)
## Exclusions

```{r check-attention-test}

dat.social.type.token.sequential.bad.subj.attention <- dat.social.type.token.sequential.raw %>% 
    dplyr::filter(myPhase == "attentionTest") %>% 
    dplyr::select(filename, myPhase, response) %>% 
    dplyr::filter(response !=2)

if (nrow (dat.social.type.token.sequential.bad.subj.attention) > 0 ){
    dat.social.type.token.sequential.raw <- 
        anti_join(
            dat.social.type.token.sequential.raw,
            dat.social.type.token.sequential.bad.subj.attention,
            by = "filename")
    
}
    
    
```

I excluded `r nrow (dat.social.type.token.sequential.bad.subj.attention)` participants because they failed the attention test.

## SD3 REMOVE THIS IN PAPER

We next analyze the SD3 and combine the results with the data frame for the main experiment. 


```{r analyze-sd3}

# Run for city students only

dat.social.type.token.sequential.sd3 <- dat.social.type.token.sequential.raw %>% 
    dplyr::filter(population == "students") %>% 
    dplyr::filter(myPhase == "SD3") %>% 
    dplyr::mutate(max.response = str_count(responseOptions, ";") + 1) %>% 
    dplyr::mutate(responseCode = as.numeric(responseCode)) %>% 
    # Don't know if it's logical or not
    dplyr::mutate(mySD3reversed = as.character(mySD3reversed)) %>% 
    dplyr::mutate(responseCode = ifelse(mySD3reversed == "TRUE",
                                          max.response + 1 - responseCode,
                                          responseCode)) %>% 
    dplyr::group_by(population, filename, myPhase, mySD3subScale) %>% 
    dplyr::summarize(score = sum(responseCode)) %>% 
    tidyr::pivot_wider(id_cols = c(population, filename, myPhase),
                       names_from = mySD3subScale,
                       values_from = score) %>% 
    dplyr::ungroup()
    
```

```{r analyze-sd3-add-median-split}
    
dat.social.type.token.sequential.sd3 <- 
    dat.social.type.token.sequential.sd3 %>% 
    dplyr::mutate(dplyr::across(where(is.numeric),
                                ~ dplyr::case_when(
                                    .x > median(.x) ~ "high",
                                    .x < median (.x) ~ "low",
                                    TRUE ~ NA_character_),
                                .names = "{.col}.group"))



# Verify the number of participants on the median
dat.social.type.token.sequential.sd3.counts <-
    dat.social.type.token.sequential.sd3 %>%  
    dplyr::select(ends_with("group")) %>% 
    tidyr::pivot_longer(ends_with("group"),
                        names_to = "scale",
                        values_to = "group") %>% 
    dplyr::mutate(scale = str_remove(scale, ".group")) %>% 
    janitor::tabyl(scale, group)
    


dplyr::left_join(
    dat.social.type.token.sequential.sd3.counts,
    dat.social.type.token.sequential.sd3.counts %>% 
        janitor::adorn_percentages("row"),
    by = "scale",
    suffix = c(".N", ".P")) %>% 
    knitr::kable(caption = "Number of participants in each group of the SD3 scales. Note that this applies to city students only",
                 booktabs = TRUE,
                 col.names = str_remove(names(.), "\\..$")) %>% 
    kableExtra::add_header_above(c(" " = 1, "N" = 3, "Percentage" = 3), bold = TRUE) %>% 
    kableExtra::kable_classic()
    

    
```

```{r combine-with-sd3}

dat.social.type.token.sequential <- 
    left_join(
        dat.social.type.token.sequential.raw %>% 
            dplyr::filter(myPhase == "experiment"),
        dat.social.type.token.sequential.sd3 %>% 
            dplyr::ungroup() %>% 
            dplyr::select(-myPhase, -population),
        by = "filename") 
    

```


```{r format-responses}
# * separate response code into 3 separate response
# * add binary responses
# * transform to long

dat.social.type.token.sequential <- 
    dat.social.type.token.sequential %>% 
    dplyr::mutate(max.response = str_count(responseOptions, ";") + 1) %>% 
    tidyr::separate(responseCode, 
                    c("prevalence_raw", "third.party.acceptability_raw", "first.party.acceptability_raw"),
                    convert = TRUE) %>% 
    dplyr::mutate(dplyr::across(ends_with("raw"),
                                  ~ 1 * (.x > max.response/2), 
                                  .names = "{.col}_bin")) %>% 
    dplyr::rename_with(~ str_replace (.x, "raw_bin", "bin"), ends_with("bin")) %>% 
    tidyr::pivot_longer(c(ends_with("raw"), ends_with("bin")),
                        names_to = "question",
                        values_to = "rating") %>% 
    tidyr::separate(question, c("question", "scoring"), "_") %>% 
    dplyr::mutate(question = factor(question, levels = c("prevalence", "third.party.acceptability", "first.party.acceptability"))) %>% 
    dplyr::mutate(myValence = factor(myValence, levels = c("bad", "neutral", "good")))
    
    

```

```{r make-averages}

dat.social.type.token.sequential.m <- dat.social.type.token.sequential %>% 
    dplyr::group_by(population, filename, age, gender, 
                    Machiavellianism, Narcissism, Psychopathy, 
                    Machiavellianism.group, Narcissism.group, Psychopathy.group, 
                    myQueriedActionStatus, myValence, question, scoring) %>% 
    dplyr::summarize(rating = mean(rating), .groups = "drop") %>% 
    dplyr::arrange(filename, scoring, myValence, myQueriedActionStatus, question) %>% 
    dplyr::mutate(question = factor(question, levels = c("prevalence", "first.party.acceptability", "third.party.acceptability")))



```



```{r make-wide}

dat.social.type.token.sequential.m.wide <- dat.social.type.token.sequential.m %>% 
    tidyr::pivot_wider(id_cols = c(population, filename, age, gender, 
                                   Machiavellianism, Narcissism, Psychopathy, 
                                   Machiavellianism.group, Narcissism.group, Psychopathy.group,
                                   myValence),
                       names_from = c(myQueriedActionStatus, question, scoring),
                       values_from = rating)

```

```{r add-diff-scores-to-wide-define-function}

# Function to apply all the difference score calculations based on the grid
add_all_diff_scores <- function(df_wide = ., cond_grid) {
  
  # Nested function to calculate the difference score
  add_diff_score <- function(df, freq_cond1, freq_cond2, measure, value_type) {
      
    # Construct the column names dynamically based on the inputs
    col1 <- paste0(freq_cond1, "_", measure, "_", value_type)
    col2 <- paste0(freq_cond2, "_", measure, "_", value_type)
    
    # Create the new column name
    new_col_name <- paste0("d.", freq_cond1, ".vs.", freq_cond2, "_", measure, "_", value_type)
    
    
    # Calculate the difference score
    df <- df %>%
      dplyr::mutate(!!new_col_name := make.diff.score(!!sym(col1), !!sym(col2)))
    
    return(df)
  } # End of add_diff_score
  
  
  cond_list <- purrr::transpose(cond_grid)
  
  # Iterate over the grid and apply the difference score calculation
  df_augmented <- purrr::reduce(
      cond_list,
      .init = df_wide,
      .f = function(current_df, current_cond) {
          
          # Apply the function using extracted values
          add_diff_score(current_df,
                         freq_cond1 = current_cond$freq_cond1,
                         freq_cond2 = current_cond$freq_cond2,
                         measure = current_cond$measure,
                         value_type = current_cond$value_type)
      }
  )
  
  return(df_augmented)
}
```

```{r add-diff-scores-to-wide-define-comparisons}
# Create the comparison grid for all difference scores using tidyr::crossing()
comparison_grid <- tidyr::crossing(freq_cond1 = c("single", "highTypeFreq", "lowTypeFreq"),
                                   freq_cond2 = c("single", "highTypeFreq", "lowTypeFreq"),
                                   measure = c("prevalence", "first.party.acceptability", "third.party.acceptability"),
                                   value_type = c("bin", "raw")) %>%
    # Filter out comparisons where freq1 == freq2 
    dplyr::filter(freq_cond1 != freq_cond2) %>% 
    # Create a new column with sorted pairs to remove duplicates regardless of order
    dplyr::mutate(freq_pair = purrr::pmap_chr(list(freq_cond1, freq_cond2), 
                                              ~paste(sort(c(.x, .y)), collapse = "_"))) %>%
    # Remove duplicate rows based on the sorted freq_cond pairs
    dplyr::distinct(freq_pair, measure, value_type, .keep_all = TRUE) %>%
    # Drop the freq_pair column
    dplyr::select(-freq_pair)
```

```{r add-diff-scores-to-wide-define-calculate}
# Now add all difference scores
dat.social.type.token.sequential.m.wide <- dat.social.type.token.sequential.m.wide %>% 
    add_all_diff_scores(comparison_grid)


```



```{r add-diff-scores-to-wide-per-valency-averages}

dat.social.type.token.sequential.m.wide <- dat.social.type.token.sequential.m.wide %>% 
    dplyr::rowwise() %>% 
    # Select columns that don't start with d
    dplyr::mutate(mean.prevalence_raw = mean(dplyr::c_across(tidyr::matches("^[^d].*prevalence_raw"))),
                  mean.third.party.acceptability_raw = mean(dplyr::c_across(tidyr::matches("^[^d].*third.party.acceptability_raw"))),
                  mean.first.party.acceptability_raw = mean(dplyr::c_across(tidyr::matches("^[^d].*first.party.acceptability_raw")))) 

```

```{r diff-scores-make-long-version}

dat.social.type.token.sequential.m.d.long <- dat.social.type.token.sequential.m.wide %>% 
    dplyr::ungroup() %>% 
    dplyr::select(population, filename, age, gender, 
                  Machiavellianism, Narcissism, Psychopathy, 
                  Machiavellianism.group, Narcissism.group, Psychopathy.group,
                  myValence,
                  starts_with(fixed ("d."))) %>% 
    tidyr::pivot_longer(starts_with(fixed ("d.")),
                        names_to = "contrast",
                        values_to = "d") %>% 
    tidyr::separate_wider_delim(contrast,
                                    delim = "_",
                                    names = c("contrast", "question", "scoring"), 
                                    too_few = "error") 

# 2 x scoring
# 3 x questions
# 3 types of difference scores (against single: 2 x scores + high vs. low: 1 score)
if(nrow(dat.social.type.token.sequential.m.wide) * 2 * 3 * 3 !=  nrow(dat.social.type.token.sequential.m.d.long)){
    stop("Check the creation of difference scores")
}



        

```

```{r determine-number-of-trials}

n.trials.per.condition <- dat.social.type.token.sequential %>% 
    dplyr::count(population, filename, question, scoring, myValence, myQueriedActionStatus) %>% 
    dplyr::select(n) %>% 
    dplyr::distinct() %>% 
    pull(n)

```

```{r save-for-students, eval - FALSE}

xlsx::write.xlsx (
    data.frame (column = names (dat.social.type.token.sequential.m.wide)),
    file="output/dat.social.type.token.sequential.xlsx",
    row.names=FALSE,
    sheetName="Explanation",
    append=FALSE)

xlsx::write.xlsx (
    dat.social.type.token.sequential.m.wide %>% 
        dplyr::select(-ends_with(fixed ("_bin"))) %>% 
        as.data.frame,
    file="output/dat.social.type.token.sequential.xlsx",
    row.names=FALSE,
    sheetName="Raw ratings",
    append=TRUE)


xlsx::write.xlsx (
    dat.social.type.token.sequential.m.wide %>% 
        dplyr::select(-ends_with(fixed ("_raw"))) %>% 
        as.data.frame,
    file="output/dat.social.type.token.sequential.xlsx",
    row.names=FALSE,
    sheetName="Binary ratings",
    append=TRUE)

```

`r clearpage()`


## Analysis strategy
I analyzed the data in three stages. First, I present descriptives of the raw ratings to serve as task validations, as good actions should be rated as morally better than bad actions. However, I had no other predictions for the raw levels of acceptability.

Second, for each domain (first-party acceptability, third-party acceptability, prevalence), I calculated two types of difference scores. Following [@Rosenthal1999], I used focused difference scores (rather than models with effects for which I had no predictions) to target the contrasts of interest, also ensuring consistency between visualizations and statistical tests. The first type of difference score assesses the effect of type and token frequency compared to single occurrence events, namely  $\frac{\text{High Type-Frequency} - \text{Single Occurrence}}{\text{High Type-Frequency} + \text{Single Occurrence}}$ and $\frac{\text{Low Type-Frequency} - \text{Single Occurrence}}{\text{Low Type-Frequency} + \text{Single Occurrence}}$. I compared these difference scores to the chance level of zero using Wilcoxon tests.

The second type of difference score compared the effects of type and token frequency with each other, specifically $\frac{\text{High Type-Frequency} - \text{Low Type-Frequency}}{\text{High Type-Frequency} + \text{Low Type-Frequency}}$. Again, I compared these difference scores to the chance level of zero. For both types of difference scores, I also asked whether they would be affected by the valence.  P-values were corrected using the Holm-Bonferroni method.

Finally, I used a series of Cumulative Linear Mixed Model (CLMM) with a logit link function to confirm these results [@Buerkner2019;@Liddell2018], using the ordinal $R$ package [@ordinal]. CLMMs assume that participant responses reflect an underlying latent variable. The model estimates multiple thresholds corresponding to different response categories, with a response given when the latent variable exceeds the threshold for that category. In addition to the thresholds, they also estimate linear predictors influencing the latent variable.

NOTE TO SELF: THERE ARE ALSO SEQUENTIAL MODELS, SEE [@Buerkner2019].

Problems with treating ordinal responses [@Liddell2018]


https://pmc.ncbi.nlm.nih.gov/articles/PMC10439063/ 
[@Taylor2023] this is about norms

## Participants

```{r print-demographics}

dat.social.type.token.sequential %>% 
    get.demographics2(filename, gender, age, population) %>% 
    knitr::kable(
    caption = "Demographics of the final sample",
        escape = FALSE) %>%
    kableExtra::add_header_above(c(" " = 5, "Age" = 2), bold = TRUE) %>% 
    kableExtra::kable_classic_2() 

```


`r clearpage()`

# Results
## Raw ratings 


```{r plot-ratings-raw, fig.cap = "Ratings for (a) testable participants and (b) students. The dots, error bars and violin represent the sample average, 95\\% bootstrap confidence intervals and the distribution of the individual responses, respectively. Open circles represent individual participants.", fig.height=6.5, fig.width=9.5}

levels2(dat.social.type.token.sequential.m$population) %>% 
    sort %>% 
    purrr::map(~ {
        
        dat.social.type.token.sequential.m %>% 
            dplyr::filter(population == .x) %>% 
            dplyr::filter(scoring == "raw") %>% 
            relabel_conds %>% 
            relabel_questions(wrap = TRUE, sort = TRUE, sort_order = c(2, 3, 1)) %>% 
            ggplot(aes (x = myQueriedActionStatus, y = rating)) %>% 
            violin_plot_template(yintercept = 2.5) +
            theme(axis.title.x = element_blank(),
                  axis.text.x = element_text(angle = 60, vjust = .5, hjust=.5)) + 
            labs(y = "Rating", 
                 title = str_to_title(.x)) + 
            #scale_x_discrete(labels = c("Pre-segmented", "Continuous (1)", "Continuous (2)"))
            facet_grid(question ~ myValence, labeller = labeller(.default = title_case_labeller))
        
    }) %>% 
ggpubr::ggarrange (plotlist = .,

    nrow = 1,
    labels = "auto",
    common.legend = TRUE,
    legend = "bottom")


```

The raw ratings are shown in Figure \ref{fig:plot-ratings-raw} and Table \ref{tab:print-descriptives-ratings-raw2}. As shown in Table \ref{tab:clmm-raw-effects-of-valency2}, a  CLMM with a logit link function, including the fixed predictors Valence and Frequency Condition, their interaction, and a random slope for participants—showed that, for both acceptability questions and both samples, good deeds were judged more positively than neutral ones, and neutral ones more positively than bad ones. The valence manipulation was thus successful.


```{r clmm-raw-effects-of-valency, results = 'hide'}

tidyr::crossing(
    # Avoid clashes with the column names below
    pop = levels2(dat.social.type.token.sequential.m$population),
    Q = levels2(dat.social.type.token.sequential.m$question) %>% 
        grepv("accept", .)) %>% 
    purrr::pmap_df(function(pop, Q){
        
        
        tmp_model <- ordinal::clmm(rating ~ myValence * myQueriedActionStatus + 
                                       (1|filename), 
                                   data = dat.social.type.token.sequential %>% 
                                       dplyr::filter(scoring == "raw") %>% 
                                       dplyr::filter(population == pop) %>% 
                                       dplyr::filter(str_detect(as.character(question), Q)) %>% 
                                       dplyr::mutate(
                                           rating = factor(rating, ordered = TRUE),
                                           myValence = factor(myValence, levels = c("neutral", "bad", "good"))) %>% 
                                       relabel_conds(wrap = FALSE) %>% 
                                       relabel_questions(wrap = FALSE, sort = TRUE),
                                   control = clmm.control(
                                       method = "nlminb",
                                       trace = 0,
                                       maxIter = 100, # Default 50
                                       gradTol = 1e-6, # Default 1e-4
                                       maxLineIter = 100, # Default 50
                                       useMatrix = FALSE,
                                       innerCtrl = "warnOnly",
                                       checkRanef = "warn"
                                   ),
                                    Hess = TRUE,
                                   link = "logit") 
        
        parameters::model_parameters(tmp_model) %>% 
        # Maybe cleaner with parameters
        # coefficients(summary(tmp_model)) %>%
        #     as.data.frame %>%
        #     tibble::rownames_to_column("Parameter") %>%
            dplyr::filter(str_detect(Parameter, "\\|", negate = TRUE)) %>% 
            dplyr::mutate(population = pop, 
                          question = Q,
                          .before = 1)
    }
    ) %>%
    dplyr::filter(str_detect(Parameter, "^myValence(good|bad)$")) %>%
    add_sig_stars(p) %>% 
    dplyr::rename_with(rename_col_names) %>% 
    relabel_questions(wrap = FALSE, sort = TRUE) %>% 
    relabel_terms %>% 
    tidyr::unite(pack.col, question, population, sep = " - ") %>%
    dplyr::select(-Effects, -Group, -df_error) %>% 
    kable.packed("pack.col",
                 caption = "Results on a set of cumulative linear mixed model, fitted separately for each sample (online or students) and domain (first-part acceptability and third-party acceptability), with the fixed factor predictors valence and frequency condition as well as their interaction, as well as a random slope for participants. Only the main effect of valence is shown. Significance codes: *** $p \\\\leq .001$, ** $p \\\\leq .01$, * $p \\\\leq .05$, . $p \\\\leq .10$, ns = not significant.",
                 #col.names = c("", rep(c("N", "M", "SE", "Cohen's d", "p"), 2)),
                 booktabs = TRUE,
                 longtable = TRUE) %>%
    #kableExtra::add_header_above(header = c(" " = 1, "Students" = 5, "Testable" = 5), bold = TRUE) %>%
    kableExtra::kable_styling(latex_options = "repeat_header") %>%
    # kableExtra::row_spec(which(dat.social.type.token.sequential.m.for.table$is_below_chance),
    #                      bold = TRUE, color = "red", background = "gray!20") %>%
    kableExtra::kable_classic_2()



```

```{r print-descriptives-ratings-raw, results = 'hide'}

dat.social.type.token.sequential.m.for.table <- dat.social.type.token.sequential.m %>% 
    dplyr::filter(scoring == "raw") %>% 
    dplyr::select(-scoring) %>% 
    dplyr::group_by(population, myValence, myQueriedActionStatus, question) %>% 
    relabel_conds(wrap = FALSE) %>% 
    dplyr::summarize(
        N = n(),
        M = mean(rating),
        SE = se(rating),
        d = M/sd(rating),
        # That's correct only for raw ratings
        p = wilcox.p(rating, mu = 2.5),
        .groups = "drop") %>% 
    add_sig_stars(p) %>% 
    tidyr::pivot_wider(id_cols = c(myValence, myQueriedActionStatus, question),
                       names_from = population,
                       values_from = c("N", "M", "SE", "d", "p", "sig"),
                       names_vary = "slowest") %>%     
    relabel_questions(wrap = FALSE, sort = TRUE) %>% 
    dplyr::arrange(desc(question), myValence, myQueriedActionStatus) %>% 
    tidyr::unite(pack.col, question, myValence, sep = " - ") %>% 
    dplyr::mutate(is_above_chance = p_testable <= 0.05 & M_testable > 2.5,
                  is_below_chance = p_testable <= 0.05 & M_testable < 2.5)


dat.social.type.token.sequential.m.for.table %>% 
    dplyr::rename_with(rename_col_names) %>% 
    dplyr::select(-is_above_chance, -is_below_chance) %>% 
    kable.packed("pack.col", 
                 caption = "Descriptives for the raw ratings. The p value reflects a Wilcoxon test against the scale midpoint of 2.5. Lines in bold face and with a clear background reflect ratings that are significantly above 2.5 in the online sample. Lines in bold face, red font color and a gray background reflect ratings that are significantly below 2.5 in the online sample. Significance codes: *** $p \\leq .001$, ** $p \\leq .01$, * $p \\leq .05$, . $p \\leq .10$, ns = not significant.",
                 col.names = c("", rep(c("N", "M", "SE", "Cohen's d", "p", " "), 2)),
                 booktabs = TRUE,
                 escape = FALSE,
                 longtable = TRUE) %>% 
    kableExtra::add_header_above(header = c(" " = 1, "Students" = 6, "Testable" = 6), bold = TRUE) %>% 
    kableExtra::kable_styling(latex_options = "repeat_header") %>% 
#    kableExtra::row_spec(which(dat.social.type.token.sequential.m.for.table$is_above_chance), 
#                         bold = TRUE) %>%
#    kableExtra::row_spec(which(dat.social.type.token.sequential.m.for.table$is_below_chance), 
#                         bold = TRUE, color = "red", background = "gray!20") %>% 
    kableExtra::kable_classic_2()


```


`r clearpage()`


## Comparisons of the high and low type-frequency conditions against the single occurrence condition

I next turned to the question of whether type-frequency or token-frequency would affect acceptability and prevalence judgments, using the difference scores that compared each frequency condition to the single-occurrence condition.

### Difference scores

```{r difference-vs-single-raw-calculate}


dat.social.type.token.sequential.m.d.long.summary.vs.single  <-
    dat.social.type.token.sequential.m.d.long %>% 
    dplyr::filter(str_detect(contrast, "vs.single")) %>% 
    dplyr::group_by(population, scoring, question, myValence, contrast) %>% 
    dplyr::summarize(N = n(),
                     M = mean(d),
                     SE = se(d),
                     cohen.d = M/sd(d),
                     p = wilcox.p(d, 0), 
                     lr01.bic = lik.ratio(d, 0, correctionType = "BIC", verbose = FALSE),
                     lr01.aic = lik.ratio(d, 0, correctionType = "AIC", verbose = FALSE),
                     .groups = "drop") %>% 
    dplyr::group_by(population, scoring) %>% 
    dplyr::mutate(p_hb = p.adjust(p, method = "holm")) %>% 
    dplyr::ungroup() %>% 
    add_sig_stars(p_hb) %>% 
    dplyr::mutate(dplyr::across(starts_with("lr01."),
                                ~ dplyr::if_else(p_hb > .05,
                                                 .x, NA_real_))) %>% 
    dplyr::relocate(starts_with("lr01."), .after = "sig") 
    # tidyr::pivot_wider(id_cols = c(population, question, myValence, contrast),
    #                    names_from = scoring,
    #                    values_from = c(N, M, SE, cohen.d, p, p_hb),
    #                    names_vary = "slowest") %>% 
    # dplyr::select(-N_raw) %>% 


```

```{r difference-vs-single-raw-print, results = 'hide'}


dat.social.type.token.sequential.m.d.long.for.table <-
    dat.social.type.token.sequential.m.d.long.summary.vs.single %>% 
    dplyr::filter(scoring == "raw") %>% 
    dplyr::mutate(contrast = str_replace(contrast, "d\\.(.*)\\.vs.*", "\\1")) %>% 
    dplyr::mutate(question = str_replace_all(question, fixed ("."), " ")) %>% 
    relabel_conds(cond_col = contrast, wrap = FALSE) %>% 
    relabel_questions(wrap = FALSE, sort = TRUE) %>% 
    dplyr::arrange(question, population, myValence, contrast) %>% 
    tidyr::unite(pack.col, question, population,  sep = " - ") %>% 
    dplyr::mutate(significance_color = dplyr::case_when(
        (p <= .06 & p_hb > .05) ~ 1,
        p_hb <= .05 ~ 2,
        TRUE ~ 0)) %>% 
    dplyr::rename_with(rename_col_names) %>% 
    dplyr::rename(`Frequency Condition` = contrast) 
    
dat.social.type.token.sequential.m.d.long.for.table %>%  
    dplyr::select(-significance_color, -scoring) %>% 
    kable.packed("pack.col", 
                 caption = "Descriptives for the difference scores against the single occurrence condition ($\\frac{\\text{High Type-Frequency} - \\text{Single Occurrence}}{\\text{High Type-Frequency} + \\text{Single Occurrence}}$ and $\\frac{\\text{Low Type-Frequency} - \\text{Single Occurrence}}{\\text{Low Type-Frequency} + \\text{Single Occurrence}}$). The p-value reflects a Wilcoxon test against zero. $p_{\\scriptsize{hb}}$ reflects the Holm-Bonferroni corrected p-value. The correction was applied separately for each sample. The likelihood ratios $LR_{01,\\text{BIC}}$ and $LR_{01,\\text{AIC}}$ reflect likelihood ratios in favor of the null hypothesis after correction with the Bayesian Information Criterion and the Akaike Information Criterion, respectively. Significance codes: *** $p \\leq .001$, ** $p \\leq .01$, * $p \\leq .05$, . $p \\leq .10$, ns = not significant.",
                 #col.names = c("Valency", "Action Status", "N", rep(c("M", "SE", "Cohen's d", "p", "$p_{HB}$"), 2)),
                 escape = FALSE,
                 booktabs = TRUE,
                 longtable = TRUE) %>% 
    #kableExtra::add_header_above(header = c(" " = 3, "Binary ratings" = 5, "Raw ratings" = 5), bold = TRUE) %>%
    #kableExtra::add_header_above(header = c(" " = 3, "Raw ratings" = 6), bold = TRUE) %>% 
    kableExtra::kable_styling(latex_options = "repeat_header") %>% 
    # kableExtra::row_spec(which(dat.social.type.token.sequential.m.d.long.for.table$significance_color == 1), 
    #                      bold = TRUE, color = "orange") %>%
    # kableExtra::row_spec(which(dat.social.type.token.sequential.m.d.long.for.table$significance_color == 2),
    #                      bold = TRUE, color = "red", background = "gray!20") %>% 
    kableExtra::kable_classic_2()




```

```{r plot-difference-vs-single-raw, fig.cap = "Difference scores against the single occurrence condition ($\\frac{\\text{High Type-Frequency} - \\text{Single Occurrence}}{\\text{High Type-Frequency} + \\text{Single Occurrence}}$ and $\\frac{\\text{Low Type-Frequency} - \\text{Single Occurrence}}{\\text{Low Type-Frequency} + \\text{Single Occurrence}}$). The dot, error bars and violin represent the sample average, 95\\% bootstrap confidence intervals and the distribution of the individual responses, respectively. Open circles represent individual participants. Significance codes: *** $p \\leq .001$, ** $p \\leq .01$, * $p \\leq .05$, . $p \\leq .10$, ns = not significant.", fig.width=9.5, fig.height=15}

l_plot_difference_vs_single_raw <- levels2(dat.social.type.token.sequential.m$population) %>% 
    sort %>% 
    purrr::map(~ {
        
        
        plot_temp <- dat.social.type.token.sequential.m.d.long %>% 
            dplyr::filter(scoring == "raw", population == .x, str_detect(contrast, "vs.single")) %>% 
            dplyr::mutate(contrast = str_replace(contrast, "d\\.(.*)\\.vs.*", "\\1")) %>% 
            relabel_conds(cond_col = contrast) %>% 
            relabel_questions(wrap = TRUE, sort = TRUE) %>%     
            ggplot(aes (x = contrast, y = d)) %>% 
            violin_plot_template(yintercept = 0) +
            theme(axis.title.x = element_blank(),
                  axis.text.x = element_text(angle = 35, vjust = .5, hjust=.5)) + 
            labs (y = "Difference score (vs. single occurrence)",
                  title = str_to_title(.x)) + 
            facet_grid(question ~ myValence, scale = "free", labeller = labeller(.default = title_case_labeller))
        
        
        
        plot_temp  <- plot_temp  %>% 
            add_sig_labels(
                dat.social.type.token.sequential.m.d.long.summary.vs.single %>% 
                    dplyr::filter(scoring == "raw", population == .x, str_detect(contrast, "vs.single")) %>% 
                    relabel_questions(wrap = TRUE, sort = TRUE) %>%    
                    dplyr::mutate(contrast = str_replace(contrast, "d\\.(.*)\\.vs.*", "\\1")) %>% 
                    relabel_conds(cond_col = contrast)  %>% 
                    dplyr::select(question, myValence, contrast, sig))
        
        plot_temp
    })


ggpubr::ggarrange (plotlist = l_plot_difference_vs_single_raw,
    nrow = 2,
    labels = "auto",
    common.legend = TRUE,
    legend = "bottom")


```



The results are shown in Figures \ref{fig:plot-difference-vs-single-raw} and Table \ref{tab:difference-vs-single-raw-print2}. For first-party acceptability, ratings in the high type frequency condition differed reliably from those in the single occurrence condition, mainly for good and neutral actions. For bad actions, while the uncorrected effect was significant, it became marginal after correction in the testable sample, and non-significant in the student sample. In contrast, ratings in the low type frequency condition did not significantly differ from those in the single occurrence condition. First-party acceptability thus seems primarily driven by type rather than token frequency.

To provide evidence for the null hypothesis, I fit two linear models to the first-party acceptability difference scores: one representing the null hypothesis (with the mean fixed at 0) and one representing the alternative hypothesis (with the mean estimated from the data). I then calculated the likelihood of the data under each model, applied corrections for the numbers of parameters using the Bayesian Information Criterion (BIC) and the Akaike Information Criterion (AIC), and computed the likelihood ratio, with values greater than one indicating support for the null hypothesis. As shown in Table \ref{tab:difference-vs-single-raw-print2}, the first-party acceptability difference scores comparing the low type-frequency condition to the single-occurrence condition generally provided weak to moderate evidence in favor of the null hypothesis, suggesting again that first-party acceptability is primarily driven by type frequency rather than token frequency.

For both third-party acceptability and prevalence, ratings in both the high and low type frequency conditions differed from the single occurrence condition across all valence conditions, though the difference scores were roughly twice as large for the high type frequency condition compared to the low type frequency condition. Both type and token frequency thus affect these ratings, though I will demonstrate below that the effect of type frequency is substantially larger.


`r clearpage()`
### Confirmation with ordinal model

I confirmed these results with a series of CLMMs. For each domain (acceptability and prevalence), I included the fixed factor predictors Frequency Condition (High Type-Frequency vs. Single Occurrence and Low Type-Frequency vs. Single Occurrence) and Valence (with the reference level set to neutral), as well as a random slope for participants.


```{r clmm-vs-single-occurrence-prepare}

 
dat.social.type.token.sequential.for.clmm.vs.single.occurrence <- purrr::map_dfr(
    dat.social.type.token.sequential$myQueriedActionStatus %>% 
        unique %>% 
        grepv("single", ., invert = TRUE),
    function(freqCond) {
    
        dat.social.type.token.sequential %>% 
            dplyr::filter(scoring == "raw") %>% 
            dplyr::filter(myQueriedActionStatus %in% c("single", freqCond)) %>% 
            dplyr::mutate(myQueriedActionStatus = factor(myQueriedActionStatus,
                                                         levels = c("single", freqCond)),
                          myValence = factor(myValence, 
                                             levels = c("neutral", "bad", "good")),
                          question = factor(question,
                                            levels = c("first.party.acceptability", "third.party.acceptability", "prevalence")),
                          rating = factor(rating, ordered = TRUE)) %>% 
                dplyr::mutate(across(c(filename, myQueriedAction), factor)) %>% 
            dplyr::mutate(targetActionStatus = freqCond, .before = 1)
    })


```


```{r clmm-vs-single-occurrence-calculate}


clmm.social.type.token.sequential.vs.single.occurrence <- dat.social.type.token.sequential.for.clmm.vs.single.occurrence %>% 
    dplyr::group_by(question, targetActionStatus, population) %>% 
    dplyr::group_modify(~ {
        ordinal::clmm(rating ~ myValence * myQueriedActionStatus + 
                                       (1|filename),
                                   data = .x, 
                      control = clmm.control(
                          method = "nlminb",
                          trace = 0,
                          maxIter = 100, # Default 50
                          gradTol = 1e-7, # Default 1e-4
                          maxLineIter = 100, # Default 50
                          useMatrix = FALSE,
                          innerCtrl = "warnOnly",
                          checkRanef = "warn"
                      ),
                      Hess = TRUE,
                      link = "logit") %>% 
            parameters::model_parameters(.) %>% 
            # Maybe cleaner with parameters
            # coefficients(summary(tmp_model)) %>%
            #     as.data.frame %>%
            #     tibble::rownames_to_column("Parameter") %>%
            dplyr::filter(str_detect(Parameter, "\\|", negate = TRUE),
                          Effects == "fixed") 
            # dplyr::mutate(population = pop, 
            #               question = Q,
            #               .before = 1)
            # 
    })  



```



```{r clmm-vs-single-occurrence-print}


clmm.social.type.token.sequential.vs.single.occurrence %>% 
    #filter(p <=.05) %>% 
    relabel_questions(wrap = FALSE, sort = TRUE) %>%
    relabel_conds(cond_col = targetActionStatus, wrap = FALSE) %>% 
    relabel_terms() %>% 
    relabel_questions(wrap = FALSE, sort = TRUE) %>%
    add_sig_stars(p) %>% 
    dplyr::rename_with(rename_col_names) %>% 
    dplyr::mutate(
        targetActionStatus = str_c(targetActionStatus, " (vs. Single Occurrence)"),
        population = str_to_title(population)) %>% 
    dplyr::arrange(question, targetActionStatus, population) %>% 
    tidyr::unite(pack.col, question, targetActionStatus, population, sep = " - ") %>%
    dplyr::select(-Effects, -Group, -df_error) %>% 
    kable.packed("pack.col",
                 caption = "Results from a set of cumulative link mixed models, fitted separately for each sample (testable and students), domain (First-Party Acceptability, Third-Party Acceptability, and Prevalence), and frequency contrast (High Type-Frequency vs. Single Occurrence and Low Type-Frequency vs. Single Occurrence), with fixed factor predictors Frequency Condition and Valence, their interaction, and a random slope for participants. Significance codes: *** $p \\leq .001$, ** $p \\leq .01$, * $p \\leq .05$, . $p \\leq .10$, ns = not significant.",
                 #col.names = c("", rep(c("N", "M", "SE", "Cohen's d", "p"), 2)),
                 booktabs = TRUE,
                 longtable = TRUE) %>%
    #kableExtra::add_header_above(header = c(" " = 1, "Students" = 5, "Testable" = 5), bold = TRUE) %>%
    kableExtra::kable_styling(latex_options = "repeat_header") %>%
    # kableExtra::row_spec(which(dat.social.type.token.sequential.m.for.table$is_below_chance),
    #                      bold = TRUE, color = "red", background = "gray!20") %>%
    kableExtra::kable_classic_2() 
```

The results are shown in Table \ref{tab:clmm-vs-single-occurrence-print}. For first-party acceptability, ratings differed significantly from the single-occurrence condition only in the high type-frequency condition, confirming that first-party acceptability is primarily driven by type frequency. (In the student sample, some additional interactions emerged, but these could not be replicated in the testable sample.)


For third-party acceptability and prevalence, both the high and low type-frequency conditions differed from the single-occurrence condition (except for the low type-frequency condition in third-party acceptability ratings within the student sample). However, the parameter estimates were approximately two to three times greater for the high type-frequency condition than for the low type-frequency condition.

For prevalence, the effect of high type-frequency was reduced for good and bad actions relative to neutral actions, while the effect of token frequency was slightly stronger for bad actions in the testable sample.


## Comparisons of the high and low type-frequency conditions

I now turn to the question of whether type and token frequency affect ratings differentially. I first address this question using difference scores, and then confirm these results using an CLMM. 

### Difference scores


```{r difference-high-vs-low-type-frequency-calculate}


dat.social.type.token.sequential.m.d.long.summary.high.vs.low.tf <- dat.social.type.token.sequential.m.d.long %>% 
    dplyr::filter(!str_detect(contrast, "vs.single")) %>% 
    dplyr::mutate(contrast = str_replace(contrast, "d\\.(.*)\\.vs.*", "\\1")) %>% 
    dplyr::group_by(population, scoring, question, contrast, myValence) %>% 
    dplyr::summarize(N = n(),
                     M = mean(d),
                     SE = se(d),
                     cohen.d = M/sd(d),
                     p = wilcox.p(d, 0), 
                     .groups = "drop") %>% 
    dplyr::group_by(population, scoring) %>% 
    dplyr::mutate(p_hb = p.adjust(p, method = "holm")) %>% 
    dplyr::ungroup()  %>% 
    add_sig_stars(p_hb)
```
    
    
```{r difference-high-vs-low-type-frequency-print, results = 'hide'}

dat.social.type.token.sequential.m.d.long.summary.high.vs.low.tf %>% 
    dplyr::filter(scoring == "raw") %>% 
    relabel_questions(wrap = FALSE, sort = TRUE) %>% 
    dplyr::rename_with(rename_col_names) %>% 
    dplyr::mutate(
        population = str_to_title(population)) %>% 
    dplyr::arrange(question, population) %>% 
    dplyr::select(-scoring, -contrast) %>% 
    tidyr::unite(pack.col, question, population, sep = " - ") %>% 
    kable.packed("pack.col", 
                 caption = "Descriptive statistics for the difference scores comparing the High and Low Type-Frequency Conditions ($\\frac{\\text{High Type-Frequency} - \\text{Low Type-Frequency}}{\\text{High Type-Frequency} + \\text{Low Type-Frequency}}$). The p-value reflects a Wilcoxon test against zero. $p_{\\scriptsize{hb}}$ reflects the Holm-Bonferroni corrected p-value. The correction was applied separately for each sample. Significance codes: *** $p \\leq .001$, ** $p \\leq .01$, * $p \\leq .05$, . $p \\leq .10$, ns = not significant.",
                 #col.names = c("Valency", "N", rep(c("M", "SE", "Cohen's d", "p", "$p_{HB}$", ""), 1)),
                 booktabs = TRUE,
                 escape = FALSE,
                 longtable = TRUE) %>% 
    #kableExtra::add_header_above(header = c(" " = 2, "Binary ratings" = 5, "Raw ratings" = 5), bold = TRUE) %>% 
    #kableExtra::add_header_above(header = c(" " = 2, "Raw ratings" = 6), bold = TRUE) %>% 
    kableExtra::kable_styling(latex_options = "repeat_header") %>% 
    kableExtra::kable_classic_2()
    
```

```{r plot-difference-high-vs-low-type-frequency-raw, fig.cap = "Difference scores comparing the High and Low Type-Frequency Conditions ($\\frac{\\text{High Type-Frequency} - \\text{Low Type-Frequency}}{\\text{High Type-Frequency} + \\text{Low Type-Frequency}}$). The dots, error bars and violin represent the sample average, 95\\% bootstrap confidence intervals and the distribution of the individual responses, respectively. Open circles represent individual participants. Significance codes: *** $p \\leq .001$, ** $p \\leq .01$, * $p \\leq .05$, . $p \\leq .10$, ns = not significant.", message=TRUE, warning=TRUE}

plot_difference_high_vs_low_type_frequency_raw <- dat.social.type.token.sequential.m.d.long %>% 
    dplyr::filter(scoring == "raw") %>% 
    dplyr::filter(!str_detect(contrast, "vs.single")) %>% 
    relabel_questions(wrap = FALSE, sort = TRUE) %>% 
    ggplot(aes(x = myValence, y = d)) %>% 
    violin_plot_template(yintercept = 0) +
    theme (axis.title.x = element_blank(),
           axis.text.x = element_text(angle = 35, vjust = .5, hjust=.5)) +
    ylab ("Difference score (High vs. low TF)") + 
    #scale_x_discrete(labels = c("Pre-segmented", "Continuous (1)", "Continuous (2)"))
    facet_grid(population ~ question, scales = "free")

plot_difference_high_vs_low_type_frequency_raw <- 
    plot_difference_high_vs_low_type_frequency_raw %>% 
    add_sig_labels(
        dat.sig.summary = dat.social.type.token.sequential.m.d.long.summary.high.vs.low.tf %>% 
            dplyr::filter(scoring == "raw") %>%
            relabel_questions(wrap = FALSE, sort = TRUE) %>% 
            dplyr::select(population, question, myValence, sig))
 
plot_difference_high_vs_low_type_frequency_raw
```

The results are shown in Figure \ref{fig:plot-difference-high-vs-low-type-frequency-raw} and Table \ref{tab:difference-high-vs-low-type-frequency-print1}. For first-party acceptability, the difference scores were significantly greater than zero for good and neutral actions in the testable sample, and for neutral actions only in the student sample. First-party acceptability ratings thus increase when the type frequency of an action is increased, even when the frequency of occurrence is held constant.

For third-party acceptability and prevalence, the difference scores were significantly greater than zero for all valence conditions and samples, showing again that type-frequency has an effect over and above frequency of occurrence. 



`r clearpage()`

### Confirmation with ordinal model

I confirmed these results with a series of CLMMs. For each domain, I fitted a model including the fixed factor predictors Frequency Condition (High Type-Frequency vs. Low Type-Frequency) and Valence, with the reference level set to neutral.


```{r clmm-high-vs-low-type-frequency-prepare}

 
dat.social.type.token.sequential.for.clmm.high.vs.low.type.frequency <- 
    dat.social.type.token.sequential %>% 
    dplyr::filter(scoring == "raw") %>% 
    dplyr::filter(myQueriedActionStatus %in% 
                      (dat.social.type.token.sequential$myQueriedActionStatus %>% 
                      unique %>% 
                      grepv("single", ., invert = TRUE))) %>% 
    dplyr::mutate(myQueriedActionStatus = factor(myQueriedActionStatus,
                                                 levels =                                                      dat.social.type.token.sequential$myQueriedActionStatus %>% 
                                                     unique %>% 
                                                     grepv("single", ., invert = TRUE) %>% 
                                                     rev),
                  myValence = factor(myValence, 
                                     levels = c("neutral", "bad", "good")),
                  question = factor(question,
                                    levels = c("first.party.acceptability", "third.party.acceptability", "prevalence")),
                  rating = factor(rating, ordered = TRUE)) %>% 
    dplyr::mutate(across(c(filename, myQueriedAction), factor))

```


```{r clmm-high-vs-low-type-frequency-calculate}


clmm.social.type.token.sequential.for.clmm.high.vs.low.type.frequency <- dat.social.type.token.sequential.for.clmm.high.vs.low.type.frequency %>% 
    dplyr::group_by(question, population) %>% 
    dplyr::group_modify(~ {
        ordinal::clmm(rating ~ myValence * myQueriedActionStatus + 
                          (1|filename), 
                      data = .x, 
                      control = clmm.control(
                          #method = "nlminb",
                          method = "ucminf", 
                          trace = 0,
                          maxIter = 100, # Default 50
                          gradTol = 1e-4, # Default 1e-4
                          maxLineIter = 100, # Default 50
                          useMatrix = FALSE,
                          innerCtrl = "warnOnly",
                          checkRanef = "warn"
                      ),
                      Hess = TRUE,
                      link = "logit") %>% 
            parameters::model_parameters(.) %>% 
            # Maybe cleaner with parameters
            # coefficients(summary(tmp_model)) %>%
            #     as.data.frame %>%
            #     tibble::rownames_to_column("Parameter") %>%
            dplyr::filter(str_detect(Parameter, "\\|", negate = TRUE),
                          Effects == "fixed") 
        # dplyr::mutate(population = pop, 
        #               question = Q,
        #               .before = 1)
        # 
    })  

 


```



```{r clmm-high-vs-low-type-frequency-print}

clmm.social.type.token.sequential.for.clmm.high.vs.low.type.frequency %>% 
    relabel_questions(wrap = FALSE, sort = FALSE) %>%
    relabel_terms() %>% 
    add_sig_stars(p) %>% 
    dplyr::rename_with(rename_col_names) %>% 
    dplyr::mutate(
        population = str_to_title(population)) %>% 
    dplyr::arrange(question, population) %>% 
    tidyr::unite(pack.col, question,  population, sep = " - ") %>%
    dplyr::select(-Effects, -Group, -df_error) %>% 
    kable.packed("pack.col",
                 caption = "Results from a set of cumulative link mixed models, contrasting the High Type-Frequency condition with the Low Type-Frequency condition. Models were fitted separately for each sample (online or student) and domain (Prevalence, First-Party Acceptability, and Third-Party Acceptability), with fixed factor predictors Valence, Frequency Condition, and their interaction, as well as a random slope for participants. Significance codes: *** $p \\leq .001$, ** $p \\leq .01$, * $p \\leq .05$, . $p \\leq .10$, ns = not significant.",
                 #col.names = c("", rep(c("N", "M", "SE", "Cohen's d", "p"), 2)),
                 booktabs = TRUE,
                 longtable = TRUE) %>%
    #kableExtra::add_header_above(header = c(" " = 1, "Students" = 5, "Testable" = 5), bold = TRUE) %>%
    kableExtra::kable_styling(latex_options = "repeat_header") %>%
    # kableExtra::row_spec(which(dat.social.type.token.sequential.m.for.table$is_below_chance),
    #                      bold = TRUE, color = "red", background = "gray!20") %>%
    kableExtra::kable_classic_2()

```

The results are shown in Table \ref{tab:clmm-high-vs-low-type-frequency-print}. In all domains and samples, ratings in the high type-frequency condition were higher than those in the low type-frequency condition.

We also observed main effects of valence, showing that good actions were rated higher than neutral ones, while neutral ones were rated higher than bad ones (except for prevalence ratings, where the latter two conditions did not differ).
These results thus mirror those of the difference scores above."

`r clearpage()`

## Alternative analyses

In  SI \ref{app:alternative-analyses}, I report two alternative sets of analyses in addition to the difference score analyses and the CLMMs. First, I fit a series of generalized linear mixed models (GLMMs) using binarized responses, where ratings of 1 or 2 were coded as "unacceptable" and ratings of 3 or 4 as "acceptable." These models compared both the High Type-Frequency (TF) and Low TF conditions to the Single Occurrence condition, as well as directly compared the High TF and Low TF conditions. Second, I conducted a set of equivalent mixed ANOVAs to assess the robustness of the results.

The results were largely consistent with those of the main analyses, with one exception. In the GLMMs for the testable sample, ratings in the High Type-Frequency condition were neither significantly greater than those in the Low Type-Frequency condition nor than those in the Single Occurrence condition. It is unclear why these results diverge from those based on the difference scores, CLMMs, and ANOVAs.

`r clearpage()`

# Appendix
# Descriptives 
## Raw ratings

```{r print-descriptives-ratings-raw2, ref.label = 'print-descriptives-ratings-raw', echo = FALSE, results = 'markup'}

```


For bad actions, *prevalence ratings* were above the midpoint of 2.5 for low and high type-frequency actions, and below the midpoint for single occurrence actions (though these differences did not reach significance for the student population). For neutral actions, the results were similar, except that single occurrence actions were only marginally below the midpoint in the online sample. In contrast, for good actions, prevalence ratings were above the midpoint in all frequency conditions. 

For bad actions, *first-party acceptability* ratings were below the midpoint in all frequency conditions. In contrast, for neutral and good actions, the ratings were above the midpoint (though these effects did not reach significance in the student sample.)

For bad actions, *first-party acceptability* were above the midpoint for high type-frequency actions, below the midpoint for single occurrence actions and did not differ from the midpoint for low type-frequency actions. For good actions, ratings were above the midpoint for all frequency conditions. 



```{r clmm-raw-effects-of-valency2, ref.label = 'clmm-raw-effects-of-valency', echo = FALSE, results = 'markup'}
```

As shown in Table \ref{tab:clmm-raw-effects-of-valency2}, acceptability ratings were higher for good actions than for neutral actions, and for neutral actions than for bad actions.



`r clearpage()`

## Comparisons of the high and low type-frequency conditions against the single occurrence condition


```{r difference-vs-single-raw-print2, ref.label = 'difference-vs-single-raw-print', echo = FALSE, results = 'markup'}
```


`r clearpage()`

## Comparisons of the high and low type-frequency conditions

```{r difference-high-vs-low-type-frequency-print2, ref.label = 'difference-high-vs-low-type-frequency-print', echo = FALSE, results = 'markup'}
```



`r clearpage()`

# Alternative analyses {#app:alternative-analyses}



## Comparisons of the high and low type-frequency conditions against the single occurrence condition
### GLMMs

I analyzed the results using a series of generalized linear mixed models (GLMMs), in which responses were converted to binary outcomes on each trial: ratings of 1 or 2 were coded as "unacceptable," and ratings of 3 or 4 as "acceptable." The models included fixed factor predictors for Frequency Condition and Valence, their interaction, and a random slope for participants. The results are shown in Table \ref{tab:glmm-vs-single-occurrence-print}.



```{r glmm-vs-single-occurrence-prepare}

 
dat.social.type.token.sequential.for.glmm.vs.single.occurrence <- purrr::map_dfr(
    dat.social.type.token.sequential$myQueriedActionStatus %>% 
        unique %>% 
        grepv("single", ., invert = TRUE),
    function(freqCond) {
    
        dat.social.type.token.sequential %>% 
            dplyr::filter(scoring == "bin") %>% 
            dplyr::filter(myQueriedActionStatus %in% c("single", freqCond)) %>% 
            dplyr::mutate(myQueriedActionStatus = factor(myQueriedActionStatus,
                                                         levels = c("single", freqCond)),
                          myValence = factor(myValence, 
                                             levels = c("neutral", "bad", "good")),
                          question = factor(question,
                                            levels = c("first.party.acceptability", "third.party.acceptability", "prevalence"))) %>% 
                dplyr::mutate(across(c(filename, myQueriedAction), factor)) %>% 
            dplyr::mutate(targetActionStatus = freqCond, .before = 1)
    })


```


```{r glmm-vs-single-occurrence-calculate}


glmm.social.type.token.sequential.vs.single.occurrence <- dat.social.type.token.sequential.for.glmm.vs.single.occurrence %>% 
    dplyr::group_by(question, targetActionStatus, population) %>% 
    dplyr::group_modify(~ {
        lme4::glmer(
            rating ~ myValence * myQueriedActionStatus + 
                (1|filename) + (1|myQueriedAction), 
            control=glmerControl(optimizer="bobyqa"),
            family="binomial",
            data = .x) %>% 
            parameters::model_parameters(.) %>% 
            # Maybe cleaner with parameters
            # coefficients(summary(tmp_model)) %>%
            #     as.data.frame %>%
            #     tibble::rownames_to_column("Parameter") %>%
            dplyr::filter(Effects == "fixed") 
    })  



```


```{r glmm-vs-single-occurrence-print}

glmm.social.type.token.sequential.vs.single.occurrence %>% 
    relabel_questions(wrap = FALSE, sort = FALSE) %>%
    relabel_conds(cond_col = targetActionStatus, wrap = FALSE) %>% 
    relabel_terms() %>% 
    add_sig_stars(p) %>% 
    dplyr::rename_with(rename_col_names) %>% 
    dplyr::mutate(
        targetActionStatus = str_c(targetActionStatus, " (vs. Single Occurrence)"),
        population = str_to_title(population)) %>% 
    dplyr::arrange(question, targetActionStatus, population) %>% 
    tidyr::unite(pack.col, question, targetActionStatus, population, sep = " - ") %>%
    dplyr::select(-Effects, -Group, -df_error) %>% 
    kable.packed("pack.col",
                 caption = "Results from a set of generalized linear mixed models, fitted to the binarized trial-by-trial data, separately for each sample (online or student), domain (First-Party Acceptability, Third-Party Acceptability, and Prevalence), and frequency contrast (High Type-Frequency vs. Single Occurrence and Low Type-Frequency vs. Single Occurrence). The models included the fixed factor predictors Valence and Frequency Condition, their interaction, and random slopes for participants and actions. Significance codes: *** $p \\leq .001$, ** $p \\leq .01$, * $p \\leq .05$, . $p \\leq .10$, ns = not significant.",
                 #col.names = c("", rep(c("N", "M", "SE", "Cohen's d", "p"), 2)),
                 booktabs = TRUE,
                 longtable = TRUE) %>%
    #kableExtra::add_header_above(header = c(" " = 1, "Students" = 5, "Testable" = 5), bold = TRUE) %>%
    kableExtra::kable_styling(latex_options = "repeat_header") %>%
    # kableExtra::row_spec(which(dat.social.type.token.sequential.m.for.table$is_below_chance),
    #                      bold = TRUE, color = "red", background = "gray!20") %>%
    kableExtra::kable_classic_2()

```

When comparing the High Type-Frequency and Low Type-Frequency conditions to the Single Occurrence condition, the results of the GLMMs were similar to those of the CLMMs. However, for first-party acceptability in the testable sample, the effect of Frequency Condition was not significant in the High Type-Frequency condition.  In the student sample, and as in the CLMMs, ratings differed from the Single Occurrence condition only in the High Type-Frequency condition, and not in the Low Type-Frequency condition.

For third-party acceptability and prevalence, both the High and Low Type-Frequency conditions differed significantly from the Single Occurrence condition, although parameter estimates were approximately two to three times larger in the High Type-Frequency condition.

I also observed main effects of valence, indicating that good actions were rated higher than neutral ones, and neutral actions higher than bad ones—except in prevalence ratings, where neutral and bad actions did not differ.


### ANOVAs
The results were also analyzed using a series of mixed ANOVAs, with Frequency Condition (High Type-Frequency vs. Single Occurrence and Low Type-Frequency vs. Single Occurrence) as a within-participant factor, and Valence as a between-participant factor, including their interaction.


```{r sw-vs-single-occurrence-calculate, eval = FALSE}

# We could run shapiro wilks tests, but since we don't really care about ANOVAs, we don't

#get.lambda.trans 

sw.social.type.token.sequential.vs.single.occurrence <-  purrr::map_dfr(
    dat.social.type.token.sequential.m$myQueriedActionStatus %>% 
        unique %>% 
        grepv("single", ., invert = TRUE),
    function(freqCond) {
        
        dat.social.type.token.sequential.m %>% 
            dplyr::filter(scoring == "raw") %>% 
            dplyr::filter(myQueriedActionStatus %in% c("single", freqCond)) %>% 
            dplyr::mutate(myQueriedActionStatus = factor(myQueriedActionStatus,
                                                         levels = c("single", freqCond)),
                          myValence = factor(myValence, 
                                             levels = c("neutral", "bad", "good")),
                          question = factor(question,
                                            levels = c("first.party.acceptability", "third.party.acceptability", "prevalence"))) %>% 
            dplyr::mutate(across(c(filename), factor)) %>% 
            dplyr::mutate(targetActionStatus = freqCond, .before = 1)
    }) %>% 
    group_by(question, targetActionStatus, population) %>%
    group_modify(~ {
        
        tryCatch({
            calculate.shapiro.wilk.test.for.cells(
                .x,
                c("myValence",
                  "myQueriedActionStatus"),
                "rating")
        }, error = function(e) {
            message("Error in group: ", paste(unique(.x$question), unique(.x$targetActionStatus), unique(.x$population), collapse = " / "))
            return(tibble())
        })
    })


```


```{r anova-vs-single-occurrence-calculate}

aov.social.type.token.sequential.vs.single.occurrence <-  purrr::map_dfr(
    dat.social.type.token.sequential.m$myQueriedActionStatus %>% 
        unique %>% 
        grepv("single", ., invert = TRUE),
    function(freqCond) {
        
        dat.social.type.token.sequential.m %>% 
            dplyr::filter(scoring == "raw") %>% 
            dplyr::filter(myQueriedActionStatus %in% c("single", freqCond)) %>% 
            dplyr::mutate(myQueriedActionStatus = factor(myQueriedActionStatus,
                                                         levels = c("single", freqCond)),
                          myValence = factor(myValence, 
                                             levels = c("neutral", "bad", "good")),
                          question = factor(question,
                                            levels = c("first.party.acceptability", "third.party.acceptability", "prevalence"))) %>% 
            dplyr::mutate(across(c(filename), factor)) %>% 
            dplyr::mutate(targetActionStatus = freqCond, .before = 1)
    }) %>% 
    group_by(question, targetActionStatus, population) %>%
    group_modify(~ {
        
        tryCatch({
            afex::aov_ez(
                id = "filename",
                dv = "rating",
                data = .x,
                within = c("myQueriedActionStatus"),
                between = c("myValence"),
                return = "afex_aov" 
            ) %>% 
                afex::nice() 
                #parameters::model_parameters(., eta_squared = "ges")
        }, error = function(e) {
            message("Error in group: ", paste(unique(.x$question), unique(.x$targetActionStatus), unique(.x$population), collapse = " / "))
            return(tibble())
        })
    })


```


```{r anova-vs-single-occurrence-print}

aov.social.type.token.sequential.vs.single.occurrence %>% 
    relabel_questions(wrap = FALSE, sort = TRUE) %>%
    relabel_conds(cond_col = targetActionStatus, wrap = FALSE) %>% 
    relabel_terms(type = "aov", term_col = Effect) %>% 
    add_sig_stars(p.value) %>% 
    dplyr::rename_with(rename_col_names) %>% 
    dplyr::mutate(
        targetActionStatus = str_c(targetActionStatus, " (vs. Single Occurrence)"),
        population = str_to_title(population)) %>% 
    tidyr::unite(pack.col, question, targetActionStatus, population, sep = " - ") %>%
    abbreviate_cols() %>% 
    kable.packed("pack.col",
                 caption = "Results from a set of mixed ANOVAs, fitted separately for each sample (online or student), domain (First-Party Acceptability, Third-Party Acceptability, and Prevalence), and frequency contrast (High Type-Frequency vs. Single Occurrence and Low Type-Frequency vs. Single Occurrence). The models included Valence (between-subjects) and Frequency Condition (within-subjects) as fixed factors, along with their interaction. Significance codes: *** $p \\leq .001$, ** $p \\leq .01$, * $p \\leq .05$, . $p \\leq .10$, ns = not significant.",
                 #col.names = c("", rep(c("N", "M", "SE", "Cohen's d", "p"), 2)),
                 booktabs = TRUE,
                 longtable = TRUE) %>%
    #kableExtra::add_header_above(header = c(" " = 1, "Students" = 5, "Testable" = 5), bold = TRUE) %>%
    kableExtra::kable_styling(latex_options = "repeat_header") %>%
    # kableExtra::row_spec(which(dat.social.type.token.sequential.m.for.table$is_below_chance),
    #                      bold = TRUE, color = "red", background = "gray!20") %>%
    kableExtra::kable_classic_2()

```


As shown in \ref{tab:anova-vs-single-occurrence-print}, the results of these ANOVAs were similar to those from the CLMMs. As in the CLMMs, there was a main effect of Frequency Condition. However, the effect was also significant for the Low Type-Frequency condition, though the effect size was approximately six to eight times greater for the High Type-Frequency condition. 

There was also a main effect of Valence, as well as a significant interaction between Valence and Frequency Condition across all domains and frequency contrasts.


## Comparisons of the high and low type-frequency conditions

### GLMMs

I also analyzed the results using a series of generalized linear mixed models (GLMMs), in which responses were converted to binary outcomes on each trial: ratings of 1 or 2 were coded as "unacceptable," and ratings of 3 or 4 as "acceptable." The models included fixed factor predictors for Frequency Condition and Valence, their interaction, and a random slope for participants and actions.

When comparing the High Type-Frequency condition to the Low Type-Frequency condition, the results of the GLMMs were broadly similar to those obtained from the CLMMs and the mixed ANOVAs, with one exception. For first-party acceptability, the effect of Frequency Condition was not significant in the testable sample and only marginal in the student sample. It is unclear why this analysis diverges from the results of both the CLMMs and the ANOVAs (see below).

For third-party acceptability and prevalence, the effect of Frequency Condition was significant in both samples.

I also observed main effects of Valence, indicating that good actions were rated higher than neutral ones, and neutral actions higher than bad ones, except in prevalence ratings, where neutral and bad actions did not differ.


```{r glmm-high-vs-low-type-frequency-prepare}

 
dat.social.type.token.sequential.for.glmm.high.vs.low.type.frequency <- 
    dat.social.type.token.sequential %>% 
    dplyr::filter(scoring == "bin") %>% 
    dplyr::filter(myQueriedActionStatus %in% 
                      (dat.social.type.token.sequential$myQueriedActionStatus %>% 
                      unique %>% 
                      grepv("single", ., invert = TRUE))) %>% 
    dplyr::mutate(myQueriedActionStatus = factor(myQueriedActionStatus,
                                                 levels =                                                      dat.social.type.token.sequential$myQueriedActionStatus %>% 
                                                     unique %>% 
                                                     grepv("single", ., invert = TRUE) %>% 
                                                     rev),
                  myValence = factor(myValence, 
                                     levels = c("neutral", "bad", "good")),
                  question = factor(question,
                                    levels = c("first.party.acceptability", "third.party.acceptability", "prevalence"))) %>% 
    dplyr::mutate(across(c(filename, myQueriedAction), factor))

```


```{r glmm-high-vs-low-type-frequency-calculate}

glmm.social.type.token.sequential.for.glmm.high.vs.low.type.frequency <- dat.social.type.token.sequential.for.glmm.high.vs.low.type.frequency  %>% 
    dplyr::group_by(question, population) %>% 
    dplyr::group_modify(~ {
        lme4::glmer(
            rating ~ myValence * myQueriedActionStatus + 
                (1|filename) + (1|myQueriedAction), 
            control=glmerControl(optimizer="bobyqa"),
            family="binomial",
            data = .x) %>% 
            parameters::model_parameters(.) %>% 
            # Maybe cleaner with parameters
            # coefficients(summary(tmp_model)) %>%
            #     as.data.frame %>%
            #     tibble::rownames_to_column("Parameter") %>%
            dplyr::filter(Effects == "fixed") 
    })  

 


```

```{r glmm-high-vs-low-type-frequency-print}

glmm.social.type.token.sequential.for.glmm.high.vs.low.type.frequency %>% 
    relabel_questions(wrap = FALSE, sort = FALSE) %>%
    relabel_terms() %>% 
    add_sig_stars(p) %>% 
    dplyr::rename_with(rename_col_names) %>% 
    dplyr::mutate(
        population = str_to_title(population)) %>% 
    dplyr::arrange(question, population) %>% 
    tidyr::unite(pack.col, question, population, sep = " - ") %>%
    dplyr::select(-Effects, -Group, -df_error) %>% 
    kable.packed("pack.col",
                 caption = "Results from a set of generalized linear mixed models using binarized data (ratings of 1–2 coded as unacceptable, and 3–4 as acceptable), comparing the High Type-Frequency condition to the Low Type-Frequency condition. Models were fitted separately for each sample (online or student) and domain (First-Party Acceptability and Third-Party Acceptability), with fixed factor predictors Valence and Frequency Condition, their interaction, and a random slope for participants. Significance codes: *** $p \\leq .001$, ** $p \\leq .01$, * $p \\leq .05$, . $p \\leq .10$, ns = not significant.",
                 #col.names = c("", rep(c("N", "M", "SE", "Cohen's d", "p"), 2)),
                 booktabs = TRUE,
                 longtable = TRUE) %>%
    #kableExtra::add_header_above(header = c(" " = 1, "Students" = 5, "Testable" = 5), bold = TRUE) %>%
    kableExtra::kable_styling(latex_options = "repeat_header") %>%
    # kableExtra::row_spec(which(dat.social.type.token.sequential.m.for.table$is_below_chance),
    #                      bold = TRUE, color = "red", background = "gray!20") %>%
    kableExtra::kable_classic_2()

```

### ANOVAs

```{r anova-high-vs-low-type-frequency-calculate}

aov.social.type.token.sequential.high.vs.low.type.frequency <- 
    dat.social.type.token.sequential.m %>% 
    dplyr::filter(scoring == "raw") %>% 
    dplyr::filter(myQueriedActionStatus %in% 
                      (dat.social.type.token.sequential$myQueriedActionStatus %>% 
                      unique %>% 
                      grepv("single", ., invert = TRUE))) %>% 
    dplyr::mutate(myQueriedActionStatus = factor(myQueriedActionStatus,
                                                 levels =                                                      dat.social.type.token.sequential$myQueriedActionStatus %>% 
                                                     unique %>% 
                                                     grepv("single", ., invert = TRUE) %>% 
                                                     rev),
                  myValence = factor(myValence, 
                                     levels = c("neutral", "bad", "good")),
                  question = factor(question,
                                    levels = c("first.party.acceptability", "third.party.acceptability", "prevalence"))) %>% 
    dplyr::mutate(across(c(filename), factor)) %>% 
    group_by(question, population) %>%
    group_modify(~ {

        tryCatch({
            afex::aov_ez(
                id = "filename",
                dv = "rating",
                data = .x,
                within = c("myQueriedActionStatus"),
                between = c("myValence"),
                return = "afex_aov"
            ) %>%
                afex::nice() 
                #parameters::model_parameters(., eta_squared = "ges")
        }, error = function(e) {
            message("Error in group: ", paste(unique(.x$question), unique(.x$targetActionStatus), unique(.x$population), collapse = " / "))
            return(tibble())
        })
    })


```

```{r anova-high-vs-low-type-frequency-print}


aov.social.type.token.sequential.high.vs.low.type.frequency %>% 
    relabel_questions(wrap = FALSE, sort = FALSE) %>%
    relabel_terms(type = "aov", term_col = Effect) %>% 
    add_sig_stars(p.value) %>% 
    dplyr::rename_with(rename_col_names) %>% 
    dplyr::mutate(
        population = str_to_title(population)) %>% 
    dplyr::arrange(question, population) %>% 
    tidyr::unite(pack.col, question, population, sep = " - ") %>%
    abbreviate_cols() %>% 
    kable.packed("pack.col",
                 caption = "Results from a set of mixed ANOVAs comparing the High Type-Frequency condition to the Low Type-Frequency condition, fitted separately for each sample (online or student) and domain (First-Party Acceptability and Third-Party Acceptability). The models included Valence (between-subjects) and Frequency Condition (within-subjects) as fixed factors, along with their interaction. Significance codes: *** $p \\leq .001$, ** $p \\leq .01$, * $p \\leq .05$, . $p \\leq .10$, ns = not significant.",
                 #col.names = c("", rep(c("N", "M", "SE", "Cohen's d", "p"), 2)),
                 booktabs = TRUE,
                 longtable = TRUE) %>%
    #kableExtra::add_header_above(header = c(" " = 1, "Students" = 5, "Testable" = 5), bold = TRUE) %>%
    kableExtra::kable_styling(latex_options = c(#"striped",
                                                "scale_down",
                                                "hold_position",
                                                "repeat_header")) %>%
    # kableExtra::row_spec(which(dat.social.type.token.sequential.m.for.table$is_below_chance),
    #                      bold = TRUE, color = "red", background = "gray!20") %>%
    kableExtra::kable_classic_2()

```

As shown in Table \ref{tab:anova-high-vs-low-type-frequency-print}, results from a set of mixed ANOVAs comparing the High Type-Frequency condition to the Low Type-Frequency condition, fitted separately for each sample (online or student) and domain (First-Party Acceptability and Third-Party Acceptability), were similar to those of the CLMMs reported above. The models included Valence (between-subjects) and Frequency Condition (within-subjects) as fixed factors, along with their interaction. There were significant main effects of Frequency Condition and Valence across all domains and samples, and the interaction between them was significant in most conditions.

`r clearpage()`


```{r xxx}
knit_exit()
```


# Unused 
## Power analysis (REMOVE IN PAPER)
We use the SIMR package for power analysis [@Green2016]. 

See https://besjournals.onlinelibrary.wiley.com/doi/full/10.1111/2041-210X.12504 for usage of extend and powerCurve

```{r city-power-prevalence, eval = FALSE}
library (simr)


lmer.social.type.token.sequential.bin.acceptability.other.pwr.numberCond <- 
    powerSim (
        lmer.social.type.token.sequential.bin.acceptability.other.1,
        fcompare(~ myQueriedActionStatus),
        nsim = 10)
# 75.20% power with "bad"" as base-level for valency
# 85% power with "bad"" as base-level for valency

powerSim (
    lmer.social.type.token.sequential.bin.acceptability.other.no.single.1,
    fcompare(~ myQueriedActionStatus),
    nsim = 10)


#lastResult()$errors 
#valency:genderMatch
#questionType:genderMatch


# https://stackoverflow.com/questions/57093394/confirm-succesful-extend-using-simr-package-in-r
# lmer.social.type.tokens.prevalence.bin.city.5.extended <- 
#     extend (
#         lmer.social.type.tokens.prevalence.bin.city.5,
#         #within = "questionType + numberCond + valency + genderMatch + scenarioID",
#         within = "questionType + scenarioID",
#         n = 100)

#getData (social.type.token.females.prevalence.bin.lmer5.extended) %>% 
#    nrow()

# pc <- powerCurve2 (
#     lmer.social.type.tokens.prevalence.bin.city.5.extended,
#     "questionType:valency:genderMatch",
#     #within = "questionType + numberCond + valency + genderMatch + scenarioID",
#     within = "questionType + scenarioID",
#     breaks=seq(50, 100, 10),
#     nsim = 100)

#print(pc)
# 84% power from 70 participants with neutral as base-level for bad

#plot(pc) 


```


`r clearpage()`

## Correlations

```{r correlations-vs-single-calculate}


l.dat.social.type.token.sequential.corr.vs.single <- dat.social.type.token.sequential.m.wide %>% 
    dplyr::group_by(myValence, Machiavellianism, Narcissism, Psychopathy) %>% 
    dplyr::select(matches(fixed ("vs.single_"))) %>% 
    dplyr::select(-ends_with(fixed ("_bin"))) %>%
    dplyr::rename_with(~ .x %>% 
                           str_replace("d\\.(.*)\\.vs.single", "\\1") %>% 
                           str_remove (fixed ("_raw")) %>% 
                           str_replace_all ("_", " - ") %>% 
                           str_replace_all (fixed ("."), " ") %>% 
                           str_wrap(width = 15)) %>% 
    dplyr::group_by(myValence) %>% 
    dplyr::group_split () %>% 
    map (~ list (myValence = levels2 (.$myValence),
                 corrmat = .x %>% 
                     ungroup %>% 
                     dplyr::select(-c(myValence)) %>% 
                     as.matrix %>% 
                     Hmisc::rcorr (.)))



```

```{r extract-correlations-vs-single}
v.predictors <- c("Machiavellianism", "Narcissism", "Psychopathy")

l.dat.social.type.token.sequential.corr.vs.single %>% 
    map (~ .x$corrmat$P %>% 
             as.data.frame() %>% 
             #dplyr::mutate(across (everything(), ~ .x <= .05)) %>% 
             tibble::rownames_to_column ("var") %>% 
             dplyr::select(-v.predictors) %>% 
             dplyr::rowwise() %>% 
             dplyr::mutate(keep.row = any (dplyr::c_across(-c("var")) <= .05, na.rm= TRUE)) %>% 
             dplyr::filter(keep.row) %>% 
             dplyr::select (-keep.row) %>% 
             dplyr::filter(var %in% v.predictors) %>% 
             tibble::column_to_rownames("var") %>% 
             tdf %>% 
             tibble::rownames_to_column("var") %>% 
             dplyr::rowwise() %>% 
             dplyr::mutate(keep.row = any (dplyr::c_across(-c("var")) <= .05, na.rm= TRUE)) %>% 
             dplyr::filter(keep.row) %>% 
             dplyr::select (-keep.row) %>% 
             dplyr::mutate(myValence = .x$myValence, .before = 1)) %>% 
    dplyr::bind_rows() %>% 
    dplyr::mutate(var = str_replace_all (var, fixed ("\n"), " ")) %>%
    kable.packed (
        "myValence",
        caption = "P values of significant correlations between dark triad predictors and difference scores comparing ratings to the equivalent ratings in the single occurrence condition,",
        escape = TRUE,
       booktabs = TRUE) %>%
kableExtra::kable_classic()
    

```

```{r correlations-high-vs-low-calculate}


l.dat.social.type.token.sequential.corr.high.vs.low <- dat.social.type.token.sequential.m.wide %>% 
    dplyr::group_by(myValence, Machiavellianism, Narcissism, Psychopathy) %>% 
    dplyr::select(starts_with(fixed ("d.highTypeFreq.vs.lowTypeFreq_"))) %>% 
    dplyr::select(-ends_with(fixed ("_bin"))) %>%
    dplyr::rename_with(~ .x %>% 
                           str_remove(fixed ("d.highTypeFreq.vs.lowTypeFreq_")) %>% 
                           str_remove (fixed ("_raw")) %>% 
                           str_replace_all ("_", " - ") %>% 
                           str_replace_all (fixed ("."), " ") %>% 
                           str_wrap(width = 15)) %>% 
    dplyr::group_by(myValence) %>% 
    dplyr::group_split () %>% 
    map (~ list (myValence = levels2 (.$myValence),
                 corrmat = .x %>% 
                     ungroup %>% 
                     dplyr::select(-c(myValence)) %>% 
                     as.matrix %>% 
                     Hmisc::rcorr (.)))



```

```{r extract-correlations-high-vs-low}

l.dat.social.type.token.sequential.corr.high.vs.low %>% 
    map (~ .x$corrmat$P %>% 
             as.data.frame() %>% 
             #dplyr::mutate(across (everything(), ~ .x <= .05)) %>% 
             tibble::rownames_to_column ("var") %>% 
             dplyr::select(-v.predictors) %>% 
             dplyr::rowwise() %>% 
             dplyr::mutate(keep.row = any (dplyr::c_across(-c("var")) <= .05, na.rm= TRUE)) %>% 
             dplyr::filter(keep.row) %>% 
             dplyr::select (-keep.row) %>% 
             dplyr::filter(var %in% v.predictors) %>% 
             tibble::column_to_rownames("var") %>% 
             tdf %>% 
             tibble::rownames_to_column("var") %>% 
             dplyr::rowwise() %>% 
             dplyr::mutate(keep.row = any (dplyr::c_across(-c("var")) <= .05, na.rm= TRUE)) %>% 
             dplyr::filter(keep.row) %>% 
             dplyr::select (-keep.row) %>% 
             dplyr::mutate(myValence = .x$myValence, .before = 1)) %>% 
    dplyr::bind_rows() %>% 
    dplyr::mutate(var = str_replace_all (var, fixed ("\n"), " ")) %>%
    kable.packed (
        "myValence",
        caption = "P values of significant correlations between dark triad predictors and difference scores comparing comparing the high and the low type-frequency conditions.",
        escape = TRUE,
       booktabs = TRUE) %>%
kableExtra::kable_classic()


```

```{r correlations-vs-single-plot, fig.cap = "Correlation for difference scores comparing actions against single occurrence actions.", fig.height=17}


par(mfrow=c(3, 1),  
    mar = c(1, 1, 1, 1))
    #xpd = TRUE)

l.dat.social.type.token.sequential.corr.vs.single %>% 
    purrr::walk(~ corrplot::corrplot(.x$corrmat$r,
                       is.corr = TRUE,
                       type = "lower",
                       diag = FALSE,
                       tl.col = "blue",
                       tl.cex = 1.5,
                       cl.cex = .5,
                       #bg = "gray",
                       tl.srt = 75,
                       title = str_c ("\n\n\n\n\n", .x$myValence),
                       addCoef.col = "black",
                       addgrid.col = "black",
                       #order = "hclust",
                       p.mat = .x$corrmat$P,
                       insig = "label_sig",
                       sig.level = .05,
                       mar = c(1, 1, 1, 1)
                       ))






```

```{r correlations-high-vs-low-plot, fig.cap = "Correlation for difference scores comparing high vs. low type-frequency actions.", fig.height=17}


par(mfrow=c(3, 1),  
    mar = c(1, 1, 1, 1))
    #xpd = TRUE)

l.dat.social.type.token.sequential.corr.high.vs.low %>% 
    purrr::walk(~ corrplot::corrplot(.x$corrmat$r,
                       is.corr = TRUE,
                       type = "lower",
                       diag = FALSE,
                       tl.col = "blue",
                       tl.cex = 1.5,
                       cl.cex = .5,
                       #bg = "gray",
                       tl.srt = 75,
                       title = str_c ("\n\n\n\n\n", .x$myValence),
                       addCoef.col = "black",
                       addgrid.col = "black",
                       #order = "hclust",
                       p.mat = .x$corrmat$P,
                       insig = "label_sig",
                       sig.level = .05,
                       mar = c(1, 1, 1, 1)
                       ))






```

