---
title: "Social learning by type-token frequency - stimulus preparation - actor focus experiment"
author: |
  | Ansgar D. Endress
  | City, University of London
bibliography: /Users/endress/ansgar.bib
output:
  pdf_document:
    citation_package: natbib
    toc: no
    number_sections: yes
    keep_tex: yes
    fig_caption: yes
    highlight: tango
  html_notebook:
    theme: spacelab
    number_sections: yes
    toc: yes
    toc_float: yes
    fig_caption: yes
    highlight: tango
  html_document:
    theme: spacelab
    number_sections: yes
    df_print: paged
    toc: yes
    toc_float: yes
    fig_caption: yes
    highlight: tango
csl: /Users/endress/csl_files/science.csl
keywords: Keywords
abstract: Abstract (to be written)
---

```{r setup, echo = FALSE, include=FALSE}
rm (list=ls())

options (digits = 3)
knitr::opts_chunk$set(
    # Run the chunk
    eval = TRUE,
    # Don't include source code
    echo = FALSE, 
    # Print warnings to console rather than the output file
    warning = FALSE,  
    # Stop on errors
    error = FALSE,
    # Print message to console rather than the output file
    message = FALSE,
    # Include chunk output into output
    include = TRUE,
    # Don't reformat R code
    tidy = FALSE,
    # Center images
    fig.align = 'center',
    # Default image width
    out.width = '80%')

# other knits options are here:
# https://yihui.name/knitr/options/
```


```{r load-libraries, include = FALSE, message = TRUE, warning = TRUE}

if (Sys.info()[["user"]] %in% c("ansgar", "endress")){
    source ("/Users/endress/R.ansgar/ansgarlib/R/tt.R")
    source ("/Users/endress/R.ansgar/ansgarlib/R/null.R")
    #source ("helper_functions.R")
} else {
    # Note that these will probably not be the latest versions
    source("http://endress.org/progs/tt.R")
    source("http://endress.org/progs/null.R")
}

library (knitr)
library (kableExtra)
```

```{r set-parameters}
DATA.DIR <- "../results/"
OUTPUT.DIR <- "output/"
FIG.DIR <- "figs/"




FILTER.BY.ATTRACTIVENESS <- FALSE    
MIN.ATTRACTIVENESS.QUANTILE <- .25
MAX.ATTRACTIVENESS.QUANTILE <- 1

# Parameters for analysis
IGNORE.COL.PREFIXES <- c("ITI_", "presTime_", "ISI_")

PRINT.INDIVIDUAL.FIGURES <- FALSE
PRINT.INDIVIDUAL.TABLES <- FALSE

REMOVE.BAD.SUBJ <- TRUE


# Should we remove participants who take excessively long/short?
DURATION.REMOVAL.THRESHOLD.Z <- 3

# Stimulus parameters
# PRESTIME <- 4000
# ITI <- 1000
PRESTIME <- 4500
ITI <- 500


N.REPETITIONS.PER.ACTION <- 6
# Number of face stimuli required
N.FACES.PER.GENDER <- 3 * 4 * 3 * N.REPETITIONS.PER.ACTION

VALENCE.IS.BETWEEN.SUBJECTS <- TRUE

# Set seed to Cesar's birthday
set.seed (1207100)
```

```{r helper-functions}


```

# Materials

## Faces
We selected the stimuli from the 2,222 annotated face images in [@Bainbridge2013]. For each gender and valency, we selected 4 (sets) $\times$ 3 (actions per set) $\times$ `r N.REPETITIONS.PER.ACTION` (actions) $\times$ 3 (occurrences per set) = `r 4 * 3 * N.REPETITIONS.PER.ACTION * 3` faces per gender. 


```{r load-face-attributes-nonfamous}
dat.face.attributes <- left_join(
    # Demographic attributes
    # We use the following columns: 
    # Filename
    # Image.Id 
    # "Image quality"" (as filter > 4)
    # "Is this person famous?" (as filter == 0)
    # Emotion (as filter == 0)
    # Age 
    # Race 
    # 
    # Complete description of columns:
    # Age 
	#	1 = < 20 years
	#	2 = 20 - 30 years
	#	3 = 30 - 45 years
	#	4 = 45 - 60 years
	#	5 = 60+ years
    # Attractive: 1 (unattractive) - 5 (attractive)
    # "Is this person famous?" 0 = No, 1 = Maybe, 2 = Yes
    # Common
    #   How common is this face?: 1 (uncommon) - 5 (common)
    # "How much emotion is in this face?": 1 (little) - 5 (a lot)
    # Emotion?
	#	0 = Neutral
	#	1 = Happiness
	#	2 = Sadness
	#	3 = Anger
	#	4 = Fear
	#	5 = Surprise
	#	6 = Disgust
    # "Eyes direction?"
	#	1 = At you
	#	2 = Up
	#	3 = Down
	#	4 = Left (of screen)
	#	5 = Right (of screen)
    # "Face direction?"
	#	1 = At you
	#	2 = Up
	#	3 = Down
	#	4 = Left (of screen)
	#	5 = Right (of screen)
    # "Facial hair?" ", 0 = None, 1 = A little, 2 = A lot
    # Friendly: (very unfriendly - 5 (very friendly)
    # "Makeup?" ", 0 = None, 1 = A little, 2 = A lot
    # Gender: 0 = Female		1 = Male
    # "Would you cast this person as the star of a movie?""
	#	0 = No			1 = Maybe			2 = Yes
    # Would this be a good profile picture?
    #   0 = No			1 = Maybe			2 = Yes
    # "Image quality" 1 (poor) - 5 (very good)
    # Race
	#	0 = Other
	#	1 = White
	#	2 = Black
	#	3 = East Asian
	#	4 = South Asian
	#	5 = Hispanic
	#	6 = Middle Eastern
    # Memorable: 1 (forgettable) - 5 (memorable)
    # "At what speed do you think this expression is happening?"" 1 (slowly) - 5 (quickly)
    # "How much teeth is showing?" 0 = None, 1 = A little, 2 = A lot
    readxl::read_excel (
        '~/Experiments/other_race_effect_predictability/stimuli/10k US Adult Faces Database/Full Attribute Scores/demographic & others labels/demographic-others-labels.xlsx',
        # Data collated across participants
        sheet = "Final Values") %>%
        # Don't keep rater information
        dplyr::select(-starts_with(c("sub", "catch"))) %>% 
        # Avoid problems with # character
        dplyr::rename("Image.Id" = "Image #"),
    
    # Memorability
    readxl::read_excel ("~endress/Experiments/other_race_effect_predictability/stimuli/10k US Adult Faces Database/Memorability Scores/memorability-scores.xlsx",
                        sheet = "Memorability-Scores") %>% 
        dplyr::mutate (A = purrr::map2_dbl(
            .x = `Hit Rate (HR)`,
            .y = `False Alarm Rate (FAR)`,
            .f = ~ {A.zhang.mueller (.x, .y)}
        )) %>% 
        dplyr::select (Filename, A),
    
    # Psychological attributes (e.g., personality, social, emotional traits)
    # Not currently used 
    # readxl::read_excel (
    #     'stimuli/10k US Adult Faces Database/Full Attribute Scores/psychology attributes/psychology-attributes.xlsx',
    #     # Data collated across participants
    #     sheet = "Final Values") %>%
    #     # Don't keep rater information
    #     dplyr::select(-starts_with(c("sub", "catch"))) %>% 
    #     # Avoid problems with # character
    #     dplyr::rename("Image.Id" = "Image #")
    
    
    ) %>% 
    dplyr::mutate(across (c(`Is this person famous?`, `Image quality`, `Emotion?`, Race, Gender, Age, A), 
                    as.numeric)) %>% 
    # Remove file ending for testable
    dplyr::mutate(Filename = gsub (".jpg$", "", Filename, ignore.case = TRUE))

    # We will do this conversion after plotting
    # mutate (Gender = ifelse (Gender==0, "female", "male"))
    
```


```{r filter-face-attributes-nonfamous}
dat.face.attributes %>% 
    dplyr::filter (Gender %in% 0:1,
            `Is this person famous?` == 0,
            `Image quality` >= 3.5,
            # between 20 and 60
            between(Age, 2, 4),
            between(A, quantile (A, .25), quantile(A, .85)),
            between(Race, -1, 99), 
            between(`Emotion?`, -1, 99)
            ) ->
    dat.face.attributes.filtered
    

```

```{r filter-face-attributes-attractiveness, eval = FALSE}
dat.face.attributes.filtered %>% 
    mutate (Attractive = as.numeric (Attractive)) %>% 
    filter (is.finite (Attractive)) %>% 
    mutate (Attrative.Filter = between (Attractive, 
                                        quantile (Attractive, MIN.ATTRACTIVENESS.QUANTILE), 
                                        quantile (Attractive, MAX.ATTRACTIVENESS.QUANTILE))) ->
    dat.face.attributes.filtered
    

if (FILTER.BY.ATTRACTIVENESS){
    dat.face.attributes.filtered %>% 
        filter (Attrative.Filter) -> dat.face.attributes.filtered
    
}
```

We selected photographs of non-famous faces with an image quality rating of at least 3.5, an estimated age between 20 and 60 years, and memorability (operationalized as [@ZhangMueller2005] version of $A^\prime$) between the 25% and 85% percentiles This yielded `r dat.face.attributes.filtered  %>% group_by (Gender) %>% summarize (N = n()) %>% pull(N) %>% knitr::combine_words()` photoes for female and male faces, respectively. I then randomly selected the required number of faces from this initial set, with `r N.FACES.PER.GENDER` faces being chosen for each gender.

```{r random-select-faces}

dat.face.attributes.filtered %>% 
    group_by(Gender) %>% 
    slice_sample(n = N.FACES.PER.GENDER) %>% 
    ungroup -> dat.face.attributes.filtered

```    

The distribution of various face properties is shown in Figure \ref{fig:plot-face-attributes-nonfamous}.


```{r plot-face-attributes-nonfamous, fig.cap="Distribution of various properties of the faces in the database after filtering. See main text for the filters."}

dat.face.attributes.filtered %>% 
    pivot_longer(cols = c("Age", "Race", "Gender", "A"),
                 names_to = "measure",
                 values_to = "value") %>% 
    ggplot (aes (x = value)) +
    geom_histogram() +
    scale_y_continuous(trans='log10') + 
    facet_wrap( ~ measure, scales = "free")
    
```


```{r rename-gender-labels-faces-nonfamous}
dat.face.attributes.filtered %>% 
    dplyr::mutate(Gender = case_when(
        Gender == 0 ~ "female", 
        Gender == 1 ~ "male",
        TRUE ~ as.character (Gender))) -> dat.face.attributes.filtered


```


```{r copy-stimuli}

dat.face.attributes.filtered %>% 
    group_by (Gender) %>% 
    dplyr::mutate (rownumber = dplyr::row_number()) %>% 
    tidyr::unite(stimFileName, Gender, rownumber) %>% 
    dplyr::mutate (cmd = purrr::map2_chr (
        Filename, stimFileName,
        ~ str_c ('cp \"/Users/endress/Experiments/other_race_effect_predictability/stimuli/10k US Adult Faces Database/10k US Adult Faces Database/Face Images/',
                .x,
                '.jpg\" ../stim/faces/',
                .y,
                '.jpg'))) %>% 
    pull (cmd) %>% 
    walk (~ system (.x))
            
    

      
```

## Vignettes

```{r read-scenarios}

# The scenario has different columns for the prevalenceQuestion, acceptabilityQuestionThirdParty and acceptabilityQuestionFirstParty because some differ in the pronouns that will be used
dat.scenarios <- read.delim("raw_materials/scenarios.tab", 
                            header = TRUE,
                            stringsAsFactors = FALSE) %>% 
    # Remove trailing space from character columns
    dplyr::mutate (dplyr::across (where (is.character), str_trim)) %>% 
    # Turn the following columns to numeric and set to NA
    dplyr::mutate (dplyr::across (c(set, numberWithinSet), ~ NA_integer_))

# Repeat rows for debug purposes
# dat.scenarios <- 
#     dplyr::bind_rows(
#         dat.scenarios %>% 
#             slice(rep(1:n(), 
#                       each = 4)),
#         dat.scenarios %>% 
#             dplyr::mutate(valence="neutral") %>% 
#             slice(rep(1:n(), 
#                       each = 4)),
#         dat.scenarios %>% 
#             dplyr::mutate(valence="good") %>% 
#             slice(rep(1:n(), 
#                       each = 4))
#     )

    

# Shuffle scenarios by valence
dat.scenarios <- dat.scenarios %>%
    dplyr::group_by(valence) %>%
    dplyr::slice_sample(prop = 1, replace = FALSE) %>%
    ungroup


```

We created `r dat.scenarios %>% dplyr::count(valence) %>% dplyr::pull(n) %>% unique` actions for each valence. Good and bad actions were designed to be clearly identifiable as good or bad, while avoiding actions that would be unlikely to be performed by the general population (e.g., unlike self-sacrifice or mass murder). The scenarios are given in Table \ref{tab:print-scenarios2}.

```{r print-scenarios}

dat.scenarios %>% 
    dplyr::select(valence, observation, matches ("Question")) %>% 
    dplyr::mutate(valence = factor (valence, levels = c("good", "neutral", "bad"))) %>% 
    kable.packed("valence", caption = "Actions",
                 col.names = c("Observation",
                               "How likely are people in [city] to...",
                               "Would people in [city] consider it morally acceptable to...", 
                               "Would you consider it morally acceptable to..."),
                 booktabs = TRUE, longtable = TRUE) %>% 
    kableExtra::kable_styling(latex_options = c("striped", "repeat_header")) %>% 
    kableExtra::column_spec(1, width = "6.5cm") %>% 
    kableExtra::column_spec(2:4, width = "2.5cm") %>% 
    kableExtra::add_footnote(str_c ("Place names: ", 
                                    str_c (dat.scenarios$placeName, collapse = ", ")),
                             notation = "none") %>% 
    kableExtra::kable_classic()
```

## City names

City names were generated using https://www.fantasynamegenerators.com/.

`r clearpage()`

# Design and counterbalancing
In the experiment, a traveler observed a number of actions in each city he visits. Hereafter, I refer to a "block" of trials as all actions occurring within a city, while trials are single occurrences of an action.  

Each block consisted of a behavior performed `r N.REPETITIONS.PER.ACTION` times by the same individual, one performed once by `r N.REPETITIONS.PER.ACTION` different individuals each, and a behavior performed once by one individual. To ensure that responses were not based on prior estimates of the prevalence of individual actions, the behaviors were counterbalanced across participants. 

Specifically, the 12 actions per valence were grouped into four sets of three actions. I then created three assignment conditions such that the roles of actions within blocks (high type-frequency, low type-frequency/high token-frequency, single occurrence) were counterbalanced across participants (see Table \ref{tab:counterbalancing-frequency-conditions-print2}). 


The role of the actions within the blocks was counterbalanced within participants. To maintain a reasonable experiment duration, the role of valence was counterbalanced across participants, with each participant seeing only one valence.

!!! EXPLANATION CONTINUES AFTER CHUNK !!!

```{r counterbalancing-frequency-conditions-print}

chunk.vector(1:12, 
             chunk.number = 4, 
             return.df = FALSE) %>% 
    purrr::map (function (l) purrr::map (0:2, 
                           ~ cyclic.shift (l, .x))) %>% 
    purrr::map (~ unlist (.x)) %>% 
    as.data.frame %>% 
    setNames (str_c ("Set ", 1:4)) %>% 
    dplyr::mutate (across (dplyr::everything(), ~ str_c ("Action ", .x))) %>% 
    dplyr::mutate (Condition = str_c ("Condition ", rep (1:3, each = 3)),
            Role = rep (c("High Type-Frequency", "Low Type-Frequency", "Single occurrence"), 
                        times = 3),
            .before = 1) %>% 
    kable.packed("Condition", caption="Counterbalancing of the roles of actions. Separately for each valency, actions were organized into 4 sets. Across blocks, each action of a set was presented as the high type-frequency, low type-frequency and single occurrence action.", booktabs = TRUE) %>% 
    kableExtra::kable_classic()

    
```
Specifically, all three assignment conditions were administered to all participants. Each set of four actions thus occurred in three blocks, so that each action was seen once as high type-frequency, low type-frequency/high token-frequency and single occurrence action. The faces and place names  associated with each action differed across the block. (I used the faces and placenames associated with the high type-frequency action in the original table.) This design thus yielded 12 blocks in total that appeared in random order. (In terms of testable programming, these blocks were implemented as randomblocks.)

For each participant, half of the blocks used female face and half used male faces. The correspondence between sets and genders was counterbalanced across participants. Specifically, for half of the participants, Sets 1 and 2 were presented with male faces and Sets 3 and 4 with female faces. For the remaining participants, this assignment was reversed.

This resulted in the 2 (gender/set correspondence) $\times$ 3 (valence) = $6$ participant groups shown in Table \ref{tab:counterbalancing-gender-print2}

In each block, actions were presented in a random order, with the constraint that all three types of actions (high type-frequency, low type-frequency/high token-frequency, single occurrence) appeared in the last three trials.

```{r counterbalancing-gender-print}

dat.counterbalancing.gender <- dplyr::tribble(
    ~genderSubjectGroup, ~set, ~faceGender,
    1, 1, "male",
    1, 2, "male",
    1, 3, "female",
    1, 4, "female",
    
    2, 1, "female",
    2, 2, "female",
    2, 3, "male",
    2, 4, "male"
) %>% 
    ungroup
    

if (VALENCE.IS.BETWEEN.SUBJECTS){
    dat.counterbalancing <- dplyr::tribble(
        ~valence,
        "bad",
        "neutral",
        "good") %>% 
        dplyr::arrange (valence) %>% 
        dplyr::mutate (valenceSubjectGroup = 1:n())
} else {
    dat.counterbalancing <- dplyr::tribble(
        ~valenceSubjectGroup, ~valence,
        1, NA_character_)
}
    
dat.counterbalancing <- 
    dat.counterbalancing %>% 
    dplyr::mutate (data = map (1:n(), 
                       ~ dat.counterbalancing.gender)) %>% 
    unnest %>% 
    dplyr::mutate (subjectGroup = 
                       (valenceSubjectGroup - 1) * (nlevels2 (genderSubjectGroup)) + genderSubjectGroup,
                   .before = 1)


dat.counterbalancing %>% 
    dplyr::mutate(subjectGroup = str_c ("Participant Group ", subjectGroup)) %>% 
    kable.packed("subjectGroup", caption = "Counterbalancing. The valency of the action is counter-balanced across participants. Within each valency, the gender of the face the actions are combined to is counterbalanced across participants, giving 3 groups in total.", booktabs = TRUE) %>% 
    kableExtra::kable_classic()

```

`r clearpage()`

# Procedure 

## Instructions 
Participants were first told a cover story, where a student called Noah took a gap year to visit different cities. He stayed 13 days in each city and witnessed various interesting behaviors. 

Participants were then instructed to estimate how widespread and morally acceptable the events in each city were, using a 4-point scale. 

Participants were also encouraged to use their gut reaction. 

The specific instructions are shown in Table \ref{tab:print-instructions2}.

```{r define-instructions}

dat.instructions <- data.frame(
    subjectGroup = 0,
    type = "instructions",
    myPhase = "instructionsExperiment",
    title = "Noah\'s travel journal",
    content = c(
        "<p style=\'text-align:left;\'>Noah is studying journalism at university. He decides to take a gap year to explore some countries and cities that have always interested him.<br><br>He usually stays 13 days in each place. In each place, Noah makes some interesting observations.<br><br>We will now share 12 of these stories.</p><br>Press NEXT to continue&hellip;",
        
        "<p style=\'text-align:left;\'>For each of these stories, we will ask you to guess how widespread and morally acceptable the events in the story are, in the place Noah visits.Your task is to indicate on a 4-point scale how widespread and morally acceptable these events are:<br><ul><li>\'1\' means that the events are very rare or completely unacceptable (depending on the question)</li><li>\'4\' means that the events are very common or completely acceptable (depending on the question)</li></ul></p><br>Press NEXT to continue&hellip;",
        
        "<p style=\'text-align:left;\'>We are interested in your gut reaction, so please answer with the first idea that comes to your mind after reading the stories.</p><br>Press NEXT to continue&hellip;"),
    button1 = "NEXT",
    script = "%day%=0"
)

```

```{r print-instructions}
dat.instructions %>% 
    dplyr::select(content) %>% 
    dplyr::mutate(content = str_replace_all(content, "<br>", "\n")) %>% 
    dplyr::mutate(content = str_replace_all(content, "&hellip;", "…")) %>% 
    dplyr::mutate(content = str_remove_all(content, "<.*?>")) %>% 
    knitr::kable(caption = "Cover story",
                 col.names = NULL) %>% 
    kableExtra::kable_classic_2()

```

## Attention check 

Following this, participants completed an attention check where they had to select the name of the traveller from three options (Noah, Moses, Fred). Only those who passed the attention check proceeded to the experiment. 

```{r define-attention-check}
dat.attention.check <- data.frame(
    subjectGroup = 0,
    type = "test",
    myPhase = "attentionTest",
    stim1 = "What is the name of the person whose travel journal you are about to read?",
    stimFormat = "word",
    button1 = "Moses",
    button2 = "Noah",
    button3 = "Fred",
    pageBreak = 1,
    required = 1,
    # Correct trial file: if column comes out as if.
    `if` = "!2",
    then = "end",
    feedback = "1: This is not correct, the experiment will end now.;2: This is correct.; 3: This is not correct, the experiment will end now.")
```

## Block structure

Each trial began with a screen informing participants that Noah was about to visit a new city, and that participants were about to read about Noah's visit in <city name>. Participants had to acknowledge this screen by pressing a button.

Then they were shown 13 trials, each involving three distinct actions (6 high type-frequency action trials, 6 low type-frequency/high token-frequency action trials, and one single occurrence action trial). Each trial featured a header indicating the day and the city name (e.g., "Day 2 in Cluakpus), a face, and a description of the action (e.g., "Noah went to the cinema and saw this person skip the queue"). While the trials were presented in random order, all three types of actions appear in the last three trials. Trials lasted 4500 ms, with a 500 ms intertrial-interval.

Finally, participants had to estimate the prevalence of each actions (i.e., "How likely are people in <city> to *<action>*?"), its third-person acceptability (i.e., Would *people in <city>* consider it morally acceptable to *<action>*?"), and its first-person acceptability (i.e., "Would *you* consider it morally acceptable to *<action>*?"; all emphases in original). All question were answered on a four point scale. In each trial, I first queried the high type-frequency action, then the low type-frequency action, and finally the single occurrence action.

In the pilot experiment with students, I also included the Short Dark Triad (SD3) questionnaire \cite{Jones2014}, which was removed in the main experiment. 

A demo of a trial can be found at XXXX.


# Stimulus generation code for testable.


For each action, we first generate we add `r N.REPETITIONS.PER.ACTION` faces to each action. We thus add `r 2*N.REPETITIONS.PER.ACTION` new columns to the data frame.


```{r add-faces-to-actions}

# Here dat.scenarios is just the data frame of actions and placeames

# Add columns with face stimuli to scenarios
dat.scenarios <- dplyr::bind_cols(
    dat.scenarios,
    
    # Male face stimuli
    chunk.vector (str_c ("stimuli/male_", sample.int (N.FACES.PER.GENDER), ".jpg"),
                  chunk.number = N.REPETITIONS.PER.ACTION,
                  col.names = str_c ("face.male.", 1:N.REPETITIONS.PER.ACTION)),
    
    # Female face stimuli
    chunk.vector (str_c ("stimuli/female_", sample.int (N.FACES.PER.GENDER), ".jpg"),
                  chunk.number = N.REPETITIONS.PER.ACTION,
                  col.names = str_c ("face.female.", 1:N.REPETITIONS.PER.ACTION)))
    


```

We next add the set id and number within sets

```{r add-set-ids}

dat.scenarios <- dat.scenarios %>% 
    group_by(valence) %>% 
    dplyr::mutate(
        set = 1 + ((dplyr::row_number() - 1) %/% 3)) %>% 
    group_by(valence, set) %>%
    dplyr::mutate(numberWithinSet = dplyr::row_number()) %>% 
    ungroup


```

We first initialize the trial file according to 

| randomBlock | type | stim | option  |
| --- | --- | --- | --- |
| 1 1 | learn | list with 9 occurrences of the two high token frequency actions  | randomize |
| 1 1 | learn | list with 1 occurrence of all three actions in a block | randomize |
| 1 1 | form | 3 questions in fixed order for single occurrence action | header = &nbsp; or “In <place>” |
| 1 1 | form | 3 questions in fixed order for low type frequency action | header = &nbsp; or “In <place>” |
| 1 1 | form | 3 questions in fixed order for high type frequency action | header = &nbsp; or “In <place>” |

<aside>
!!! We might add a second condition where the order of the forms is inverted
</aside>



```{r initialize-trial-file}

dat.trials <- data.frame (
    subjectGroup = numeric(),
    myGenderSubjectGroup = numeric (),
    myFaceGender = character (),
    myValence = character(),
    myPlaceName = character (),
    mySet = numeric(),
    # action 123, 231... 
    myAssignmentCondition = numeric(),
    myHighTypeFreqAction = character(),
    myLowTypeFreqAction = character(),
    mySingletonAction = character(),
    randomBlock = character(),
    myPhase = character(),
    type = character(),
    stim = character(),
    stim1 = character(),
    stimFormat = character(),
    listOptions = character(),
    title = character (),
    content = character (),
    head = character(),
    body = character (),
    button1 = character (),
    button2 = character (),
    button3 = character (),
    presTime = numeric (),
    ITI = numeric (),
    script = character()
)

```

```{r add-instructions}
dat.trials <- 
    dplyr::bind_rows(
        dat.trials,
        dat.instructions)

```

```{r add-attention-test}

dat.trials <- 
    dplyr::bind_rows(
        dat.trials,
        dat.attention.check)
            
            
            
            
```            



```{r make-trials}

make_stim_list_lines <- function (...){
    
    args <- list (...)
    
    map (args,
         function (l) {
             map2_chr (rep (l$observation, length (l$faces)),
                       l$faces,
                       ~ str_c (
                           "<p style=\'text-align:left;width:900px;\'><img src=\'",
                           .y,
                           "\' height=\'300\' style=\'padding: 0 10px 10px 0; float:left;\'  /><br><br>",
#                           "On day %day% of his visit in ", l$placeName, ", ",
                           "<b>Day %day% in ", l$placeName, "</b><br><br>",
                           .x,
                           "</p>"))
         }) %>% 
        unlist
    
    
}




random.block.counter <- 0

for (current.genderSubjectGroup in 1:2){
    
    for (cond in 1:3){
        
        row.offsets <- cyclic.shift(0:2, cond-1)
        
        # i are the starting indices of each set
        for (i in seq (1, nrow(dat.scenarios), by = 3)){
            
            random.block.counter <- random.block.counter + 1
            
            # These are the scenarios from the current set in the order
            # 123 (cond == 1), 231 (cond==2) and 312 (cond==3)
            # As the non-action trial data is taken from the first in each set, the place name is different for each occurrence of a set
            dat.current.scenarios <- dat.scenarios %>% 
                slice (i + row.offsets) 
            
            if (VALENCE.IS.BETWEEN.SUBJECTS){
                            
                current.subjectGroup <- dat.counterbalancing %>% 
                    dplyr::filter (genderSubjectGroup == current.genderSubjectGroup) %>%
                    dplyr::filter (valence == dat.current.scenarios$valence[1]) %>% 
                    pull (subjectGroup) %>% 
                    unique
                
            } else {
                
                current.subjectGroup <- current.genderSubjectGroup
            }
            
            current.faceGender <- dat.counterbalancing.gender %>% 
                dplyr::filter (genderSubjectGroup == current.genderSubjectGroup) %>% 
                dplyr::filter (set == dat.current.scenarios$set[1]) %>% 
                pull (faceGender)
            
            
            # Make list for the 5 first presentations of the high frequency actions 
            # Print in file set<set>_<action1>_<action2>_<action 3>_<cond#>_<gender>_list1.csv
            # For example, set1_action1_action2_action3_cond1_male_list1.csv would contain
            # - action1_male_face1.jpg …. action1_male_face9.jpg
            # - 5 $\times$ action2_male_face1.jpg
            
            stimList1.name <- str_c (
                current.faceGender,
                dat.current.scenarios$valence[1],
                str_c("set", dat.current.scenarios$set[1]),
                str_c("cond", cond),
                dat.current.scenarios$placeName[1],
                "list1",
                str_c(dat.current.scenarios$actionName, collapse = "_"),
                sep = "_"
            )

            current.stim.list.lines1 <- make_stim_list_lines (
                # 5 occurrences of the high type frequency action
                list (
                    placeName = dat.current.scenarios$placeName[1],
                    observation = dat.current.scenarios$observation[1],
                    faces = dat.current.scenarios %>% 
                        slice (1) %>% 
                        dplyr::select(str_c("face", current.faceGender, 1:(N.REPETITIONS.PER.ACTION-1), sep = ".")) %>% 
                        t %>% 
                        as.vector
                ), 
                # 5 occurrences of the low type frequency action
                list (
                    # Place name is taken from the high type frequency action
                    placeName = dat.current.scenarios$placeName[1],
                    observation = dat.current.scenarios$observation[2],
                    faces = dat.current.scenarios %>% 
                        slice(2) %>% 
                        dplyr::select(str_c("face", current.faceGender, N.REPETITIONS.PER.ACTION, sep = ".")) %>% 
                        t %>% 
                        as.vector %>% 
                        rep (N.REPETITIONS.PER.ACTION-1)
                )
            )
            
            # Make list for the last presentation of all 3 actions 
            # This will be identical for all conditions, but we keep the list separate for clarity
            # - set<set>_<action1>_<action2>_<action 3>_<gender>_list2.csv
            # - For example, set1__action1_action2_action3_male_list2.csv would contain
            # - action1_male_face1.jpg
            # - action2_male_face1.jpg
            # - action3_male_face1.jpg
            
            stimList2.name <- str_c (
                current.faceGender,
                dat.current.scenarios$valence[1],
                str_c("set", dat.current.scenarios$set[1]),
                str_c("cond", cond),
                dat.current.scenarios$placeName[1],
                "list2",
                str_c(dat.current.scenarios$actionName, collapse = "_"),
                sep = "_"
            )

            
            current.stim.list.lines2 <- make_stim_list_lines (
                # 1 occurrence of the high type frequency action
                list (
                    placeName = dat.current.scenarios$placeName[1],
                    observation = dat.current.scenarios$observation[1],
                    faces = dat.current.scenarios %>% 
                          slice (1) %>% 
                          pull(str_c("face", current.faceGender, N.REPETITIONS.PER.ACTION, sep = ".")) 
                ), 
                
                # 1 occurrence of the low type frequency action
                list (
                    # Place name is taken from the high type frequency action
                    placeName = dat.current.scenarios$placeName[1],
                    observation = dat.current.scenarios$observation[2],
                    faces = dat.current.scenarios %>% 
                        slice (2) %>% 
                        pull(str_c("face", current.faceGender, N.REPETITIONS.PER.ACTION, sep = ".")) 
                ),
                
                # 1 occurrence of the low type and token action (i.e., the singleton action)
                list (
                    # Place name is taken from the high type frequency action
                    placeName = dat.current.scenarios$placeName[1],
                    observation = dat.current.scenarios$observation[3],
                    faces = dat.current.scenarios %>% 
                        slice (3) %>% 
                        pull(str_c("face", current.faceGender, N.REPETITIONS.PER.ACTION, sep = ".")) 
                )
            )
            
            # Print testable rows
            dat.trials <- 
                dplyr::bind_rows(
                    dat.trials,
                    
                    # Present the announcement of the visit and the two lists
                    data.frame (
                        subjectGroup = current.subjectGroup,
                        myGenderSubjectGroup = current.genderSubjectGroup,
                        myFaceGender = current.faceGender,
                        mySet = dat.current.scenarios$set[1],
                        myAssignmentCondition = cond,
                        myPhase = "experiment",
                        myValence = dat.current.scenarios$valence[1],
                        myPlaceName = dat.current.scenarios$placeName[1],
                        myHighTypeFreqAction = dat.current.scenarios$actionName[1],
                        myLowTypeFreqAction = dat.current.scenarios$actionName[2],
                        mySingletonAction = dat.current.scenarios$actionName[3],
                        myQueriedAction = NA_character_,
                        myQueriedActionStatus = NA_character_,
                        randomBlock = random.block.counter %>% 
                            as.character(),
                        type = "learn",
                        stim = c("",
                                 stimList1.name, 
                                 stimList2.name),
                        stim1 = c(
                            str_c ("<p style=\'text-align:left;width:900px;\'>",
                                   "<font color=\'red\'>Noah will now visit a new city.</font><br><br>",
                                   "You will now read about Noah\'s visit in ",
                                   dat.current.scenarios$placeName[1],
                                   ".</p>"),
                                   "", ""),
                        stimFormat = c("word", "list", "list"),
                        listOptions = c("", "random", "random"),
                        presTime = PRESTIME,
                        ITI = ITI,
                        script = c("%day%=0",
                                   "%day%+=1",
                                   "%day%+=1")
                    ),
                    
                    # Present the surveys
                    data.frame (
                        myQueriedAction = dat.current.scenarios$actionName,
                        myQueriedActionStatus = c("highTypeFreq",
                                                  "lowTypeFreq",
                                                  "single"),
                        randomBlock = random.block.counter %>% 
                            as.character(),
                        type = "form",
                        head = str_c ("<h1>Noah in ", dat.current.scenarios$placeName[1],"</h1>"),
                        responseType = "radio",
                        responseRows = dat.current.scenarios %>% 
                            dplyr::mutate (prevalenceQuestion = str_c ("How likely are people in ", dat.current.scenarios$placeName[1], " to <b>",  prevalenceQuestion, "</b>")) %>% 
                            dplyr::mutate (acceptabilityQuestionThirdParty = str_c ("Would <i><b>people in ", dat.current.scenarios$placeName[1], "</b></i> consider it morally acceptable to <b>",  acceptabilityQuestionThirdParty, "</b>")) %>% 
                            dplyr::mutate (acceptabilityQuestionFirstParty = str_c ("Would <i><b>you</b></i> consider it morally acceptable to <b>",  acceptabilityQuestionFirstParty, "</b>")) %>% 
                            dplyr::mutate(across (matches("Questions"), 
                                                  ~ str_c ("<p style=\'text-align:left;\'>",
                                                           .x,
                                                           "</p>"))) %>% 
                            tidyr::unite(responseRows, matches ("Question"), sep = ";") %>% 
                            pull (responseRows),
                        responseOptions = "Not at all;Not really;Somewhat;Very Much so",
                        pageBreak = 1,
                        required = 1
                    )
                ) 
            
            
            # Print lists to file
            write.table(data.frame(current.stim.list.lines1),
                       file=str_c("../lists/exp1/", stimList1.name, ".csv"),
                       row.names = FALSE,
                       col.names = FALSE,
                       quote=TRUE,
                       sep = ",",
                       na = "")
            
            write.table(data.frame(current.stim.list.lines2),
                       file=str_c("../lists/exp1/", stimList2.name, ".csv"),
                       row.names = FALSE,
                       col.names = FALSE,
                       quote=TRUE,
                       sep = ",",
                       na = "")
        }# for (i in seq (1, nrow(dat.scenarios), by = 3)
    } # for (cond in 1:3){
} # for (gender in v.genders){


dat.trials <- dat.trials %>% 
                tidyr::fill (subjectGroup, myGenderSubjectGroup, myPhase, myFaceGender, myValence, myPlaceName, mySet, myAssignmentCondition, myHighTypeFreqAction, myLowTypeFreqAction, mySingletonAction, .direction = "down")

```

## SD3
We next add the Short Dark Triad (SD3) questions from \cite{Jones2014}. The survey starts with the question 

    > Please indicate how much you agree with each of the following statements.

The head on each page is then 

    > How much do you agree with this statement?

Items should be kept in the same order.


```{r read-sd3}


dat.sd3 <- read.csv("raw_materials/sd3.csv",
                    header  = TRUE,
                    comment = "#") %>% 
    dplyr::mutate(subjectGroup = 0)


```

```{r add-sd3-to-trials}

dat.trials <- 
    dplyr::bind_rows(
        dat.trials,
        data.frame (
            subjectGroup = 0,
            type = "instructions",
            myPhase = "instructionsSD3",
            title = "Please tell us more about you.",
            content = "<p style=\'text-align:left;\'>We will now ask you some questions about yourself.<br><br>Please indicate how much you agree with each of the following statements.</p><br>Press NEXT to continue&hellip;",
            button1 = "NEXT"
        ),
        dat.sd3)

    

```


```{r write-trial-file}

write.table (dat.trials,
             file = str_c ("../social_learning_type_token_sequential_trials.csv"),
             row.names = FALSE,
             quote = TRUE,
             sep = ",",
             na = "")

```



# Supplementary Only Information


## Vignettes

```{r print-scenarios2, ref.label='print-scenarios', echo=FALSE, results='asis'}
```

## Counterbalancing

```{r counterbalancing-frequency-conditions-print2, ref.label='counterbalancing-frequency-conditions-print', echo=FALSE, results='asis'}
```

```{r counterbalancing-gender-print2, ref.label='counterbalancing-gender-print', echo=FALSE, results='asis'}
```

## Instructions 
```{r print-instructions2, ref.label='print-instructions', echo=FALSE, results='asis'}
```

