---
title: "unuused_stuff"
author: "Ansgar"
date: "2025-05-09"
output: pdf_document
---

# Maybe usable

## Binarized ratings descriptives

Descriptives for the binarized ratings are given in Table \ref{tab:print-descriptives-ratings-bin}

```{r print-descriptives-ratings-bin, results = 'hide'}

dat.social.type.token.sequential.m %>% 
    dplyr::filter(scoring == "bin") %>% 
    dplyr::select(-scoring) %>% 
    dplyr::group_by(population, myValence, myQueriedActionStatus, question) %>% 
    dplyr::summarize(
        N = n(),
        M = mean(rating),
        SE = se(rating),
        d = M/sd(rating),
        # That's correct only for raw ratings, but I won't fit a GLMM here
        p = wilcox.p(rating, mu = .5),
        .groups = "drop") %>% 
    tidyr::pivot_wider(id_cols = c(myValence, myQueriedActionStatus, question),
                       names_from = population,
                       values_from = c("N", "M", "SE", "d", "p"),
                       names_vary = "slowest") %>%     
    dplyr::arrange(question, myValence, myQueriedActionStatus) %>% 
    relabel_conds(wrap = FALSE) %>% 
    relabel_questions(wrap = FALSE) %>% 
    tidyr::unite(pack.col, myValence, question, sep = " - ") %>% 
    kable.packed("pack.col", 
                 caption = "Descriptives for the binarized ratings. The p value reflects a Wilcoxon test against the  the chance level of .5. PUT TO APPENDIX",
                 col.names = c("", rep(c("N", "M", "SE", "Cohen's d", "p"), 2)),
                 booktabs = TRUE,
                 longtable = TRUE) %>% 
    kableExtra::add_header_above(header = c(" " = 1, "Students" = 5, "Testable" = 5), bold = TRUE) %>% 
    kableExtra::kable_styling(latex_options = "repeat_header") %>% 
    kableExtra::kable_classic_2()


```

## Binarized difference scores

```{r plot-difference-vs-single-bin, fig.cap = "Binary difference scores vs. single occurrence actions"}

dat.social.type.token.sequential.m.wide %>% 
    group_by (myValence) %>% 
    dplyr::select(starts_with(fixed ("d."))) %>% 
    dplyr::select(ends_with(fixed ("_bin"))) %>% 
    dplyr::select(contains (fixed ("vs.single"))) %>% 
    tidyr::pivot_longer(-c(myValence),
                        names_to = "contrast",
                        values_to = "d") %>% 
    dplyr::mutate(contrast = contrast %>% 
                       str_remove ("_bin$") %>% 
                       str_remove ("^d\\.vs\\.single\\_")) %>% 
    tidyr::separate(contrast, c("myQueriedActionStatus", "question"), sep = "_") %>% 
    dplyr::mutate(question = str_replace_all(question, fixed ("."), " ")) %>% 
    dplyr::mutate(question = str_wrap(question, 20)) %>% 
    ggplot (aes (x = myQueriedActionStatus, y = d)) %>% 
        violin_plot_template(yintercept = 0) +
    theme (axis.title.x = element_blank(),
           axis.text.x = element_text(angle = 35, vjust = .5, hjust=.5)) + 
    ylab ("Difference score (binary)") + 
    #scale_x_discrete(labels = c("Pre-segmented", "Continuous (1)", "Continuous (2)"))
    facet_grid(question ~ myValence)




```


```{r plot-difference-high-vs-low-type-frequency-bin, fig.cap = "Binary difference scores high vs. low type frequency actions"}

dat.social.type.token.sequential.m.wide %>% 
    group_by (myValence) %>% 
    dplyr::select(starts_with(fixed ("d."))) %>% 
    dplyr::select(ends_with(fixed ("_bin"))) %>% 
    dplyr::select(-contains (fixed ("vs.single"))) %>% 
    tidyr::pivot_longer(-c(myValence),
                        names_to = "question",
                        values_to = "d") %>%
    dplyr::mutate(question = question %>% 
                       str_remove ("_bin$") %>% 
                       str_remove ("^d\\.high\\.vs\\.low\\.TypeFreq_")) %>% 
    dplyr::mutate(question = str_replace_all(question, fixed ("."), " ")) %>% 
    dplyr::mutate(question = str_wrap(question, 20)) %>% 
    ggplot (aes (x = question, y = d)) %>% 
    violin_plot_template(yintercept = 0) +
    theme (axis.title.x = element_blank(),
           axis.text.x = element_text(angle = 35, vjust = .5, hjust=.5)) +
    ylab ("Difference score (binary)") + 
    #scale_x_discrete(labels = c("Pre-segmented", "Continuous (1)", "Continuous (2)"))
    facet_grid(. ~ myValence)




```



# Most likely junk

### GLMMS REMOVE? 
We analyze the binary ratings using two types of GLMMs. For valency, we set the reference level to neutral. For the frequency condition, we fit a GLMMM including all frequency conditions and setting the reference level to single occurrence events (corresponding to the first type of difference scores); we also fit a GLMM excluding the single occurrence events (corresponding to the second type of differences scores).


### Binary ratings (analyzed using GLMER) 


```{r prepare-data-for-bin-glmer-2-freq-conds}



# Two frequency conditions (i.e., low type frequency, high type frequency, but not single)
dat.social.type.token.sequential.for.glmm.bin.2freq.cond <- dat.social.type.token.sequential %>% 
    dplyr::filter(scoring == "bin") %>% 
    dplyr::filter(myQueriedActionStatus != "single") %>% 
    dplyr::mutate(myQueriedActionStatus = factor(myQueriedActionStatus,
                                                 levels = c("lowTypeFreq", "highTypeFreq")),
                  myValence = factor(myValence, 
                                     levels = c("neutral", "bad", "good")),
                  question = factor(question,
                                    levels = c("first.party.acceptability", "third.party.acceptability", "prevalence"))) %>% 
    dplyr::mutate(across(c(filename, myQueriedAction), factor))



```

##### Overall

```{r overall-glmer-bin-calculate-2freq-conds}


lmer.social.type.token.sequential.bin.overall.2freq.cond.1 <- 
    map.by.population(~  glmer(
        rating ~ question * myQueriedActionStatus * myValence + 
            (1|filename) + (1|myQueriedAction), 
        control=glmerControl(optimizer="bobyqa"),
        family="binomial",
        data = dat.social.type.token.sequential.for.glmm.bin.2freq.cond %>% 
            dplyr::filter(population == .x)))


# Remove random factor; keep it
# lmer.social.type.token.sequential.bin.overall.2freq.cond.2 <-
#     lmer.social.type.token.sequential.bin.overall.2freq.cond.1 %>%
#     purrr::map (~ update(.x,
#                          ~ . - (1|myQueriedAction)))
# 
# purrr::map2(lmer.social.type.token.sequential.bin.overall.2freq.cond.1,
#             lmer.social.type.token.sequential.bin.overall.2freq.cond.2,
#             ~ anova(.x, .y))

# Remove triple interactions; keep it
# lmer.social.type.token.sequential.bin.overall.2freq.cond.3 <-
#     lmer.social.type.token.sequential.bin.overall.2freq.cond.1 %>%
#     purrr::map (~ update(.x,
#                          ~ . - question:myQueriedActionStatus:myValence))
#  
# purrr::map2(lmer.social.type.token.sequential.bin.overall.2freq.cond.1,
#             lmer.social.type.token.sequential.bin.overall.2freq.cond.3,
#             ~ anova(.x, .y))

lmer.social.type.token.sequential.bin.overall.2freq.cond.results <- 
    lmer.social.type.token.sequential.bin.overall.2freq.cond.1 %>%
    purrr::map(~ extract.results.from.binary.model(.x)) %>%
    purrr::list_rbind(names_to = "population") 


```




##### Prevalence

```{r city-prevalence-glmer-bin-calculate-2-freq-conds}

lmer.social.type.token.sequential.bin.prevalence.2freq.cond.1 <- 
    map.by.population(~  glmer(
        rating ~ myQueriedActionStatus * myValence + 
            (1|filename) + (1|myQueriedAction), 
        control=glmerControl(optimizer="bobyqa"),
        family="binomial",
        data = dat.social.type.token.sequential.for.glmm.bin.2freq.cond %>% 
            dplyr::filter(population == .x) %>% 
            dplyr::filter(question == "prevalence")))

# Remove random factor  
lmer.social.type.token.sequential.bin.prevalence.2freq.cond.2 <- 
    lmer.social.type.token.sequential.bin.prevalence.2freq.cond.1 %>% 
    purrr::map (~ update(.x,
                         ~ . - (1|myQueriedAction)))

# purrr::map2(lmer.social.type.token.sequential.bin.prevalence.2freq.cond.1,
#             lmer.social.type.token.sequential.bin.prevalence.2freq.cond.2,
#             ~ anova(.x, .y))
    

## Remove interaction
lmer.social.type.token.sequential.bin.prevalence.2freq.cond.3 <- 
    lmer.social.type.token.sequential.bin.prevalence.2freq.cond.1 %>% 
    purrr::map(~ update(.x, ~ . - myQueriedActionStatus:myValence))

# purrr::map2(
#     lmer.social.type.token.sequential.bin.prevalence.2freq.cond.1,
#     lmer.social.type.token.sequential.bin.prevalence.2freq.cond.3,
#     ~ anova(.x, .y))

# Keep full models

lmer.social.type.token.sequential.bin.prevalence.2freq.cond.results <- 
    lmer.social.type.token.sequential.bin.prevalence.2freq.cond.1 %>% 
    purrr::map(~ extract.results.from.binary.model(.x)) %>% 
    purrr::list_rbind(names_to = "population")

```



##### Third-party acceptability

```{r city-acceptability-other-glmer-bin-calculate-2-freq-conds}


lmer.social.type.token.sequential.bin.acceptability.other.2freq.cond.1 <- 
    map.by.population(~ glmer(rating ~ myQueriedActionStatus * myValence + 
        (1|filename) + (1|myQueriedAction), 
    control = glmerControl(optimizer="bobyqa"),
    family = "binomial",
    data = dat.social.type.token.sequential.for.glmm.bin.2freq.cond %>% 
        dplyr::filter(population == .x) %>% 
        dplyr::filter(question == "third.party.acceptability")))

    
# Remove random factor  
lmer.social.type.token.sequential.bin.acceptability.other.2freq.cond.2 <- 
    lmer.social.type.token.sequential.bin.acceptability.other.2freq.cond.1 %>% 
    purrr::map(~update(., ~ . - (1|myQueriedAction)))
    
# purrr:::map2(
#     lmer.social.type.token.sequential.bin.acceptability.other.2freq.cond.1,
#     lmer.social.type.token.sequential.bin.acceptability.other.2freq.cond.2,
#     ~ anova(.x, .y))

## Remove interaction
lmer.social.type.token.sequential.bin.acceptability.other.2freq.cond.3 <- 
    lmer.social.type.token.sequential.bin.acceptability.other.2freq.cond.1 %>% 
    purrr::map(~ update(.x, ~ . - myQueriedActionStatus:myValence)  )

# purrr::map2(lmer.social.type.token.sequential.bin.acceptability.other.2freq.cond.1,
#             lmer.social.type.token.sequential.bin.acceptability.other.2freq.cond.3,
#             ~ anova(.x, .y))

# Keep full model in consistence with 3 freq condition model abvoe

lmer.social.type.token.sequential.bin.acceptability.other.2freq.cond.results <- 
    lmer.social.type.token.sequential.bin.acceptability.other.2freq.cond.1 %>% 
    purrr::map(~ extract.results.from.binary.model(.x)) %>% 
    purrr::list_rbind(names_to = "population")


```


##### First-party acceptability


```{r city-acceptability-self-glmer-bin-calculate-2-freq-conds}


lmer.social.type.token.sequential.bin.acceptability.self.2freq.cond.1 <- 
    map.by.population(~ glmer(rating ~ myQueriedActionStatus * myValence + 
        (1|filename) + (1|myQueriedAction), 
    control = glmerControl(optimizer="bobyqa"),
    family = "binomial",
    data = dat.social.type.token.sequential.for.glmm.bin.2freq.cond %>% 
        dplyr::filter(population == .x) %>% 
        dplyr::filter(question == "first.party.acceptability")))

    
# Remove random factor  
lmer.social.type.token.sequential.bin.acceptability.self.2freq.cond.2 <-
    lmer.social.type.token.sequential.bin.acceptability.self.2freq.cond.1 %>% 
    purrr::map(~  update(.x, ~ . - (1|myQueriedAction)))
    
# purrr::map2(lmer.social.type.token.sequential.bin.acceptability.self.2freq.cond.1,
#       lmer.social.type.token.sequential.bin.acceptability.self.2freq.cond.2,
#       ~ anova(.x, .y))

## Remove interaction
lmer.social.type.token.sequential.bin.acceptability.self.2freq.cond.3 <- 
    lmer.social.type.token.sequential.bin.acceptability.self.2freq.cond.1 %>% 
    purrr::map(~ update(.x, ~ . - myQueriedActionStatus:myValence))

# purrr::map2(lmer.social.type.token.sequential.bin.acceptability.self.2freq.cond.1,
#       lmer.social.type.token.sequential.bin.acceptability.self.2freq.cond.3,
#        ~ anova(.x, .y))

# Keep full model for consistency

lmer.social.type.token.sequential.bin.acceptability.self.2freq.cond.results <- 
    lmer.social.type.token.sequential.bin.acceptability.self.2freq.cond.1 %>% 
    purrr::map(~ extract.results.from.binary.model(.x)) %>% 
    purrr::list_rbind(names_to = "population")

```


```{r city-glmer-print-2-freq-conds}
dplyr::bind_rows(
    lmer.social.type.token.sequential.bin.overall.2freq.cond.results %>% 
        dplyr::mutate(pack.col = "Overall", .before = 1),
    
    lmer.social.type.token.sequential.bin.prevalence.2freq.cond.results %>% 
        dplyr::mutate(pack.col = "Prevalence", .before = 1),
    
    lmer.social.type.token.sequential.bin.acceptability.other.2freq.cond.results %>% 
        dplyr::mutate(pack.col = "Third party acceptability", .before = 1),
    
    lmer.social.type.token.sequential.bin.acceptability.self.2freq.cond.results %>% 
        dplyr::mutate(pack.col = "First party acceptability", .before = 1)
) %>% 
    dplyr::arrange(population, pack.col) %>% 
    relabel_conds(cond_col = term, wrap = FALSE) %>%
    relabel_questions(question_col = term, wrap = FALSE) %>% 
    dplyr::mutate(term = term %>% 
                      str_to_lower() %>% 
                      str_replace_all("myvalence", "valence = ") %>% 
                      str_replace_all("question", "question = ") %>% 
                      str_replace_all("myqueriedactionstatus", "status = ") %>% 
                      str_replace(":", " X ")) %>% 
    dplyr::filter(population != "testable") %>% 
    tidyr::unite(pack.col, population, pack.col, sep = " - ") %>% 
    dplyr::select (-c("t_log", "p_log")) %>% 
    dplyr::filter(p_or < .1) %>% 
    #filter (!grepl ("Intercept", term)) %>% 
    kable.packed (
    "pack.col",
    caption = "GLMER results, using the full models comparing the two frequency conditions. ONLY EFFECTS < .1 ARE SHOWN; CHANGE THIS",
    col.names = str_remove(names (.[,-1]), "_.*$"),
       booktabs = TRUE, escape = FALSE) %>%
    kableExtra::kable_classic() %>%
    kableExtra::add_header_above(c(" " = 1, "Log-odds" = 3, "Odd ratios" = 3, " " = 2),
                                 bold = TRUE) %>% 
    kableExtra::kable_styling(latex_options =
                                  c("scale_down",
                              "hold_position",
                              "full_width"))

```



## GLMM with 3 frequency conditions 
#### Binary ratings (analyzed using GLMER) ADD ORDINAL LATER
##### Overall


```{r prepare-data-for-bin-glmer-3-freq-conds}

# All three frequency conditions (i.e., single, low type frequency, high type frequency)
dat.social.type.token.sequential.for.glmm.bin.3freq.cond <- dat.social.type.token.sequential %>%
    dplyr::filter(scoring == "bin") %>% 
    dplyr::mutate(myQueriedActionStatus = factor(myQueriedActionStatus,
                                                 levels = c("single", "lowTypeFreq", "highTypeFreq")),
                  myValence = factor(myValence, 
                                     levels = c("neutral", "bad", "good")),
                  question = factor(question,
                                    levels = c("prevalence", "first.party.acceptability", "third.party.acceptability"))) %>% 
    dplyr::mutate(across(c(filename, myQueriedAction), factor))
```


```{r overall-glmer-bin-calculate-3-freq-conds}


lmer.social.type.token.sequential.bin.overall.3freq.cond.1 <- 
    map.by.population(~  glmer(
        rating ~ question * myQueriedActionStatus * myValence + 
            (1|filename) + (1|myQueriedAction), 
        control=glmerControl(optimizer="bobyqa"),
        family="binomial",
        data = dat.social.type.token.sequential.for.glmm.bin.3freq.cond %>% 
            dplyr::filter(population == .x)))


# Remove random factor; keep it  
# lmer.social.type.token.sequential.bin.overall.3freq.cond.2 <- 
#     lmer.social.type.token.sequential.bin.overall.3freq.cond.1 %>% 
#     purrr::map (~ update(.x,
#                          ~ . - (1|myQueriedAction)))

# purrr::map2(lmer.social.type.token.sequential.bin.overall.3freq.cond.1,
#             lmer.social.type.token.sequential.bin.overall.3freq.cond.2,
#             ~ anova(.x, .y))

# Remove triple interactions; keep it
# lmer.social.type.token.sequential.bin.overall.3freq.cond.3 <- 
#     lmer.social.type.token.sequential.bin.overall.3freq.cond.1 %>% 
#     purrr::map (~ update(.x,
#                          ~ . - question:myQueriedActionStatus:myValence))
# 
# purrr::map2(lmer.social.type.token.sequential.bin.overall.3freq.cond.1,
#             lmer.social.type.token.sequential.bin.overall.3freq.cond.3,
#             ~ anova(.x, .y))

lmer.social.type.token.sequential.bin.overall.3freq.cond.results <- 
    lmer.social.type.token.sequential.bin.overall.3freq.cond.1 %>%
    purrr::map(~ extract.results.from.binary.model(.x)) %>%
    purrr::list_rbind(names_to = "population") 


```

##### Prevalence (GLMM)


```{r prevalence-glmer-bin-calculate-3-freq-conds}

lmer.social.type.token.sequential.bin.prevalence.3freq.cond.1 <- 
    map.by.population(~  glmer(
        rating ~ myQueriedActionStatus * myValence + 
            (1|filename) + (1|myQueriedAction), 
        control=glmerControl(optimizer="bobyqa"),
        family="binomial",
        data = dat.social.type.token.sequential.for.glmm.bin.3freq.cond %>% 
            dplyr::filter(population == .x) %>% 
            dplyr::filter(question == "prevalence")))

# Remove random factor  
lmer.social.type.token.sequential.bin.prevalence.3freq.cond.2 <- 
    lmer.social.type.token.sequential.bin.prevalence.3freq.cond.1 %>% 
    purrr::map (~ update(.x,
                         ~ . - (1|myQueriedAction)))

# purrr::map2(lmer.social.type.token.sequential.bin.prevalence.3freq.cond.1,
#             lmer.social.type.token.sequential.bin.prevalence.3freq.cond.2,
#             ~ anova(.x, .y))
    

## Remove interaction
lmer.social.type.token.sequential.bin.prevalence.3freq.cond.3 <- 
    lmer.social.type.token.sequential.bin.prevalence.3freq.cond.1 %>% 
    purrr::map(~ update(.x, ~ . - myQueriedActionStatus:myValence))

# purrr::map2(
#     lmer.social.type.token.sequential.bin.prevalence.3freq.cond.1,
#     lmer.social.type.token.sequential.bin.prevalence.3freq.cond.3,
#     ~ anova(.x, .y))

# Keep full models

lmer.social.type.token.sequential.bin.prevalence.3freq.cond.results <- 
    lmer.social.type.token.sequential.bin.prevalence.3freq.cond.1 %>% 
    purrr::map(~ extract.results.from.binary.model(.x)) %>% 
    purrr::list_rbind(names_to = "population")

```


##### Third-party acceptability

```{r city-acceptability-other-glmer-bin-calculate-3-freqs-conds}


lmer.social.type.token.sequential.bin.acceptability.other.3freq.cond.1 <- 
    map.by.population(~ glmer(rating ~ myQueriedActionStatus * myValence + 
        (1|filename) + (1|myQueriedAction), 
    control = glmerControl(optimizer="bobyqa"),
    family = "binomial",
    data = dat.social.type.token.sequential.for.glmm.bin.3freq.cond %>% 
        dplyr::filter(population == .x) %>% 
        dplyr::filter(question == "third.party.acceptability")))

    
# Remove random factor  
lmer.social.type.token.sequential.bin.acceptability.other.3freq.cond.2 <- 
    lmer.social.type.token.sequential.bin.acceptability.other.3freq.cond.1 %>% 
    purrr::map(~update(., ~ . - (1|myQueriedAction)))
    
# purrr:::map2(
#     lmer.social.type.token.sequential.bin.acceptability.other.3freq.cond.1,
#     lmer.social.type.token.sequential.bin.acceptability.other.3freq.cond.2,
#     ~ anova(.x, .y))

## Remove interaction
lmer.social.type.token.sequential.bin.acceptability.other.3freq.cond.3 <- 
    lmer.social.type.token.sequential.bin.acceptability.other.3freq.cond.1 %>% 
    purrr::map(~ update(.x, ~ . - myQueriedActionStatus:myValence)  )

# purrr::map2(lmer.social.type.token.sequential.bin.acceptability.other.3freq.cond.1,
#             lmer.social.type.token.sequential.bin.acceptability.other.3freq.cond.3,
#             ~ anova(.x, .y))

# Keep full model

lmer.social.type.token.sequential.bin.acceptability.other.3freq.cond.results <- 
    lmer.social.type.token.sequential.bin.acceptability.other.3freq.cond.1 %>% 
    purrr::map(~ extract.results.from.binary.model(.x)) %>% 
    purrr::list_rbind(names_to = "population")


    
```

##### First-party acceptability

```{r city-acceptability-self-glmer-bin-calculate-3-freq-conds}


lmer.social.type.token.sequential.bin.acceptability.self.3freq.cond.1 <- 
    map.by.population(~ glmer(rating ~ myQueriedActionStatus * myValence + 
        (1|filename) + (1|myQueriedAction), 
    control = glmerControl(optimizer="bobyqa"),
    family = "binomial",
    data = dat.social.type.token.sequential.for.glmm.bin.3freq.cond %>% 
        dplyr::filter(population == .x) %>% 
        dplyr::filter(question == "first.party.acceptability")))

    
# Remove random factor  
lmer.social.type.token.sequential.bin.acceptability.self.3freq.cond.2 <-
    lmer.social.type.token.sequential.bin.acceptability.self.3freq.cond.1 %>% 
    purrr::map(~  update(.x, ~ . - (1|myQueriedAction)))
    
# purrr::map2(lmer.social.type.token.sequential.bin.acceptability.self.3freq.cond.1,
#       lmer.social.type.token.sequential.bin.acceptability.self.3freq.cond.2,
#       ~ anova(.x, .y))

## Remove interaction
lmer.social.type.token.sequential.bin.acceptability.self.3freq.cond.3 <- 
    lmer.social.type.token.sequential.bin.acceptability.self.3freq.cond.1 %>% 
    purrr::map(~ update(.x, ~ . - myQueriedActionStatus:myValence))

# purrr::map2(lmer.social.type.token.sequential.bin.acceptability.self.3freq.cond.1,
#       lmer.social.type.token.sequential.bin.acceptability.self.3freq.cond.3,
#        ~ anova(.x, .y))

# Keep full model for consistency

lmer.social.type.token.sequential.bin.acceptability.self.3freq.cond.results <- 
    lmer.social.type.token.sequential.bin.acceptability.self.3freq.cond.1 %>% 
    purrr::map(~ extract.results.from.binary.model(.x)) %>% 
    purrr::list_rbind(names_to = "population")

```


```{r city-glmer-print-3-freq-conds}

dplyr::bind_rows(
    lmer.social.type.token.sequential.bin.overall.3freq.cond.results %>% 
        dplyr::mutate(pack.col = "Overall", .before = 1),
    
    lmer.social.type.token.sequential.bin.prevalence.3freq.cond.results %>% 
        dplyr::mutate(pack.col = "Prevalence", .before = 1),
    
    lmer.social.type.token.sequential.bin.acceptability.other.3freq.cond.results %>% 
        dplyr::mutate(pack.col = "Third party acceptability", .before = 1),
    
    lmer.social.type.token.sequential.bin.acceptability.self.3freq.cond.results %>% 
        dplyr::mutate(pack.col = "First party acceptability", .before = 1)
) %>% 
    dplyr::arrange(population, pack.col) %>% 
    relabel_conds(cond_col = term, wrap = FALSE) %>%
    relabel_questions(question_col = term, wrap = FALSE) %>% 
    dplyr::mutate(term = term %>% 
                      str_replace_all("Myvalence", "valence = ") %>% 
                      str_replace_all("Question", "question = ") %>% 
                      str_replace_all("myqueriedactionstatus", "status = ") %>% 
                      str_replace(":", " X ")) %>% 
    dplyr::filter(population == "testable") %>% 
    tidyr::unite(pack.col, population, pack.col, sep = " - ") %>% 
    dplyr::select (-c("t_log", "p_log")) %>% 
    #filter (!grepl ("Intercept", term)) %>% 
    dplyr::filter(p_or < .1) %>% 
    kable.packed(
    "pack.col",
    caption = "GLMER results, using the full models comparing the three frequency conditions. ONLY EFFECTS < .1 ARE SHOWN; CHANGE THIS",
    col.names = str_remove(names (.[,-1]), "_.*$"),
    booktabs = TRUE, 
    escape = TRUE) %>%
    kableExtra::kable_classic() %>%
    kableExtra::column_spec(1, width = "2.5cm", latex_valign = "c") %>% 
    kableExtra::kable_styling(latex_options =
                                  c("scale_down",
                                    "hold_position")) %>% 
    kableExtra::add_header_above(c(" " = 1, "Log-odds" = 3, "Odd ratios" = 3, " " = 2),
                                 bold = TRUE) 

```


